### 2017-02-23 manuscript/manuscript.tex
include the manuscript files

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.

%% 2-Column Papers and Discussion Papers
\documentclass[gmd, manuscript]{copernicus}

%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)

% Archives Animal Breeding (aab)
% Atmospheric Chemistry and Physics (acp)
% Advances in Geosciences (adgeo)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% ASTRA Proceedings (ap)
% Atmospheric Measurement Techniques (amt)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Biogeosciences (bg)
% Climate of the Past (cp)
% Drinking Water Engineering and Science (dwes)
% Earth System Dynamics (esd)
% Earth Surface Dynamics (esurf)
% Earth System Science Data (essd)
% Fossil Record (fr)
% Geographica Helvetica (gh)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% Geothermal Energy Science (gtes)
% Hydrology and Earth System Sciences (hess)
% History of Geo- and Space Sciences (hgss)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Primate Biology (pb)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)
% Wind Energy Science (wes)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

\begin{document}

\title{3D Magnetic modelling of ellipsoidal bodies}

% \Author[affil]{given_name}{surname}

\Author[1]{Diego}{Takahashi Tomazella}
\Author[1]{Vanderlei}{C. Oliveira Jr.}

\affil[1]{Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil}
%\affil[]{}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{Magnetic modelling of ellipsoids}

\runningauthor{Tomazella and Oliveira Jr.}

\correspondence{Diego Takahashi Tomazella (diego.takahashi@gmail.com)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}

A considerable amount of literature has been published on
the magnetic modelling of of uniformly magnetized ellipsoids
since the second half of the nineteenth century.

\end{abstract}

%\introduction  %% \introduction[modified heading if necessary]
\section{Introduction}

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any uniformly magnetized body in a given direction.
By presuming that this uniform magnetization is due to
induction and that it is proportional to the resulting
magnetic field (intensity) inside the body, he postulated 
that the resulting field must also be uniform and 
parallel to the magnetization. This uniformity is due to
the fact that the resulting field is defined as the
negative gradient of the magnetic scalar potential.
As a consequence of this uniformity, 
the gravitational potential $U$ at points within the 
body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform inducing magnetic field.
This property can be extended to other bodies
defined as limiting cases of an ellipsoid
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field.

Another particularity of ellipsoids is that they are
the only bodies which enable an analytical computation 
of its self-demagnetization.
The self-demagnetization contributes to decrease the
magnitude of the magnetization along the shortest 
axes of a body.
It is a function of the body shape and gives rise
to shape anisotropy \citep{uyeda1963, thompson1986,
dunlop1997, clark1999, tauxe2003}.
It is well-established in the literature that
the self-demagnetization can be neglected if the 
body has a susceptibility lower than 0.1 \unit{SI} 
\citep{emerson1985, clark1986, eskola1980, guo1998,
guo2001, purss2005, hillan2013, austin2014, clark2014}.
On the other hand, neglecting the self-demagnetization in
geological bodies with high susceptibilities (> 0.1 \unit{SI}) 
may strongly mislead the interpretation obtained from
magnetic methods.
This limiting value, however, seems to be determined empirically
and, so far, there has been little discussion about
how it was determined.

\citet{farrar1979} demonstrated the importance of the
ellipsoidal model in taking into account the 
self-demagnetization and determining reliable 
drilling directions on the Tennant Creek field, 
Australia.
Posteriorly, \citet{hoschke1991} also showed how the
ellipsoidal model proved to be highly successful in
locating and defining ironstone bodies in the
Tennant Creek field.
\citet{clark2000} provides a good discussion about the
influence of the self-demagnetization in magnetic
interpretation of the Osborne copper-gold deposit, 
Australia. This deposit is hosted by ironstone 
bodies that have very high susceptibility.
According to \citet{clark2000}, neglecting the effects 
of self-demagnetisation led errors of $\approx 55^{\circ}$
in the interpreted dip. 
Recently, \citet{austin2014} used magnetic modelling 
and rock property measurements to show that,
contrary to previous interpretations, the magnetization
of the Candelaria iron oxide copper-gold deposit, 
Chile, is not dominated by the induced component.
Rather, the deposit has a relatively weak remanent 
magnetization and is strongly affected by 
self-demagnetization.
These examples show the importance of the self-demagnetization 
and the ellipsoidal model in 
producing trustworthy geological models of
high-susceptibility orebodies, which may save significant 
cost associated with drilling.

A vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which 
are to be found the names of many researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by a list of modern papers in this
field.
Besides, the geoscientific community lacks an easy-to-use 
tool to simulate the magnetic field produced by uniformly 
magnetized ellipsoids.
Such a tool could prove to be useful either for teaching
and researching geophysics.

In this work, we present a review of the vast literature
about the magnetic modelling of ellipsoidal bodies and a
theoretical discussion about the determination of the 
isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
This alternative approach is validated
by the results obtained with numerical simulations.
We also provide a set of routines to 
model the magnetic field produced by ellipsoids.
The routines are written in Python language as part of
the Fatiando a Terra \citep{uieda2013}, which is an 
open-source library for modelling and inversion in geophysics.
We attempt to use the best practices of continuous 
integration, documentation, unit-testing, and version-control
for the purpose of providing a reliable and easy-to-use
code.

\section{Methodology}

\subsection{Geometrical parameters and coordinate systems}

Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
$x$, $y$ and $z$ pointing to, respectively, North, East and down.
For convenience, we denominate this coordinate system as 
\textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
Let us consider an ellipsoidal body with centre at the point 
$(x_{c}, y_{c}, z_{c})$, orientation defined by three angles 
$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a), 
and semi-axes defined by
positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
The angles $\varepsilon$, $\zeta$, and $\eta$ are called \textit{strike}, 
\textit{dip}, and \textit{rake}, respectively, and are commonly used to
define the orientation of lines in structural geology
\citep{clark1986, allmendinger2012}.
The points $(x, y, z)$ located on the surface of this ellipsoidal body
satisfy the following equation:
\begin{equation}
(\mathbf{r} - \mathbf{r}_c)^T \mathbf{A} (\mathbf{r} - \mathbf{r}_c) = 1 \: ,
\label{eq:ellipsoid_surface}
\end{equation}
where $\mathbf{r} = [\begin{array}{ccc} x & y & z \end{array} ]^{\top}$,
$\mathbf{r}_{c} = [\begin{array}{ccc} x_{c} & y_{c} & z_{c} \end{array} ]^{\top}$,
$\mathbf{A}$ is a positive definite matrix given by
\begin{equation}
\mathbf{A} = \mathbf{V}
\left[ \begin{array}{ccc}
a^{-2} & 0 & 0 \\
0 & b^{-2} & 0 \\
0 & 0 & c^{-2} 
\end{array} \right] \mathbf{V}^{\top} \: ,
\label{eq:A}
\end{equation}
and $\mathbf{V}$ is an orthogonal matrix whose first, second and third columns 
are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
(Fig. \ref{fig:orientation-angles}b), respectively.
These unit vectors are commonly described in terms of auxiliary 
orientation angles $\alpha$, $\gamma$, and $delta$, which are not used
by the geoscientific community. These angles, however, can be defined from
$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a)
as follows \citep{clark1986}:
\begin{equation}
\alpha = \varepsilon - \cos^{-1} \left[ \frac{\cos \eta}
{\left( 1 - \sin^{2} \zeta \, \sin^{2} \eta \right)^{\frac{1}{2}}}\right] \: ,
\label{eq:alpha}
\end{equation}
\begin{equation}
\gamma = \tan^{-1} \left( \frac{\cos \zeta}{\sin \zeta \, \cos \eta}\right)
\label{eq:gamma}
\end{equation}
and
\begin{equation}
\delta = \sin^{-1} \left( \sin \zeta \, \sin \eta \right) \: ,
\label{eq:delta}
\end{equation}
where $-90^{\circ} \leq \gamma \leq 90^{\circ}$ and
$0 \leq \delta \leq 90^{\circ}$.
Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a and Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}), we define the unit vectors
$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
(Fig. \ref{fig:orientation-angles}b) according to the ellipsoid type.
For triaxial ellipsoids (i.e., $a > b > c$), these unit vectors are 
given by \citep{clark1986}:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v1_triaxial_prolate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v2_triaxial_prolate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_triaxial_prolate}
\end{equation}
Similarly, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
for prolate ellipsoids (i.e., $a > b = c$) are calculated
by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$
\citep{emerson1985}.
Finally, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
for oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \sin\gamma \; \sin\delta + \sin\alpha \; \cos\gamma \\               
                  -\sin\alpha \; \sin\gamma \; \sin\delta - \cos\alpha \; \cos\gamma \\ 
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v1_oblate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v2_oblate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \sin\gamma + \cos\alpha \; \cos\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \sin\gamma + \sin\alpha \; \cos\gamma \; \sin\delta \\
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_oblate}
\end{equation}
These formulas are similar to those presented by \citep{emerson1985}.

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre
(Fig. \ref{fig:orientation-angles}b).
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
(Eq. \ref{eq:A}) is defined according to the ellipsoid type.
Subsequently, quantities referred to the local coordinate system
(Fig. \ref{fig:orientation-angles}b) are represented with
the simbol "$\sim$".

\subsection{Theoretical background}

Consider a magnetized ellipsoid immersed in
a uniform inducing magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
given by
\begin{equation}
\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
\begin{array}{c}
\cos I \: \cos D \\
\cos I \: \sin D \\
\sin I
\end{array}
\right] \: ,
\label{eq:H0}
\end{equation}
where $\| \cdot \|$ denotes the Euclidean norm (or 2-norm) and
$D$ and $I$ are respectively, the declination and inclination of the 
local-geomagnetic field in the main coordinate system
(Fig. \ref{fig:orientation-angles}a).
This field represents the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:V-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Eq. \ref{eq:V-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896, reitz1992, sttraton2007}.

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
This is a good approximation for bodies at room temperature,
subjected to an inducing field $\mathbf{H}_{0}$ with 
strength $\leq 1$ \unit{mT} \citep{rochette1992}.
In this case, the susceptibility tensor $\mathbf{K}$ is commonly
represented, in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions}.
The unit vectors $\mathbf{u}_{i}$ may be defined
similarly to $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ (Eqs. \ref{eq:v1_triaxial_prolate},
\ref{eq:v2_triaxial_prolate}, \ref{eq:v3_triaxial_prolate},
\ref{eq:v1_oblate}, \ref{eq:v2_oblate}, and \ref{eq:v3_oblate}),
by a given set of orientation angles $\varepsilon$, $\zeta$,
and $\eta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}).

If the principal susceptibilities are different from
each other, we say that the body has an
anisotropy of magnetic susceptibility (AMS).
The AMS is generally associated to the preferred orientation
of the grains of magnetic minerals forming the rock
\citep{fuller1963, uyeda1963, janak1972, hrouda1982, 
thompson1986, macdonald1987, rochette1992, dunlop1997,
tauxe2003}.
For the particular case in which the principal directions 
coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
equal to the matrix $\mathbf{V}$ (Eq. \ref{eq:A}).
Another important particular case is that in which the
susceptibility is isotropic and, consequently, the principal
susceptibilities $k_{1}$, $k_{2}$, and $k_{3}$ (Eq. \ref{eq:K})
are equal to a constant $\chi$. In this case, the susceptibility
tensor $\mathbf{K}$ (Eq. \ref{eq:K}) assumes the particular form
\begin{equation}
\mathbf{K} = \chi \, \mathbf{I} \: ,
\label{eq:K-isotropic}
\end{equation}
where $\mathbf{I}$ represents the identity matrix.

By using the magnetization $\mathbf{M}$ defined by Eq. \ref{eq:M-KH}, 
the total magnetic field $\mathbf{H}(\mathbf{r})$ (Eq. \ref{eq:H}) 
can be rewritten as follows:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
+ \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:H-M-uniform}
\end{equation}
where $\mathbf{N}(\mathbf{r})$ is a symmetrical matrix whose
$ij$-element $n_{ij}(\mathbf{r})$ is given by
\begin{equation}
n_{ij}(\mathbf{r}) = 
\frac{1}{4\pi} \frac{\partial^{2} \, f(\mathbf{r})}
{\partial r_{i} \, \partial r_{j}} 
\: , \quad i = 1, 2, 3 \: , 
\quad j = 1, 2, 3 \: ,
\label{eq:nij}
\end{equation}
$r_{1} = x$, $r_{2} = y$, $r_{3} = z$ are the elements of 
the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}), 
and
\begin{equation}
f(\mathbf{r}) = \iiint_{\vartheta} 
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:f}
\end{equation}
Notice that the scalar function $f(\mathbf{r})$ 
(Eq. \ref{eq:f}) is proportional
to the gravitational potential that would be produced by the 
ellipsoidal body with volume $\vartheta$ if it had a uniform density 
equal to the inverse of the gravitational constant.
It can be shown that the elements $n_{ij}(\mathbf{r})$ are
finite whether $\mathbf{r}$ is a point within or without
the volume $\vartheta$ \citep{peirce1902, webster1904}.
The matrix $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform})
is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008}.

The following part of this paper moves on to describe 
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) at points located
both within and without the volume $\vartheta$ of the ellipsoidal
body. However, the mathematical developments are conveniently 
performed in the local coordinate system (Fig. \ref{fig:orientation-angles}b)
related to the respective ellipsoidal body.

\subsection{Coordinate transformation}

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system (Fig. \ref{fig:orientation-angles}a)
into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system (Fig. \ref{fig:orientation-angles}b).
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
peake1953, macmillan1958, chang1961, lowes1974,  clark1986, 
tejedor1995, sttraton2007}.

It is convenient to use $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
and $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ to define 
the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
respectively, at points 
$\tilde{\mathbf{r}}$ inside and outside the volume $\vartheta$ of the
ellipsoidal body.
The scalar function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\dagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{0}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in \vartheta \: ,
\label{eq:fi-tilde}
\end{equation}
where
\begin{equation}
R(u) = \sqrt{\left( a^{2} + u \right)\left( b^{2} + u \right)\left( c^{2} + u \right)} \: .
\label{eq:R}
\end{equation}
This function represents the gravitational potential
that would be produced by the ellipsoidal body at
points located within its volume $\vartheta$ if it
had a uniform density equal to the inverse of the
gravitational constant.
Notice that, in this case, the gravitational potential
is a quadratic function of the spatial coordinates
$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
postulate about uniformly magnetized ellipsoids.
In a similar way, the function $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\ddagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{\lambda}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in \vartheta \: ,
\label{eq:fe-tilde}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and the
parameter $\lambda$ is defined according to the
ellipsoid type as a function of the spatial coordinates
 $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ (see Appendix B). 
For readers interested in additional information about the 
parameter $\lambda$, we recommend \citet[p.~234]{webster1904},
\citet[p.~184]{kellogg1929} and \citet{clark1986}.

The second important coordinate transformation is defined
with respect to Eq. \ref{eq:H-M-uniform}.
By properly using the orthogonality of matrix $\mathbf{V}$ 
(Eq. \ref{eq:A}),
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) can be transformed
from the main coordinate system (Fig. \ref{fig:orientation-angles}a) 
to the local coordinate system (Fig. \ref{fig:orientation-angles}b) as follows:
\begin{equation}
\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
+ \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
_{\tilde{\mathbf{K}}} \; 
\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
_{\tilde{\mathbf{H}}^{\dagger}} \: ,
\label{eq:H-tilde}
\end{equation}
where the superscript "$\sim$" denotes quantities
referred to the respective local coordinate system.

In Eq. \ref{eq:H-tilde}, the transformed
depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
is calculated as a function of the original depolarization
tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
are calculated as a function of the second derivatives of the
function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
which is defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a).
It can be shown (Appendix A), however, that the
elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
as follows:
\begin{equation}
\tilde{n}_{ij}(\tilde{\mathbf{r}}) = 
\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
\label{eq:nij-tilde}
\end{equation}
where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Eq. \ref{eq:fi-tilde}
or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
point located within or without the volume $\vartheta$ of the
ellipsoidal body.

\subsection{Transformed depolarization tensors $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}

\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$}

Let $\tilde{\mathbf{N}}^{\dagger}$ be the transformed
depolarization tensor calculated for the case in which
$\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
represents a point located outside
the ellipsoidal body. In this case, 
the elements of $\tilde{\mathbf{N}}^{\dagger}$
are calculated according to Eq. \ref{eq:nij-tilde}, 
with $\tilde{f}(\tilde{\mathbf{r}})$ given by 
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the  
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the 
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}). 
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the \unit{SI}
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
It is worth stressing that, according to Eq. \ref{eq:n-tilde-dagger-ii},
the demagnetizing factors $\tilde{n}^{\dagger}_{ii}$ are 
constants defined by the ellipsoid semi-axes $a$, $b$, and $c$.

Notice that, according to Eqs. \ref{eq:H-tilde} 
and \ref{eq:N-tilde-VT-N-V},
\begin{equation}
\mathbf{N}(\mathbf{r}) = 
\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
\mathbf{V}^{\top} \: ,
\label{eq:N-V-N-dagger-VT}
\end{equation}
where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
This equation shows that, for the particular case 
in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
represent a point inside the
volume $\vartheta$ of the ellipsoid, the elements 
$\tilde{n}^{\dagger}_{ii}$
of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
columns of $\mathbf{V}$ represent the eigenvectors of the 
original depolarization tensor $\mathbf{N}(\mathbf{r})$.

\subparagraph*{Triaxial ellipsoids}

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: ,
\label{eq:E-kappa-phi}
\end{equation}
with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
$\cos \phi = c/a$.
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas. It can be shown that these demagnetizing factors
satisfy the conditions
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + \tilde{n}^{\dagger}_{33} = 1$
and
$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$.

\subparagraph*{Prolate ellipsoids}

For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
- 1 \right\rbrace
\label{eq:n-tilde-dagger-11-prolate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-prolate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
with $\tilde{n}^{\dagger}_{11}$ defined in 
Eq. \ref{eq:n-tilde-dagger-11-prolate} and $m = a/b$.
The detailed deduction of the demagnetizing factors 
$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
can be found, for example, in \citet{stoner1945}. 
These formulas were posteriorly presented by \citet{emerson1985}.
It can be shown that these demagnetizing factors
satisfy the conditions
$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
and
$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$.

\subparagraph*{Oblate ellipsoids}

For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = 
\frac{1}{1 - m^{2}} \left[
1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
\right]
\label{eq:n-tilde-dagger-11-oblate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-oblate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
with $\tilde{n}^{\dagger}_{11}$ defined in 
Eq. \ref{eq:n-tilde-dagger-11-oblate} and $m = a/b$.
The detailed deduction of these demagnetizing factors 
can be found, for example, in \citet{stoner1945}.
These formulas can also be found in \citet{emerson1985}.
The only difference, however, is that \citet{emerson1985} replaced
the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
the trigonometric identity 
$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.
It can be shown that these demagnetizing factors
satisfy the conditions
$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
and
$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$.

\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$}

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ 
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).
By following \citet{clark1986}, the diagonal elements 
$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
and the off-diagonal elements 
$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$, $i = 1, 2, 3$,
$j = 1, 2, 3$, are given by
\begin{equation}
\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
-\frac{abc}{2}
\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
+ g_{i} \right)
\label{eq:n-tilde-ddagger-ii}
\end{equation}
and
\begin{equation}
\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
-\frac{abc}{2} \left(
\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
\right) \: ,
\label{eq:n-tilde-ddagger-ij}
\end{equation}
where
\begin{equation}
h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
\label{eq:hi}
\end{equation}
\begin{equation}
g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
\label{eq:gi}
\end{equation}
$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
is defined in Appendix B (Eq. \ref{eq:dlambda}).
The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
to the ellipsoid type.
Notice that the elements $\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:n-tilde-ddagger-ii}) and 
$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:n-tilde-ddagger-ij}) 
are proportional to the second derivatives of the function
$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
which is harmonic. Consequently, the diagonal elements 
$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$ satisfy the condition
$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
of the ellipsoid type.

\subparagraph*{Triaxial ellipsoids}

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
%\begin{equation}
%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
%\left[ E\left(\kappa, \phi \right) 
%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
%F\left(\kappa, \phi \right) 
%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%\right]
%\label{eq:g2-triaxial}
%\end{equation}
\begin{equation}
g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
\left\lbrace
E\left(\kappa, \phi \right) 
- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
F\left(\kappa, \phi \right) -
\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
\right]^{\frac{1}{2}} \right\rbrace
\label{eq:g2-triaxial}
\end{equation}
and
%\begin{equation}
%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
%\: ,
%\label{eq:g3-triaxial}
%\end{equation}
\begin{equation}
g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
E\left(\kappa, \phi \right) +
\frac{2}{b^{2} - c^{2}}
\left[
\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
\right]^{\frac{1}{2}}
\: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
A detailed deduction of these formulas was presented by \citet{tejedor1995}.
Similar formulas can also be found in \citet{clark1986}.

\subparagraph*{Prolate ellipsoids}

For prolate (e.g., $a > b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by:
\begin{equation}
g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
\right\rbrace
\label{eq:g1-prolate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\frac{\left[ \left( a^{2} - b^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda} -
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
\right\rbrace \: ,
\label{eq:g2-prolate}
\end{equation}
where $g_{3} = g_{2}$.
These formulas can be obtained by properly manipulating those
presented by \citep{emerson1985}.

\subparagraph*{Oblate ellipsoids}

For oblate (e.g., $a < b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by:
\begin{equation}
g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
\right\rbrace
\label{eq:g1-oblate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
\frac{\left[ \left( b^{2} - a^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda}
\right\rbrace \: ,
\label{eq:g2-oblate}
\end{equation}
where $g_{3} = g_{2}$.
Similarly to the case of prolate ellipsoid shown previously,
these formulas can be obtained by properly manipulating those
presented by \citep{emerson1985}.

\subsection{Internal magnetic field and magnetization}

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ is defined in the
previous section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in 
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$ 
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq. \ref{eq:M-remanence}, by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

%The angular difference $\theta$ between the resultant magnetization
%and the inducing field is the same, whether the quantities
%are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
%or local coordinate system (Fig. \ref{fig:orientation-angles}b).
%For convenience, we define $\theta$ (in degrees) in the main coordinate system
%by using the scalar product definition as follows:
%\begin{equation}
%\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
%\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
%{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
%\label{eq:theta}
%\end{equation}
%where $\mathbf{M}$ is obtained by pre-multiplying the
%magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
%by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
%which is defined according to the ellipsoid type, and
%$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
%
For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and the matrix $\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda})
can be rewritten as follows:
\begin{equation}
\mathbf{M} = \mathbf{\Lambda} \left( \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \right) \: ,
\label{eq:M-K-isotropic}
\end{equation}
and
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda-K-isotropic}
\end{equation}
Despite the coordinate transformation represented by
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
this equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}), 
represents the induced magnetization whereas the term depending on
$\mathbf{M}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-K-isotropic} reveals that, as pointed out by
many authors
\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic})
approaches to the identity and the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
can be approximated by:
\begin{equation}
\breve{\mathbf{M}} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
whether it is parallel to an ellipsoid axis or not.
Usually, Eq. \ref{eq:M-approx}
is considered a good approximation for $\chi \leq 0.1$ \unit{SI}.
Although this value has been largely used in the literature,
there have been few empirical and/or theoretical investigations 
about it.

\subsubsection{Relationship between $\chi$ and the relative error in $\breve{\mathbf{M}}$}

In the case of isotropic susceptibility, the resultant magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic}) may be determined by solving the
following linear system:
\begin{equation}
\mathbf{\Lambda}^{-1} \, \mathbf{M} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-K-isotropic-inverse-Lambda}
\end{equation}
where, according to Eq. \ref{eq:Lambda-K-isotropic},
\begin{equation}
\mathbf{\Lambda}^{-1} = \mathbf{V}
\left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
\mathbf{V}^{\top} \: .
\label{eq:inverse-Lambda}
\end{equation}
As we have already pointed out, the approximated
magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
represents the particular case in which the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic}),
and consequently the matrix $\mathbf{\Lambda}^{-1}$
(Eq. \ref{eq:inverse-Lambda}), are close to the identity.
%Our goal in this subsection is to bound the norm of the
%difference between the true magnetization $\mathbf{M}$
%(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
%and the approximated magnetization $\breve{\mathbf{M}}$
%(Eq. \ref{eq:M-approx}).

Consider a perturbed matrix $\delta \mathbf{\Lambda}^{-1}$ given by
\begin{equation}
\delta \mathbf{\Lambda}^{-1} = \mathbf{\Lambda}^{-1} - \mathbf{I}
\label{eq:perturbed-inverse-Lambda}
\end{equation}
and, similarly, a perturbed magnetization vector $\delta \mathbf{M}$
given by
\begin{equation}
\delta \mathbf{M} = \mathbf{M} - \breve{\mathbf{M}} \: .
\label{eq:perturbed-M}
\end{equation}
By using these two equations, we may rewrite that of the approximated
magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) as follows:
\begin{equation}
\left( \mathbf{\Lambda}^{-1} - \delta \mathbf{\Lambda}^{-1} \right)
\left( \mathbf{M} - \delta \mathbf{M} \right) = 
\chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: .
\label{eq:perturbed-system}
\end{equation}
Now, by subtracting the true magnetization 
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic-inverse-Lambda})
from this linear system (Eq. \ref{eq:perturbed-system})
and rearranging the terms, we obtain the following linear
system for the perturbed magnetization $\delta \mathbf{M}$
(Eq. \ref{eq:perturbed-M}):
\begin{equation}
\delta \mathbf{M} = - \delta \mathbf{\Lambda}^{-1} \mathbf{M} \: .
\label{eq:perturbed-M-system}
\end{equation}

By using the concept of vector norm and its corresponding
operator norm \citep{demmel1997, golub2013}, we may use Eq.
\ref{eq:perturbed-M-system} to write the following inequality:
\begin{equation}
\frac{\| \delta \mathbf{M} \|}{\| \mathbf{M} \|} \leq
\| \delta \mathbf{\Lambda}^{-1} \| \: .
\label{eq:perturbed-M-inequality}
\end{equation}
where $\| \delta \mathbf{M} \|$ and $\| \mathbf{M} \|$
denote Euclidean norms (or 2-norms) and the term 
$\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
of $\delta \mathbf{\Lambda}^{-1}$.
By using Eqs. \ref{eq:inverse-Lambda} and \ref{eq:perturbed-inverse-Lambda}
and the orthogonal invariance of the matrix 2-norm
\citep{demmel1997, golub2013}, we define
$\| \delta \mathbf{\Lambda}^{-1} \|$ as follows:
\begin{equation}
\| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
\tilde{n}^{\dagger}_{max} \: ,
\label{eq:norm-perturbed-inverse-Lambda}
\end{equation}
where $\tilde{n}^{\dagger}_{max}$ is the demagnetization
factor associated to the shortest ellipsoid semi-axis.
For a triaxial ellipsoid, 
$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}), for a prolate ellipsoid,
$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-prolate}), and,
for an oblate ellipsoid,
$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-oblate}).
It is worth stressing that, independently of the ellipsoid
type, $\tilde{n}^{\dagger}_{max}$ is
a scalar function of the ellipsoid semi-axes.
In Eq. \ref{eq:perturbed-M-inequality}, the ratio
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$ represents the
\textit{relative error} in the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) with respect
to the true magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-K-isotropic}
and \ref{eq:M-K-isotropic-inverse-Lambda}).
Given a target relative error $\epsilon$ and an ellipsoid
with given semi-axes, we may use the inequality
represented by Eq. \ref{eq:norm-perturbed-inverse-Lambda}
to define
\begin{equation}
\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{max}} \: ,
\label{eq:chi-max}
\end{equation}
which represents the maximum isotropic susceptibility 
that the ellipsoidal body can assume in order o guarantee
a relative error lower than or equal to $\epsilon$.
For isotropic susceptibilities greater than $\chi_{max}$,
there is no guarantee that the relative error in the
approximated magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
with respect to the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
is lower than or equal to $\epsilon$. The geoscientific community
has been using $\chi_{max} = 0.1$ \unit{SI} as a limit value for
neglecting the self-demagnetization and, consequently,
use magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
as a good approximation of the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
Equation \ref{eq:chi-max}, on the other hand, defines $\chi_{max}$ 
as a function of the ellipsoid semi-axes, according to a
user-specified relative error $\epsilon$.

\subsection{External magnetic field and total-field anomaly}

The magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
produced by an ellipsoid at external points is calculated from 
Eqs. \ref{eq:H-tilde} and \ref{eq:M-remanence} as the difference
between the resultant field $\mathbf{H}(\mathbf{r})$ 
and the inducing field $\mathbf{H}_{0}$:
\begin{equation}
\Delta \mathbf{H}(\mathbf{r}) = 
\mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
\mathbf{M} \: ,
\label{eq:delta-H}
\end{equation}
where $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ is
the transformed depolarization tensor whose elements 
$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$ and
$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$ are defined,
respectively, by Eqs. \ref{eq:n-tilde-ddagger-ii} and
\ref{eq:n-tilde-ddagger-ij}.
$\Delta \mathbf{H}(\mathbf{r})$ 
represents the magnetic field produced by a uniformly magnetized 
body located in the crust.
Equation \ref{eq:delta-H} gives the magnetic field
(in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
in geophysics, the most widely used field is the magnetic 
induction (in \unit{nT}). Fortunately, this conversion can
be easily done by multiplying Eq. \ref{eq:delta-H}
by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
magnetic constant (in \unit{H \, m^{-1}}).
For geophysical applications, it is preferable to
calculate the total-field anomaly produced by the
magnetic sources. This scalar quantity is given by
\citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) = \| 
\mathbf{B}_{0} + \Delta \mathbf{B}(\mathbf{r}) \|
- \| \mathbf{B}_{0} \| \: ,
\label{eq:delta-T}
\end{equation}
where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
and $\Delta \mathbf{B}(\mathbf{r}) = 
k_{m} \, \Delta \mathbf{H}(\mathbf{r})$,
with $\mathbf{H}_{0}$ and $\Delta \mathbf{H}(\mathbf{r})$ defined,
respectively, by Eqs. \ref{eq:H0} and \ref{eq:delta-H}.
In practical situations, however, 
$\| \mathbf{B}_{0} \| >> \| \Delta \mathbf{B}(\mathbf{r}) \|$
and, consequently, the following approximation is valid \citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) \approx  
\frac{\mathbf{B}_{0}^{\top} \Delta \mathbf{B}(\mathbf{r})}{\| \mathbf{B}_{0} \|} \: .
\label{eq:delta-T-approx}
\end{equation}

\section{Computational implementation and reproducibility}

The code is implemented in Python language,
by using the NumPy and SciPy libraries \citep{vanderwalt2011},
as part of the open-source source library
Fatiando a Terra \citep{uieda2013}.
Our code is very modular and has a
test suite formed by a considerable number of 
assertions, unit tests, doc tests and integration tests.
For readers interested in automated code testing,
we recommend the freely reusable lessons of the Software Carpentry 
(\url{https://software-carpentry.org/}) and at the
description of the doctest module available
in the documentation for Python 2.X 
(\url{https://docs.python.org/2/library/doctest.html}).

The numerical simulations presented here was generated with
the Jupyter Notebook
(\url{http://jupyter-notebook.readthedocs.io/en/latest/notebook.html}),
which is a web application that allows creating and sharing
documents that contain live code, equations, visualizations and
explanatory text.
Besides using the Fatiando a Terra \citep{uieda2013},
the numerical simulations use the 
NumPy library \citep{vanderwalt2011} to perform numerical
computations, the Matplotlib library \citep{hunter2007} to plot
the results and generate figures.
The Jupyter Notebooks used to reproduce all the results presented here
are available at a repository in the GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).

\section{Numerical simulations}

\subsection{Demagnetizing factors}

We simulate a triaxial ellipsoid with semi-axes 
$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
Then we use this ellipsoid as a reference to generate
100 different triaxial ellipsoids and calculate
their demagnetizing factors $\tilde{n}^{\dagger}_{11}$,
$\tilde{n}^{\dagger}_{22}$, and $\tilde{n}^{\dagger}_{33}$ 
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
The semi-axes of these 100 ellipsoids are given by
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and 
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$.
Notice that, for $u = 0$, the resulting semi-axes are equal those
of the reference ellipsoid.
The larger the variable $u$, the larger the resulting semi-axes
$a$, $b$, and $c$, but the smaller the relative difference between
them.
Consequently, the resulting ellipsoids obtained from the semi-axes
$a$, $b$, and $c$ become more spherical as $u$ increases.
In this case, the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}),
$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial}),
and
$\tilde{n}^{\dagger}_{33}$ (Eq. \ref{eq:n-tilde-dagger-33-triaxial})
tend to $1/3$ \citep[e.g.,][]{stoner1945}.

Figure \ref{fig:demag-factors}a shows the calculated 
demagnetizing factors $\tilde{n}^{\dagger}_{11}$ (in red),
$\tilde{n}^{\dagger}_{22}$ (in green), and
$\tilde{n}^{\dagger}_{33}$ (in blue) for the 
100 triaxial ellipsoids.
The result shows that the relative difference
between the demagnetizing factors is large for
small values of $u$ and decreases as $u$ increases.
In this case, all demagnetizing factors tend to $1/3$, according
to what we know from theory. 
Besides, Fig. \ref{fig:demag-factors}a confirms that the demagnetizing
factors satisfy the condition
$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$
independently of the value of $u$.

We have also simulated 100 different prolate
ellipsoids with semi-axes $a = m \; b_{0}$ and $b = b_{0}$,
where $1.02 \leq m \leq 10$ and $b_{0} = 1000$ \unit{m},
and calculate their demagnetizing factors 
$\tilde{n}^{\dagger}_{11}$ and $\tilde{n}^{\dagger}_{22}$
by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
\ref{eq:n-tilde-dagger-22-prolate}, respectively.
Similarly, we simulated 100 different oblate
ellipsoids with semi-axes $a = m \; b_{0}$ and $b = b_{0}$,
where $0.02 \leq m \leq 0.98$ and $b_{0} = 1000$ \unit{m},
and calculate their demagnetizing factors 
$\tilde{n}^{\dagger}_{11}$ and $\tilde{n}^{\dagger}_{22}$
by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
\ref{eq:n-tilde-dagger-22-oblate}, respectively.

Figures \ref{fig:demag-factors}b and c show the results obtained for
the 100 prolate and the 100 oblate ellipsoids, respectively.
As expected from theory, the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (red line in Fig. \ref{fig:demag-factors}b)
and
$\tilde{n}^{\dagger}_{22}$ (green line in Fig. \ref{fig:demag-factors}b)
calculated for the prolate ellipsoids are close to $1/3$ for $m$ close to $1$.
Besides, these demagnetizing factors satisfy the condition 
$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$ for all values
of $m$.
The result obtained for the oblate ellipsoids (Fig. \ref{fig:demag-factors}c)
are also in perfect agreement with theory.
The demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green), which were calculated by using
Eqs. \ref{eq:n-tilde-dagger-11-oblate} and \ref{eq:n-tilde-dagger-22-oblate},
respectively, 
are close to $1/3$ for $m$ close to $0$ and satisfy the condition 
$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$ for all values
of $m$.

\subsection{Simulation of a geological body}

\citet{farrar1979} represented the Warrego orebody as a triaxial
ellipsoid having a high isotropic susceptibility.
In this case, the self-demagnetization strongly impacts the
magnetic modelling of this body.
According to \citet{wedekind1990}, the Warrego orebody is a combination of
two major and several small ironstone lodes, which are discrete bodies
comprised predominantly of magnetite or hematite above the base of
oxidation.
The Warrego orebody was the resource on which the Warrego mine was
developed. After nearly a decade as one of the most important 
gold and copper mines in Australia, the Warrego mine was closed 
in late 1989.

Table \ref{tab:parameters-warrego} shows the parameters defining
a synthetic orebody which is based on that presented by
\citet{farrar1979} to represent the Warrego orebody.
Figure \ref{fig:tfa-warrego} shows the total-field anomaly
$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) produced
by the synthetic body on a regular grid of $100 \times 100$
points at a constant vertical coordinate $z = 0$ \unit{m}.
The total-field anomaly varies from $\approx -295.3$ \unit{nT}
to $\approx 149.5$ \unit{nT}, resulting in a peak-to-peak amplitude
of $\approx 444.9$ \unit{nT}, and was calculated by using the 
true magnetization $\mathbf{M}$ defined in Eqs. 
\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}.

We have calculated the difference between the total-field anomaly
$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) calculated with the
true magnetization $\mathbf{M}$ (Eqs. 
\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
and that calculated with the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}).
The differences were calculated by using the synthetic body 
defined in Tab. \ref{tab:parameters-warrego}, but with three
different isotropic susceptibilities.
Figures \ref{fig:tfa-differences-warrego}a, \ref{fig:tfa-differences-warrego}b
and \ref{fig:tfa-differences-warrego}c show the differences calculated
by using, respectively, isotropic susceptibilities $\chi = 1.69$ \unit{SI} 
(Tab. \ref{tab:parameters-warrego}), $\chi_{1} = 0.1$ \unit{SI} and 
$\chi_{2} = 0.116$ \unit{SI}.

As expected, the differences calculated by using the higher isotropic
susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
The peak-to-peak amplitude is $\approx 212.0$ \unit{nT}
and represents $\approx 48 \%$ of the peak-to-peak amplitude of
the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
This result reinforces that the use of the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
the magnetic modelling of bodies with high isotropic susceptibility.

Figure \ref{fig:tfa-differences-warrego}b shows the differences calculated
by using $\chi_{1} = 0.1$ \unit{SI}.
It is commonly accepted that, for bodies having isotropic susceptibilities
lower than or equal to $0.1$ \unit{SI}, the self-demagnetization can be neglected and,
consequently, the magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
is a good approximation of the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.2 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 1.5$ \unit{nT},
which represents $\approx 4.5 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).

Finally, Fig. \ref{fig:tfa-differences-warrego}c shows the differences
calculated by using $\chi_{2} = 0.116$ \unit{SI}.
This value was calculated by using Eq. \ref{eq:chi-max} with a
target relative error $\epsilon = 8 \%$ and the $\tilde{n}^{\dagger}_{max}$
defined by Eq. \ref{eq:n-tilde-dagger-33-triaxial}.
By using this isotropic susceptibility, it is expected that the
calculated relative error 
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization be
lower than or equal to the target relative error $\epsilon = 8 \%$.
In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.9 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 2.0$ \unit{nT},
which represents $\approx 5.1 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In this case, the use an isotropic susceptibility greater than the usual
limit $0.1$ \unit{SI} does not mislead the magnetic modelling
dramatically. On the contrary, it shows small discrepancies in the
magnetic modelling and validates Eq. \ref{eq:chi-max}.

\section{Conclusions}  %% \conclusions[modified heading if necessary]

We present an integrated review of the vast literature 
about the magnetic modelling of triaxial, prolate and
oblate ellipsoids.
We also present a theoretical discussion about the
determination of the isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
Our approach is an alternative to the constant value which
seems to be determined empirically and
has been used by the geoscientific community.
Our alternative approach is validated
by the results obtained with numerical simulations.
In a future work,
it would be interesting to use a similar approach to
to bound the maximum relative error in the
magnetic field calculated by neglecting the self-demagnetization.

This work also provide a set of routines to model the magnetic 
field produced by ellipsoids.
The routines are written in Python language as part of
the Fatiando a Terra \citep{uieda2013}, which is an 
open-source library for modelling and inversion in geophysics.
The current version of our code is freely distributed
in a repository of GitHub. We are working to integrate our
routines in the following stable release of Fatiando a Terra.
We hope that these routines be useful to the wide geoscientific
community either in researching and teaching.

\section{Code availability}

The current version of our code is freely distributed, under 
BSD 3-clause licence, in a repository of GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
The code was developed as part of the Fatiando a Terra 
\citep{uieda2013}, which is an open-source Python 
library for modelling and inversion in geophysics.
Instructions for running the current version of our code
in the Fatiando a Terra are provided at its repository
in GitHub.
Documentation and installation instructions for 
the most current release version of Fatiando a Terra 
are provided at \url http://www.fatiando.org.

\appendix
\section{Derivatives of the functions $f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$} %% Appendix A

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
function obtained by transforming $f(\mathbf{r})$ 
(Eq. \ref{eq:f}) from the
main coordinate system (Fig. \ref{fig:orientation-angles}a)
to the local coordinate system (Fig. \ref{fig:orientation-angles}b).
For convenience, let us rewrite Eq. 
\ref{eq:coord_transformation} as follows:
\begin{equation}
\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
\label{eq:r-tilde-k}
\end{equation}
where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
$\mathbf{V}$ (Eq. \ref{eq:A}),
and $c_{k}$ is a constant defined by the coordinates
$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.

By considering the functions $f(\mathbf{r})$ 
(Eq. \ref{eq:f}) and $\tilde{f}(\tilde{\mathbf{r}})$
evaluated at the same point, but on different coordinate
systems, we have:
\begin{equation*}
\frac{\partial f(\mathbf{r})}{\partial r_{j}} = 
\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} \,
\frac{\partial \tilde{r}_{1}}{\partial r_{j}} +
\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} \,
\frac{\partial \tilde{r}_{2}}{\partial r_{j}} +
\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \,
\frac{\partial \tilde{r}_{3}}{\partial r_{j}} \: ,
\quad j = 1, 2, 3 \: ,
\end{equation*}
which, from Eq. \ref{eq:r-tilde-k}, can be given by
\begin{equation}
\frac{\partial f(\mathbf{r})}{\partial r_{j}} = 
v_{j1} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} +
v_{j2} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} +
v_{j3} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \: ,
\quad j = 1, 2, 3 \: .
\label{eq:df_drj}
\end{equation}

Now, by deriving $\frac{\partial f(\mathbf{r})}{\partial r_{j}}$
(Eq. \ref{eq:df_drj}) with respect to the $i$th element 
$r_{i}$ of the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
we obtain:
\begin{equation}
\begin{split}
\frac{\partial^{2} f(\mathbf{r})}{\partial r_{i} \, \partial r_{j}} &=
v_{j1} \, \frac{\partial}{\partial r_{i}} 
\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} \right) +
v_{j2} \, \frac{\partial}{\partial r_{i}} 
\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} \right) +
v_{j3} \, \frac{\partial}{\partial r_{i}} 
\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \right) \\
&= v_{j1} \, \left( 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{1} \, \partial \tilde{r}_{1}} \, v_{i1} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{2} \, \partial \tilde{r}_{1}} \, v_{i2} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{3} \, \partial \tilde{r}_{1}} \, v_{i3} 
\right) + \\
&+ v_{j2} \, \left( 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{1} \, \partial \tilde{r}_{2}} \, v_{i1} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{2} \, \partial \tilde{r}_{2}} \, v_{i2} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{3} \, \partial \tilde{r}_{2}} \, v_{i3} 
\right) + \\
&+ v_{j3} \, \left( 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{1} \, \partial \tilde{r}_{3}} \, v_{i1} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{2} \, \partial \tilde{r}_{3}} \, v_{i2} + 
\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{3} \, \partial \tilde{r}_{3}} \, v_{i3} 
\right) \\
&= \left[ \begin{array}{ccc}
v_{j1} & v_{j2} & v_{j3}
\end{array} \right] \tilde{\mathbf{F}}(\tilde{\mathbf{r}})
\left[ \begin{array}{c}
v_{i1} \\ v_{i2} \\ v_{i3}
\end{array} \right]
\end{split} \: ,
\label{eq:d2f-dridrj}
\end{equation}
where $\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ is a $3 \times 3$
matrix whose $ij$-th element is 
$\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}}$.
From Eq. \ref{eq:d2f-dridrj}, we obtain
\begin{equation}
\mathbf{F}(\mathbf{r}) = \mathbf{V} \, 
\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top} \: ,
\label{eq:F-V-F-tilde-VT}
\end{equation}
where $\mathbf{F}(\mathbf{r})$ is a $3 \times 3$
matrix whose $ij$-th element is 
$\frac{\partial^{2} f(\mathbf{r})}
{\partial r_{i} \, \partial r_{j}}$ and
$\mathbf{V}$ (Eq. \ref{eq:A}) is defined according
to the ellipsoid type. As one may noticed, 
the matrices $\mathbf{F}(\mathbf{r})$ and
$\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ represent the Hessians
of the functions $f(\mathbf{r})$ (Eq. \ref{eq:f})
and $\tilde{f}(\tilde{\mathbf{r}})$, respectively.
Besides, the depolarization tensor $\mathbf{N}(\mathbf{r})$
(Eq. \ref{eq:H-M-uniform}) can be 
rewritten by using the matrix $\mathbf{F}(\mathbf{r})$
as follows
\begin{equation}
\mathbf{N}(\mathbf{r}) = \frac{1}{4 \pi} \mathbf{F}(\mathbf{r}) \: .
\label{eq:N-F}
\end{equation}
By properly using the orthogonality of the matrix
$\mathbf{V}$ (Eq. \ref{eq:A}), we may rewrite Eq. \ref{eq:F-V-F-tilde-VT}
as follows:
\begin{equation}
\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) = \mathbf{V}^{\top} \, 
\mathbf{F}(\mathbf{r}) \, \mathbf{V} \: .
\label{eq:F-tilde-VT-F-V}
\end{equation}
Finally, by multiplying both sides of Eq. \ref{eq:F-tilde-VT-F-V}
by $\frac{1}{4 \pi}$ and using Eq. \ref{eq:N-F},
we conclude that 
\begin{equation}
\tilde{\mathbf{N}}(\tilde{\mathbf{r}}) = 
\mathbf{V}^{\top} \, \mathbf{N}(\mathbf{r}) \, \mathbf{V} \: .
\label{eq:N-tilde-VT-N-V}
\end{equation}

\section{Parameter $\lambda$ and its spatial derivatives}    %% Appendix B

Here, we follow the reasoning presented by \citet{webster1904}
for analysing the parameter $\lambda$ which defines triaxial, prolate
and oblate ellipsoids.

\subsection{Parameter $\lambda$ defining triaxial ellipsoids} %% Appendix A1, A2, etc.

Let us consider an ellipsoid with semi-axes $a$, $b$, $c$ oriented along 
the $\tilde{x}$-, $\tilde{y}$-, and $\tilde{z}$-axis, respectively, 
of its local coordinate system (Fig. \ref{fig:orientation-angles}b), where $a > b > c > 0$. 
This ellipsoid is defined by the following equation:
\begin{equation}
\frac{\tilde{x}^{2}}{a^{2}} + \frac{\tilde{y}^{2}}{b^{2}} + \frac{\tilde{z}^{2}}{c^{2}} = 1 \: .
\label{eq:reference-triaxial-ell}
\end{equation}
A quadric surface (e.g., ellipsoid, hyperboloid of one sheet or
hyperboloid of two sheets) which is confocal with the ellipsoid 
defined in Eq. \ref{eq:reference-triaxial-ell} can be 
described as follows:
\begin{equation}
\frac{\tilde{x}^{2}}{a^{2} + u} + \frac{\tilde{y}^{2}}{b^{2} + u} + \frac{\tilde{z}^{2}}{c^{2} + u} = 1 \: ,
\label{eq:quadric-confocal-triaxial-ell}
\end{equation}
where $u$ is a real number. Equation \ref{eq:quadric-confocal-triaxial-ell} 
represents an ellipsoid for $u$ satisfying the condition
\begin{equation}
u + c^{2} > 0 \: .
\label{eq:condition-triaxial-ell}
\end{equation}

Given $a$, $b$, $c$, and a $u$ satisfying \ref{eq:condition-triaxial-ell}, 
we may use \ref{eq:quadric-confocal-triaxial-ell} for determining a set of 
points $(x, y, z)$ lying on the surface of an ellipsoid which is confocal 
with that one defined in Eq. \ref{eq:reference-triaxial-ell}. 
Now, consider the problem of determining the ellipsoid which is confocal 
with that one defined in \ref{eq:reference-triaxial-ell} and pass through 
a particular point $(\tilde{x}, \tilde{y}, \tilde{z})$. 
This problem consists in determining the real number $u$ that, 
given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
satisfies Eq. \ref{eq:quadric-confocal-triaxial-ell} and
the condition expressed by Eq. \ref{eq:condition-triaxial-ell}.
By rearranging Eq. \ref{eq:quadric-confocal-triaxial-ell}, 
we obtain the following cubic equation for $u$:
\begin{equation}
p(u) = (a^{2} + u)(b^{2} + u)(c^{2} + u) - (b^{2} + u)(c^{2} + u) \, \tilde{x}^{2}
- (a^{2} + u)(c^{2} + u) \, \tilde{y}^{2} - (a^{2} + u)(b^{2} + u) \, \tilde{z}^{2} \: .
\label{eq:cubic-equation-triaxial-ell}
\end{equation}
This cubic equation shows that:
\begin{equation}
u = \begin{cases}
d \to \infty \: &, \quad p(u) > 0 \\
-c^{2} \: &, \quad p(u) < 0 \\
-b^{2} \: &, \quad p(u) > 0 \\
-a^{2} \: &, \quad p(u) < 0
\end{cases} \: .
\label{eq:cubic-equation-signals-triaxial-ell}
\end{equation}
Notice that, according to \ref{eq:cubic-equation-signals-triaxial-ell},
the smaller, intermediate and largest roots of the cubic 
equation $p(u)$ (Eq. \ref{eq:cubic-equation-triaxial-ell}) are 
located, respectively, in the intervals $[ -a^{2} \, , -b^{2} ]$,
$[ -b^{2} \, , -c^{2} ]$ and $[ -c^{2} \, , \infty [$.
Remember that we are interested in a $u$ satisfying 
the condition expressed by Eq. \ref{eq:condition-triaxial-ell}. 
Consequently, according to the signal analysis shown in Eq.
\ref{eq:cubic-equation-signals-triaxial-ell}, we are interested in 
the largest root $\lambda$ of the cubic equation $p(u)$ (Eq.
\ref{eq:cubic-equation-triaxial-ell}).

From Eq. \ref{eq:cubic-equation-triaxial-ell}, we obtain a
simpler one given by
\begin{equation}
p(u) =  u^{3} + p_{2} \, u^{2} + p_{1} \, u + p_{0} \: ,
\label{eq:cubic-equation-triaxial-ell-simpler}
\end{equation}
where
\begin{equation}
p_{2} = a^{2} + b^{2} + c^{2} - \tilde{x}^{2} - \tilde{y}^{2} - \tilde{z}^{2} \: ,
\label{eq:p2-triaxial-ell}
\end{equation}
\begin{equation}
p_{1} = b^{2} \, c^{2} + a^{2} \, c^{2} + a^{2} \, b^{2} 
- (b^{2} + c^{2}) \, \tilde{x}^{2}
- (a^{2} + c^{2}) \, \tilde{y}^{2} 
- (a^{2} + b^{2}) \, \tilde{z}^{2}
\label{eq:p1-triaxial-ell}
\end{equation}
and
\begin{equation}
p_{0} =  a^{2} \, b^{2} \, c^{2} - b^{2} \, c^{2} \, 
\tilde{x}^{2} - a^{2} \, c^{2} \, \tilde{y}^{2} - a^{2} \, 
b^{2} \, \tilde{z}^{2} \: .
\label{eq:p0-triaxial-ell}
\end{equation}
Finally, from Eqs. \ref{eq:p2-triaxial-ell}, 
\ref{eq:p1-triaxial-ell} and \ref{eq:p0-triaxial-ell},
the largest root $\lambda$ of $p(u)$ 
(Eq. \ref{eq:cubic-equation-triaxial-ell-simpler}) can be 
calculated as follows \citep{weisstein2017}:
\begin{equation}
\lambda = 2 \, \sqrt{-Q} \, \cos \left( \frac{\varphi}{3}\right) - \frac{p_{2}}{3} \: ,
\label{eq:lambda-triaxial-ell}
\end{equation}
where
\begin{equation}
\varphi = \cos^{-1} \left( \frac{R}{\sqrt{-Q^{3}}} \right) \: ,
\label{eq:varphi-triaxial-ell}
\end{equation}
\begin{equation}
Q = \frac{3 \, p_{1} - p_{2}^{2}}{9}
\label{eq:Q-triaxial-ell}
\end{equation}
and
\begin{equation}
R = \frac{9 \, p_{1} \, p_{2} - 27 \, p_{0} - 2 \, p_{2}^{3}}{54} \: .
\label{eq:R-triaxial-ell}
\end{equation}

\subsection{Parameter $\lambda$ defining prolate and oblate ellipsoids} %% Appendix A1, A2, etc.

Let us now consider a prolate ellipsoid with semi-axes $a$, $b$, 
$c$ oriented along the $\tilde{x}$-, $\tilde{y}$-, and 
$\tilde{z}$-axis, respectively, of its local coordinate system
(Fig. \ref{fig:orientation-angles}b), where $a > b = c > 0$. 
In this case, the Eq. defining the surface of the ellipsoid
is obtained by substituting $c = b$ in Eq. \ref{eq:reference-triaxial-ell}.
Consequently, the equation defining the respective confocal quadric
surface is given by
\begin{equation}
\frac{\tilde{x}^{2}}{a^{2} + u} + \frac{\tilde{y}^{2} + \tilde{z}^{2}}{b^{2} + u} = 1
\label{eq:quadric-confocal-prolate-ell}
\end{equation}
and the new condition that must be fulfilled by the variable
$u$ so that Eq. \ref{eq:quadric-confocal-prolate-ell}
represent an ellipsoid is
\begin{equation}
u + b^{2} > 0 \: .
\label{eq:condition-prolate-ell}
\end{equation}

Similarly to the case of a triaxial ellipsoid presented
in the previous subsection, we are interested in
determining the real number $u$ that, 
given $a$, $b$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
satisfies Eq. \ref{eq:quadric-confocal-prolate-ell} and
the condition expressed by Eq. \ref{eq:condition-prolate-ell}.
From Eq. \ref{eq:quadric-confocal-prolate-ell}, 
we obtain the following quadratic equation for $u$:
\begin{equation}
p(u) = (a^{2} + u)(b^{2} + u) - (b^{2} + u) \, \tilde{x}^{2}
- (a^{2} + u) \, (\tilde{y}^{2} + \tilde{z}^{2}) \: .
\label{eq:quadratic-equation-prolate-ell}
\end{equation}
This equation shows that
\begin{equation}
u = \begin{cases}
d \to \infty \: &, \quad f(\rho) > 0 \\
-b^{2} \: &, \quad f(\rho) < 0 \\
-a^{2} \: &, \quad f(\rho) > 0
\end{cases}
\label{eq:quadratic-equation-signals-prolate-ell}
\end{equation}
and, consequently, that its two roots lie in the intervals
$[ -a^{2} \, , -b^{2} ]$ and $[ -b^{2} \, , \infty [$.
Therefore, according to the condition established by
Eq. \ref{eq:condition-prolate-ell} and the signal analysis 
shown in Eq. \ref{eq:quadratic-equation-signals-prolate-ell}, 
we are interested in the largest root $\lambda$ of the quadratic 
equation $p(u)$ (Eq. \ref{eq:quadratic-equation-prolate-ell}).

By properly manipulating Eq. \ref{eq:quadratic-equation-prolate-ell},
we obtain a simpler one given by
\begin{equation}
p(u) =  u^{2} + p_{1} \, u + p_{0} \: ,
\label{eq:quadratic-equation-prolate-ell-simpler}
\end{equation}
where
\begin{equation}
p_{1} = a^{2} + b^{2} - \tilde{x}^{2} - \tilde{y}^{2} - \tilde{z}^{2}
\label{eq:p1-prolate-ell}
\end{equation}
and
\begin{equation}
p_{0} =  a^{2} \, b^{2} 
- b^{2} \, \tilde{x}^{2} 
- a^{2} \left( \tilde{y}^{2} + \tilde{z}^{2} \right) \: .
\label{eq:p0-prolate-ell}
\end{equation}
Finally, by using Eqs. \ref{eq:p1-prolate-ell} and
\ref{eq:p0-prolate-ell}, the largest root $\lambda$ of $p(u)$ 
(Eq. \ref{eq:quadratic-equation-prolate-ell-simpler}) can be 
easily calculated as follows:
\begin{equation}
\lambda = \frac{-p_{1} + \sqrt{p_{1}^{2} - 4 \, p_{0}}}{2} \: .
\label{eq:lambda-prolate-ell}
\end{equation}

In the case of oblate ellipsoids, the procedure for determining
the parameter $\lambda$ is very similar to this one for prolate
ellipsoids.
The semi-axes $a$, $b$, $c$ of oblate 
ellipsoids are defined so that $b = c > a > 0$
and the condition that must be fulfilled by 
the variable $u$ is $u + a^{2} > 0$.
In this case, the two roots of the resulting quadratic equation 
lie in the intervals $[ -b^{2} \, , -a^{2} ]$ and $[ -a^{2} \, , \infty [$.
Consequently, we are still interested in the largest root of
the quadratic equation for the variable $u$, which is also 
calculated by using Eq. \ref{eq:lambda-prolate-ell}.

\subsection{Spatial derivative of the parameter $\lambda$}

The magnetic modelling of triaxial, prolate or oblate ellipsoids 
requires not only the parameter lambda defined by Eqs.
\ref{eq:lambda-triaxial-ell} and \ref{eq:lambda-prolate-ell},
but also its derivatives with respect to the spatial coordinates
$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$.
Fortunately, the spatial derivatives of the parameter $\lambda$ 
can be calculated in a very similar way for all ellipsoid types.

Let us first consider a triaxial ellipsoid. In this case,
the spatial derivatives of $\lambda$ are given by
\begin{equation}
\frac{\partial \lambda}{\partial \tilde{r}_{j}} =
\frac{\frac{2 \, \tilde{r}_{j}}{\left( e_{j}^{2} + \lambda \right)}}{
\left( \frac{\tilde{x}}{a^{2} + \lambda}\right)^{2} +
\left( \frac{\tilde{y}}{b^{2} + \lambda}\right)^{2} + 
\left( \frac{\tilde{z}}{c^{2} + \lambda}\right)^{2}} \: , \quad j = 1, 2, 3 \: ,
\label{eq:dlambda}
\end{equation}
where 
$\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, $\tilde{r}_{3} = \tilde{z}$,
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$.
This equation can be determined directly from equation
\ref{eq:quadric-confocal-triaxial-ell}. 
The spatial derivatives of $\lambda$ in the case of
prolate or oblate ellipsoids can also be calculated by using
Eq. \ref{eq:dlambda} for the particular case in
with $b = c$.

\authorcontribution{TEXT}

\begin{acknowledgements}
TEXT
\end{acknowledgements}

%% REFERENCES

%% The reference list is compiled as follows:

%%\begin{thebibliography}{}

%%\bibitem[AUTHOR(YEAR)]{LABEL}
%%REFERENCE 1

%%\bibitem[AUTHOR(YEAR)]{LABEL}
%%REFERENCE 2

%%\end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{references}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% ONE-COLUMN FIGURES

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/structural_orientation_angles.png}
\caption{Schematic representation of the coordinate systems used to
represent an ellipsoidal body. 
(a) Main coordinate system with axes $x$, $y$, and $z$ pointing to
North, East, ans down, respectively.
The dark gray plane contains the centre $(x_{c}, y_{c}, z_{c})$
(white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
semi-axes of the ellipsoidal body. For triaxial and prolate ellipsoids,
$\mathbf{u}$ and $\mathbf{w}$ define, respectively, 
the semi-axes $a$ and $b$. For oblate ellipsoids, $\mathbf{u}$ and 
$\mathbf{w}$ define the semi-axes $b$ and $c$, respectively.
The strike direction is defined by the intersection of the
dark gray plane and the horizontal plane (represented in light gray),
which contains the $x$ and $y$ axes. The angle $\varepsilon$ 
between "minus $x$" and the strike direction is called \textit{strike}.
The angle $\zeta$ between the horizontal plane and the dark gray plane
is called \textit{dip}. The line containing the unit vector
$\mathbf{u}$ defines the \textit{plunge direction}. 
The angle $\eta$ between the strike direction and the plunge direction
is called \textit{rake}. The projection
of the plunge direction on the horizontal plane is called
\textit{plunge azimuth direction}. (b) Local coordinate system
with origin at the ellipsoid centre $(x_{c}, y_{c}, z_{c})$
(black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
and oblate ellipsoids in the same way.
For triaxial and prolate ellipsoids,
the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide
with $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$, respectively. For 
oblate ellipsoids, the unit vectors $\mathbf{u}$ and $\mathbf{w}$ 
shown in (a) coincide with $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$,
respectively.}
\label{fig:orientation-angles}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
\caption{(a) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red),
$\tilde{n}^{\dagger}_{22}$ (in green), and
$\tilde{n}^{\dagger}_{33}$ (in blue)
produced by 100 triaxial ellipsoids with semi-axes
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and 
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$ and
$b_{0} = 700$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
(b) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 prolate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $1.02 \leq m \leq 10$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
\ref{eq:n-tilde-dagger-22-prolate}.
(c) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 oblate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $0.02 \leq m \leq 0.98$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
\ref{eq:n-tilde-dagger-22-oblate}.
The horizontal black line represent the value $1/3$.}
\label{fig:demag-factors}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
\caption{Total-field anomaly produced by the synthetic orebody
defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
are calculated on a regular grid of $100 \times 100$ points
at the constant vertical coordinate $z = 0$ \unit{m}.}
\label{fig:tfa-warrego}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/field_differences.pdf}
\caption{Difference between the total-field 
anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}) and with the 
true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
The total-field anomalies are calculated with Eq. \ref{eq:delta-T-approx},
on a regular grid of $100 \times 100$ points,
at the constant vertical coordinate $z = 0$ \unit{m}.
The differences are produced by the synthetic orebody defined in
Tab. \ref{tab:parameters-warrego}, but with different
isotropic susceptibilities:
(a) the isotropic susceptibility defined in 
Tab. \ref{tab:parameters-warrego},
(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
This last value was calculated
with Eq. \ref{eq:chi-max}, by using $\epsilon = 8 \%$.}
\label{fig:tfa-differences-warrego}
\end{figure}

%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%

\newpage

%t
\begin{table}[t]
\caption{Parameters defining a synthetic orebody. This model is
based on the that presented by \citet{farrar1979} to simulate
the Warrego orebody, Tennant Creek field, Australia.}
%\begin{tabular}{column = lcr}
\begin{tabular}{lcr}
\tophline
Parameter & Value & Unit \\
\middlehline
Semi-axis $a$ & $490.7$ & \unit{m} \\
Semi-axis $b$ & $69.7$ & \unit{m} \\
Semi-axis $c$ & $30.0$ & \unit{m} \\
Coordinate of the centre $x_{c}$ & 0 & \unit{m} \\
Coordinate of the centre $y_{c}$ & 0 & \unit{m} \\
Coordinate of the centre $z_{c}$ & 500 & \unit{m} \\
Orientation angle $\varepsilon$ $^{\ast}$ & $-34.0$ & $^{\circ}$ \\
Orientation angle $\zeta$ $^{\ast}$ & $66.1$ & $^{\circ}$ \\
Orientation angle $\eta$ $^{\ast}$ & $45.0$ & $^{\circ}$ \\
Isotropic susceptibility $\chi$ & $1.69$ & \unit{SI} \\
$x$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 32610 & \unit{nT} \\
$y$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 0 & \unit{nT} \\
$z$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 39450 & \unit{nT} \\
\bottomhline
\end{tabular}
\belowtable{$^{\ast}$ Defined in Fig. \ref{fig:orientation-angles}a \newline
$^{\dagger}$ Defined in Eq. \ref{eq:delta-T}} % Table Footnotes
\label{tab:parameters-warrego}
\end{table}

%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation

\end{document}

### 2017-02-23 code/mesher/mesher.py
include the code files

@@ -1,0 +1,1946 @@
+"""
+Generate and operate on various kinds of meshes and geometric elements
+"""
+from __future__ import division
+import numpy
+import scipy.special
+import scipy.interpolate
+import copy as cp
+
+from . import gridder
+
+
+class GeometricElement(object):
+
+    """
+    Base class for all geometric elements.
+    """
+
+    def __init__(self, props):
+        self.props = {}
+        if props is not None:
+            for p in props:
+                self.props[p] = props[p]
+
+    def addprop(self, prop, value):
+        """
+        Add a physical property to this geometric element.
+
+        If it already has the property, the given value will overwrite the
+        existing one.
+
+        Parameters:
+
+        * prop : str
+            Name of the physical property.
+        * value : float
+            The value of this physical property.
+
+        """
+        self.props[prop] = value
+
+    def copy(self):
+        """ Return a deep copy of the current instance."""
+        return cp.deepcopy(self)
+
+
+class Polygon(GeometricElement):
+
+    """
+    Create a polygon object.
+
+    .. note:: Most applications require the vertices to be **clockwise**!
+
+    Parameters:
+
+    * vertices : list of lists
+        List of [x, y] pairs with the coordinates of the vertices.
+    * props : dict
+        Physical properties assigned to the polygon.
+        Ex: ``props={'density':10, 'susceptibility':10000}``
+
+    Examples::
+
+        >>> poly = Polygon([[0, 0], [1, 4], [2, 5]], {'density': 500})
+        >>> poly.props
+        {'density': 500}
+        >>> poly.nverts
+        3
+        >>> poly.vertices
+        array([[0, 0],
+               [1, 4],
+               [2, 5]])
+        >>> poly.x
+        array([0, 1, 2])
+        >>> poly.y
+        array([0, 4, 5])
+
+    """
+
+    def __init__(self, vertices, props=None):
+        super(Polygon, self).__init__(props)
+        self._vertices = numpy.asarray(vertices)
+
+    @property
+    def vertices(self):
+        return self._vertices
+
+    @property
+    def nverts(self):
+        return len(self.vertices)
+
+    @property
+    def x(self):
+        return self.vertices[:, 0]
+
+    @property
+    def y(self):
[…]

### 2017-02-23 code/mesher/test_oblate_ellipsoid.py

@@ -1,0 +1,26 @@
+from fatiando.mesher import OblateEllipsoid
+import numpy as np
+from numpy.random import rand
+
+
+def test_oblate_ellipsoid_copy():
+    orig = OblateEllipsoid(1, 2, 3, 4, 6, 10, 20, 30, {
+        'remanence': [10., 25., 40.],
+        'k': [0.562, 0.485, 0.25, 90., 34., 0.]})
+    cp = orig.copy()
+    assert orig is not cp
+    assert orig.x == cp.x
+    assert orig.y == cp.y
+    assert orig.z == cp.z
+    assert orig.a == cp.a
+    assert orig.b == cp.b
+    assert orig.props == cp.props
+
+    cp.x = 4
+    cp.y = 6
+    cp.z = 7
+    cp.props['remanence'] = [100., -40., -25.]
+    assert orig.x != cp.x
+    assert orig.y != cp.y
+    assert orig.z != cp.z
+    assert orig.props['remanence'] != cp.props['remanence']

### 2017-02-23 code/mesher/test_prolate_ellipsoid.py

@@ -1,0 +1,26 @@
+from fatiando.mesher import ProlateEllipsoid
+import numpy as np
+from numpy.random import rand
+
+
+def test_prolate_ellipsoid_copy():
+    orig = ProlateEllipsoid(1, 2, 3, 6, 4, 1, 29, 70, {
+                            'remanence': [8., 25., 40.],
+                            'k': [0.562, 0.485, 0.25, 90., 87., 0.]})
+    cp = orig.copy()
+    assert orig is not cp
+    assert orig.x == cp.x
+    assert orig.y == cp.y
+    assert orig.z == cp.z
+    assert orig.a == cp.a
+    assert orig.b == cp.b
+    assert orig.props == cp.props
+
+    cp.x = 4
+    cp.y = 6
+    cp.z = 7
+    cp.props['k'] = [0.7, 0.9, 10., 90., -10.]
+    assert orig.x != cp.x
+    assert orig.y != cp.y
+    assert orig.z != cp.z
+    assert orig.props['k'] != cp.props['k']

### 2017-02-23 code/mesher/test_triaxial_ellipsoid.py

@@ -1,0 +1,27 @@
+from fatiando.mesher import TriaxialEllipsoid
+import numpy as np
+from numpy.random import rand
+
+
+def test_triaxial_ellipsoid_copy():
+    orig = TriaxialEllipsoid(1, 2, 3, 6, 5, 4, 10, 20, 30, {
+                             'remanence': [10000., 25., 40.],
+                             'k': [0.562, 0.485, 0.25, 90., 0., 0.]})
+    cp = orig.copy()
+    assert orig is not cp
+    assert orig.x == cp.x
+    assert orig.y == cp.y
+    assert orig.z == cp.z
+    assert orig.a == cp.a
+    assert orig.b == cp.b
+    assert orig.c == cp.c
+    assert orig.props == cp.props
+
+    cp.x = 4
+    cp.y = 6
+    cp.z = 7
+    cp.props['k'] = [0.7, 0.9, 10., 90., 28., -10.]
+    assert orig.x != cp.x
+    assert orig.y != cp.y
+    assert orig.z != cp.z
+    assert orig.props['k'] != cp.props['k']

### 2017-02-23 code/oblate_ellipsoid.py

@@ -1,0 +1,941 @@
+r"""
+The potential fields of a homogeneous oblate ellipsoid.
+"""
+from __future__ import division
+
+import numpy as np
+
+from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS
+from .. import utils
+from .._our_duecredit import due, Doi
+
+
+due.cite(Doi("XXXXXXXXXXXXXXXXX"),
+         description='Forward modeling formula for oblate ellipsoids.',
+         path='fatiando.gravmag.oblate_ellipsoid')
+
+
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
+    r"""
+    The total-field anomaly produced by oblate ellipsoids
+    (Emerson et al., 1985).
+
+    .. math::
+
+        \Delta T = |\mathbf{T}| - |\mathbf{F}|,
+
+    where :math:`\mathbf{T}` is the measured field and :math:`\mathbf{F}` is
+    the local-geomagnetic field.
+
+    The anomaly of a homogeneous ellipsoid can be calculated as:
+
+    .. math::
+
+        \Delta T \approx \hat{\mathbf{F}}\cdot\mathbf{B}.
+
+    where :math:`\mathbf{B}` is the magnetic induction produced by the
+    ellipsoid.
+
+    The coordinate system of the input parameters is x -> North, y -> East and
+    z -> Down.
+
+    Input units should be SI. Output is in nT.
+
+    Parameters:
+
+    * xp, yp, zp : arrays
+        The x, y, and z coordinates where the anomaly will be calculated
+    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidOblate`
+        The ellipsoids. Ellipsoids must have the physical property
+        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
+        without ``'k'`` and ``'remanence'`` will be ignored.
+    * F, inc, dec : floats
+       The intensity (in nT), inclination and declination (in degrees) of
+       the local-geomagnetic field.
+    * pmag : [mx, my, mz] or None
+        A magnetization vector. If not None, will use this value instead
+        of the resultant magnetization of the ellipsoids. Use this, e.g.,
+        for sensitivity matrix building.
+
+    Returns:
+
+    * tf : array
+        The total-field anomaly
+
+    References:
+
+    Emerson, D. W., Clark, D., and Saul, S.: Magnetic exploration models
[…]

### 2017-02-23 code/plot_functions.py

@@ -1,0 +1,304 @@
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import numpy as np
+
+def draw_main_system(ax, length_axes = 1., label_size = 22, elev=200, azim=-20):
+    '''
+    Plot the axes forming the main coordinate system.
+    
+    input
+    ax: axes of a matplotlib figure.
+    length_axes: float - length of the axes (in meters).
+        Default is 1.
+    label_size: float - size of the label font. Default is 22.
+    elev and azim: floats - parameters controlling the view
+        of the figure. Default is 200 and -20, respectively.
+        
+    output
+    matplotlib objects
+    '''
+
+    # x-axis
+    ax.quiver(length_axes, 0., 0., length_axes, 0., 0., 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(1.05*length_axes, 0., 0., '$x$', color='k', fontsize=label_size)
+
+    # y-axis
+    ax.quiver(0., length_axes, 0., 0., length_axes, 0., 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(0., 1.05*length_axes, 0., '$y$', color='k', fontsize=label_size)
+
+    # z-axis
+    ax.quiver(0., 0., length_axes, 0., 0., length_axes, 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(0., 0., 1.05*length_axes, '$z$', color='k', fontsize=label_size)
+
+    ax.axis('off')
+
+    #ax.set_xlim(0., 1.1)
+    #ax.set_ylim(0., 1.1)
+    #ax.set_zlim(0., 1.1)
+
+    ax.view_init(elev=elev, azim=azim)
+    
+def draw_ellipsoid(ax, xc, yc, zc, a, b, c, strike, dip, rake,
+                   u, v, body_color, body_alpha,
+                   plot_axes=True, axes_color=(0,0,0), label_size=16):
+    '''
+    Plot an ellipsoidal body with axes a, b, c and
+    origin at (xc, yc, zc).
+    
+    input
+    ax: axes of a matplotlib figure.
[…]

### 2017-02-23 code/prolate_ellipsoid.py

@@ -1,0 +1,943 @@
+r"""
+The potential fields of a homogeneous prolate ellipsoid.
+"""
+from __future__ import division
+
+import numpy as np
+
+from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS
+from .. import utils
+from .._our_duecredit import due, Doi
+
+
+due.cite(Doi("XXXXXXXXXXXXXXXXX"),
+         description='Forward modeling formula for prolate ellipsoids.',
+         path='fatiando.gravmag.prolate_ellipsoid')
+
+
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
+    r"""
+    The total-field anomaly produced by prolate ellipsoids
+    (Emerson et al., 1985).
+
+    .. math::
+
+        \Delta T = |\mathbf{T}| - |\mathbf{F}|,
+
+    where :math:`\mathbf{T}` is the measured field and :math:`\mathbf{F}` is
+    the local-geomagnetic field.
+
+    The anomaly of a homogeneous ellipsoid can be calculated as:
+
+    .. math::
+
+        \Delta T \approx \hat{\mathbf{F}}\cdot\mathbf{B}.
+
+    where :math:`\mathbf{B}` is the magnetic induction produced by the
+    ellipsoid.
+
+    The coordinate system of the input parameters is x -> North, y -> East and
+    z -> Down.
+
+    Input units should be SI. Output is in nT.
+
+    Parameters:
+
+    * xp, yp, zp : arrays
+        The x, y, and z coordinates where the anomaly will be calculated
+    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidProlate`
+        The ellipsoids. Ellipsoids must have the physical property
+        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
+        without ``'k'`` and ``'remanence'`` will be ignored.
+    * F, inc, dec : floats
+       The intensity (in nT), inclination and declination (in degrees) of
+       the local-geomagnetic field.
+    * pmag : [mx, my, mz] or None
+        A magnetization vector. If not None, will use this value instead
+        of the resultant magnetization of the ellipsoids. Use this, e.g.,
+        for sensitivity matrix building.
+
+    Returns:
+
+    * tf : array
+        The total-field anomaly
+
+    References:
+
+    Emerson, D. W., Clark, D., and Saul, S.: Magnetic exploration models
[…]

### 2017-02-23 code/test_oblate_ellipsoid.py

@@ -1,0 +1,237 @@
+import numpy as np
+from numpy.random import rand
+
+from ... import utils, gridder
+from ...mesher import OblateEllipsoid
+from .. import oblate_ellipsoid
+
+F = 20000 + 40000*rand()
+inc = -90 + 180*rand()
+dec = 180*rand()
+sinc = -90 + 180*rand()
+sdec = 180*rand()
+
+gm = 1e4*rand()  # geometrical factor
+area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
+x, y, z = gridder.scatter(area, 300, z=0.)
+axis_ref = gm*rand()  # reference semi-axis
+
+model = [OblateEllipsoid(-3*gm, -3*gm, 3*axis_ref,
+                         0.6*axis_ref, axis_ref,
+                         180*rand(), 90*rand(), 90*rand(),
+                         {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
+         OblateEllipsoid(0, 0, 2*axis_ref,
+                         0.5*axis_ref, axis_ref,
+                         180*rand(), 90*rand(), 90*rand(),
+                         {'remanence': [4., 25., 40.],
+                          'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
+         OblateEllipsoid(3*gm, 3*gm, 3*axis_ref,
+                         0.3*axis_ref, axis_ref,
+                         180*rand(), 90*rand(), 90*rand(),
+                         {'remanence': [8., 25., 40.]})]
+
+
+def test_oblate_ellipsoid_force_prop():
+    "Test the oblate_ellipsoid code with forcing a physical property value"
+    pmag = utils.ang2vec(-1, sinc, sdec)
+    bx = oblate_ellipsoid.bx(x, y, z, model,
+                             F, inc, dec, pmag=pmag)
+    by = oblate_ellipsoid.by(x, y, z, model,
+                             F, inc, dec, pmag=pmag)
+    bz = oblate_ellipsoid.bz(x, y, z, model,
+                             F, inc, dec, pmag=pmag)
+    tf = oblate_ellipsoid.tf(x, y, z, model,
+                             F, inc, dec, pmag=pmag)
+    f = 1 + 4*rand()
+    bx2 = oblate_ellipsoid.bx(x, y, z, model,
+                              F, inc, dec, pmag=f*pmag)
+    by2 = oblate_ellipsoid.by(x, y, z, model,
[…]

### 2017-02-23 code/test_prolate_ellipsoid.py

@@ -1,0 +1,237 @@
+import numpy as np
+from numpy.random import rand
+
+from ... import utils, gridder
+from ...mesher import ProlateEllipsoid
+from .. import prolate_ellipsoid
+
+F = 20000 + 40000*rand()
+inc = -90 + 180*rand()
+dec = 180*rand()
+sinc = -90 + 180*rand()
+sdec = 180*rand()
+
+gm = 1e4*rand()  # geometrical factor
+area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
+x, y, z = gridder.scatter(area, 300, z=0.)
+axis_ref = gm*rand()  # reference semi-axis
+
+model = [ProlateEllipsoid(-3*gm, -3*gm, 3*axis_ref,
+                          axis_ref, 0.8*axis_ref,
+                          180*rand(), 90*rand(), 90*rand(),
+                          {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
+         ProlateEllipsoid(0, 0, 2*axis_ref,
+                          axis_ref, 0.6*axis_ref,
+                          180*rand(), 90*rand(), 90*rand(),
+                          {'remanence': [4., 25., 40.],
+                           'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
+         ProlateEllipsoid(3*gm, 3*gm, 3*axis_ref,
+                          axis_ref, 0.3*axis_ref,
+                          180*rand(), 90*rand(), 90*rand(),
+                          {'remanence': [8., 25., 40.]})]
+
+
+def test_prolate_ellipsoid_force_prop():
+    "Test the prolate_ellipsoid code with forcing a physical property value"
+    pmag = utils.ang2vec(-1, sinc, sdec)
+    bx = prolate_ellipsoid.bx(x, y, z, model,
+                              F, inc, dec, pmag=pmag)
+    by = prolate_ellipsoid.by(x, y, z, model,
+                              F, inc, dec, pmag=pmag)
+    bz = prolate_ellipsoid.bz(x, y, z, model,
+                              F, inc, dec, pmag=pmag)
+    tf = prolate_ellipsoid.tf(x, y, z, model,
+                              F, inc, dec, pmag=pmag)
+    f = 1 + 4*rand()
+    bx2 = prolate_ellipsoid.bx(x, y, z, model,
+                               F, inc, dec, pmag=f*pmag)
+    by2 = prolate_ellipsoid.by(x, y, z, model,
[…]

### 2017-02-23 code/test_triaxial_ellipsoid.py

@@ -1,0 +1,279 @@
+import numpy as np
+from numpy.random import rand
+
+from ... import utils, gridder
+from ...mesher import TriaxialEllipsoid
+from .. import triaxial_ellipsoid
+
+F = 20000 + 40000*rand()
+inc = -90 + 180*rand()
+dec = 180*rand()
+sinc = -90 + 180*rand()
+sdec = 180*rand()
+
+gm = 1e4*rand()  # geometrical factor
+area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
+x, y, z = gridder.scatter(area, 300, z=0.)
+axis_ref = gm*rand()  # reference semi-axis
+
+model = [TriaxialEllipsoid(-3*gm, -3*gm, 3*axis_ref,
+                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
+                           180*rand(), 90*rand(), 90*rand(),
+                           {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
+         TriaxialEllipsoid(0, 0, 2*axis_ref,
+                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
+                           180*rand(), 90*rand(), 90*rand(),
+                           {'remanence': [4., 25., 40.],
+                            'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
+         TriaxialEllipsoid(3*gm, 3*gm, 3*axis_ref,
+                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
+                           180*rand(), 90*rand(), 90*rand(),
+                           {'remanence': [8., 25., 40.]})]
+
+
+def test_triaxial_ellipsoid_force_prop():
+    "Test the triaxial_ellipsoid code with forcing a physical property value"
+    pmag = utils.ang2vec(-1, sinc, sdec)
+    bx = triaxial_ellipsoid.bx(x, y, z, model,
+                               F, inc, dec, pmag=pmag)
+    by = triaxial_ellipsoid.by(x, y, z, model,
+                               F, inc, dec, pmag=pmag)
+    bz = triaxial_ellipsoid.bz(x, y, z, model,
+                               F, inc, dec, pmag=pmag)
+    tf = triaxial_ellipsoid.tf(x, y, z, model,
+                               F, inc, dec, pmag=pmag)
+    f = 1 + 4*rand()
+    bx2 = triaxial_ellipsoid.bx(x, y, z, model,
[…]

### 2017-02-23 code/triaxial_ellipsoid.py

@@ -1,0 +1,1244 @@
+r"""
+The potential fields of a homogeneous triaxial ellipsoid.
+"""
+from __future__ import division
+
+import numpy as np
+from scipy.special import ellipeinc, ellipkinc
+
+from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS, PERM_FREE_SPACE
+from .. import utils
+from .._our_duecredit import due, Doi
+
+
+due.cite(Doi("XXXXXXXXXXXXXXXXX"),
+         description='Forward modeling formula for triaxial ellipsoids.',
+         path='fatiando.gravmag.triaxial_ellipsoid')
+
+
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
+    r"""
+    The total-field anomaly produced by triaxial ellipsoids
+    (Clark et al., 1986).
+
+    .. math::
+
+        \Delta T = |\mathbf{T}| - |\mathbf{F}|,
+
+    where :math:`\mathbf{T}` is the measured field and :math:`\mathbf{F}` is
+    the local-geomagnetic field.
+
+    The anomaly of a homogeneous ellipsoid can be calculated as:
+
+    .. math::
+
+        \Delta T \approx \hat{\mathbf{F}}\cdot\mathbf{B}.
+
+    where :math:`\mathbf{B}` is the magnetic induction produced by the
+    ellipsoid.
+
+    The coordinate system of the input parameters is x -> North, y -> East and
+    z -> Down.
+
+    Input units should be SI. Output is in nT.
+
+    Parameters:
+
+    * xp, yp, zp : arrays
+        The x, y, and z coordinates where the anomaly will be calculated
+    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidTriaxial`
+        The ellipsoids. Ellipsoids must have the physical property
+        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
+        without ``'k'`` and ``'remanence'`` will be ignored.
+    * F, inc, dec : floats
+       The intensity (in nT), inclination and declination (in degrees) of
+       the local-geomagnetic field.
+    * dmag : boolean
+        If True, will include the self-demagnetization.
+    * pmag : [mx, my, mz] or None
+        A magnetization vector. If not None, will use this value instead
+        of the resultant magnetization of the ellipsoids. Use this, e.g.,
+        for sensitivity matrix building.
+
[…]

### 2017-02-23 manuscript/manuscript.tex
include the abstract and acknowledgments

@@
 
-\correspondence{Diego Takahashi Tomazella (diego.takahashi@gmail.com)}
+\correspondence{Vanderlei C. Oliveira Jr. (vandscoelho@gmail.com)}
 
@@
 
-A considerable amount of literature has been published on
-the magnetic modelling of of uniformly magnetized ellipsoids
-since the second half of the nineteenth century.
+A considerable amount of literature has been published on the magnetic 
+modelling of uniformly magnetized ellipsoids since the second half of 
+the nineteenth century. Ellipsoids have flexibility to represent a wide 
+range of geometrical forms, are the only known bodies which can be 
+uniformly magnetized in the presence of a uniform inducing field and 
+are the only bodies for which the self-demagnetization can be treated 
+analytically. This property makes ellipsoids particularly useful for 
+modelling compact orebodies having high susceptibility. In this case, 
+neglecting the self-demagnetization may strongly mislead the interpretation 
+of these bodies by using magnetic methods. A number of previous studies 
+consider that the self-demagnetization can be neglected for the case in 
+which the geological body has an isotropic susceptibility lower than or 
+equal to 0.1 SI. This limiting value, however, seems to be determined 
+empirically and there has been no discussion about how this value was 
+determined. Besides, the geoscientific community lacks an easy-to-use 
+tool to simulate the magnetic field produced by uniformly magnetized 
+ellipsoids. Here, we present an integrated review of the magnetic 
+modelling of arbitrarily oriented triaxial, prolate and oblate 
+ellipsoids which have both induced and remanent magnetization, as 
+well as isotropic or anisotropic susceptibility. We also propose a 
+way of determining the isotropic susceptibility above which the 
+self-demagnetization must be taken into consideration. Tests with 
+synthetic data validate our approach. Finally, we provide a set 
+of routines a set of routines to model the magnetic field produced 
+by ellipsoids. The routines are written in Python language as 
+part of the Fatiando a Terra, which is an open-source library 
+for modelling and inversion in geophysics.
 
@@
 \begin{acknowledgements}
-TEXT
+
+D. T. Tomazella thanks the brazilian research founding agency 
+Conselho Nacional de 
+Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq)
+for providing financial support in the form of a scholarship. 
+Oliveira Jr. thanks the brazilian research founding agency 
+Conselho Nacional de Desenvolvimento Cient\'{i}fico e 
+Tecnol\'{o}gico (CNPq) for providing 
+financial support in the form of a grant (445752/2014-9).
+
 \end{acknowledgements}

### 2017-03-03 code/mesher/mesher.py
combine the meshser tests in a single file and review the mesher documentation

@@ -1722,10 +1722,24 @@ def vremove(value, prop, cells):
     return [c for c in cells if keep(c)]
 
 
-class TriaxialEllipsoid (GeometricElement):
+class TriaxialEllipsoid(GeometricElement):
 
     """
-    Create a triaxial ellipsoid.
+    Create an arbitrarily-oriented triaxial ellipsoid.
+
+    Triaxial ellipsoids are those having different semi-axes.
+    This code follows Clark et al. (1986) and defines the spatial
+    orientation of the ellipsoid by using three angles: strike,
+    rake and dip. These angles are commonly used to define the
+    orientation of geological structures (Allmendinger et al., 2012).
+
+    References:
+
+    Allmendinger, R., Cardozo, N., and Fisher, D. M.: Structural geology
+    algorithms : vectors and tensors, Cambridge University Press, 2012.
+
+    Clark, D., Saul, S., and Emerson, D.: Magnetic and gravity anomalies
+    of a triaxial ellipsoid, Exploration Geophysics, 17, 189-200, 1986.
 
     .. note:: The coordinate system used is x -> North, y -> East
     and z -> Down
@@ -1734,56 +1748,64 @@ class TriaxialEllipsoid (GeometricElement):
 
     * x, y, z : float
         The coordinates of the center of the ellipsoid.
-    * a, b, c : float
-        Semi-axes of the ellipsoid (a>b>c)
+    * large_axis, intermediate_axis, small_axis: float
+        Semi-axes forming the ellipsoid.
     * strike, dip, rake
         Orientation angles of the ellipsoid.
     * props : dict
         Physical properties assigned to the ellipsoid.
         Ex: ``props={'density':10,
-                     'remanence':[10., 25., 40.],
-                     'k':[0.562, 0.485, 0.25, 90., 0., 0.]}``
+                     'remanent magnetization':[10, 25, 40],
+                     'susceptibility tensor':[0.562, 0.485, 0.25,
+                                              90, 0, 0]}``
 
     Examples:
 
-        >>> e = TriaxialEllipsoid(1, 2, 3, 6, 5, 4, 10, 20, 30,{
-        ...                       'remanence': [10., 25., 40.],
-        ...                       'k': [0.562, 0.485, 0.25, 90., 0., 0.]})
-        >>> e.props['remanence']
-        [10.0, 25.0, 40.0]
[…]

### 2017-03-03 code/mesher/test_prolate_ellipsoid.py

@@ -1,26 +1,0 @@
-from fatiando.mesher import ProlateEllipsoid
-import numpy as np
-from numpy.random import rand
-
-
-def test_prolate_ellipsoid_copy():
-    orig = ProlateEllipsoid(1, 2, 3, 6, 4, 1, 29, 70, {
-                            'remanence': [8., 25., 40.],
-                            'k': [0.562, 0.485, 0.25, 90., 87., 0.]})
-    cp = orig.copy()
-    assert orig is not cp
-    assert orig.x == cp.x
-    assert orig.y == cp.y
-    assert orig.z == cp.z
-    assert orig.a == cp.a
-    assert orig.b == cp.b
-    assert orig.props == cp.props
-
-    cp.x = 4
-    cp.y = 6
-    cp.z = 7
-    cp.props['k'] = [0.7, 0.9, 10., 90., -10.]
-    assert orig.x != cp.x
-    assert orig.y != cp.y
-    assert orig.z != cp.z
-    assert orig.props['k'] != cp.props['k']

### 2017-03-03 manuscript/manuscript.tex

@@
 modelling of arbitrarily oriented triaxial, prolate and oblate 
-ellipsoids which have both induced and remanent magnetization, as 
-well as isotropic or anisotropic susceptibility. We also propose a 
+ellipsoids. Our review includes ellipsoids with both induced and 
+remanent magnetization, as well as with isotropic or anisotropic 
+susceptibility. We also propose a 
 way of determining the isotropic susceptibility above which the 
@@
 synthetic data validate our approach. Finally, we provide a set 
-of routines a set of routines to model the magnetic field produced 
+of routines to model the magnetic field produced 
 by ellipsoids. The routines are written in Python language as 

### 2017-03-15 manuscript/manuscript.tex
define the V matrix for prolate ellipsoids equal to that used for triaxial ellipsoids

@@
 (Fig. \ref{fig:orientation-angles}b) according to the ellipsoid type.
-For triaxial ellipsoids (i.e., $a > b > c$), these unit vectors are 
-given by \citep{clark1986}:
+For triaxial ellipsoids (i.e., $a > b > c$) and prolate ellipsoids
+(i.e., $a > b = c$), these unit vectors may be given by \citep{clark1986}:
 \begin{equation}
@@
 \end{equation}
-Similarly, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-for prolate ellipsoids (i.e., $a > b = c$) are calculated
-by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
-\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$
-\citep{emerson1985}.
+\citet{emerson1985} also calculate the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
+and $\mathbf{v}_{3}$ by using Eqs. \ref{eq:v1_triaxial_prolate},
+\ref{eq:v2_triaxial_prolate}, and \ref{eq:v3_triaxial_prolate}, but
+with $\gamma = 0^{\circ}$.
 Finally, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-for oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
+for oblate ellipsoids (i.e., $a < b = c$) may be calculated as follows:
 \begin{equation}
@@
 \end{equation}
-These formulas are similar to those presented by \citep{emerson1985}.
 

### 2017-03-15 manuscript/manuscript.tex
modify small parts of text and review the mesher for fatiando

@@
 $0 \leq \delta \leq 90^{\circ}$.
-Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a and Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
-\ref{eq:delta}), we define the unit vectors
+Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ 
+(Fig. \ref{fig:orientation-angles}a), we define the auxiliary angles 
+$\alpha$, $\gamma$ and $\delta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
+\ref{eq:delta}) and, finally, the unit vectors
 $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
@@
 For triaxial ellipsoids (i.e., $a > b > c$) and prolate ellipsoids
-(i.e., $a > b = c$), these unit vectors may be given by \citep{clark1986}:
+(i.e., $a > b = c$), we opted for defining these unit vectors 
+by following \citet{clark1986}:
 \begin{equation}
@@
 \end{equation}
-\citet{emerson1985} also calculate the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
-and $\mathbf{v}_{3}$ by using Eqs. \ref{eq:v1_triaxial_prolate},
+\citet{emerson1985} calculated the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
+and $\mathbf{v}_{3}$ similarly by using Eqs. \ref{eq:v1_triaxial_prolate},
 \ref{eq:v2_triaxial_prolate}, and \ref{eq:v3_triaxial_prolate}, but
 with $\gamma = 0^{\circ}$.
-Finally, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-for oblate ellipsoids (i.e., $a < b = c$) may be calculated as follows:
+Finally, we define the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
+and $\mathbf{v}_{3}$ for oblate ellipsoids (i.e., $a < b = c$) as follows:
 \begin{equation}
@@
 \end{equation}
+This approach is very similar to that presented by \citet{emerson1985}.
 
@@
 the total magnetic field $\mathbf{H}(\mathbf{r})$
-at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
-\ref{eq:coord_transformation}) of a point referred to the main 
+at the position $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}) 
+of a point referred to the main 
 coordinate system is defined as follows \citep{sharma1966, 
@@
 $\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
-(in $\unit{Am^{-1}}$).
+(in \unit{Am^{-1}}).
 Eq. \ref{eq:V-potential} is valid anywhere, 
@@
 subjected to an inducing field $\mathbf{H}_{0}$ with 
-strength $\leq 1$ \unit{mT} \citep{rochette1992}.
+strength $\leq 10^{-3} \mu_{0}^{-1}$ \unit{A \, m^{-1}} \citep{rochette1992},
+where $\mu_{0}$ represents the magnetic constant (in \unit{H \, m^{-1}}).
 In this case, the susceptibility tensor $\mathbf{K}$ is commonly

### 2017-03-15 code/mesher/mesher.py

@@ -1,7 +1,8 @@
 """
 Generate and operate on various kinds of meshes and geometric elements
 """
-from __future__ import division
+from __future__ import division, absolute_import
+from future.builtins import range
 import numpy
 import scipy.special
 import scipy.interpolate
@@ -1154,8 +1155,8 @@ class PrismMesh(object):
     def __init__(self, bounds, shape, props=None):
         object.__init__(self)
         nz, ny, nx = shape
-        if (not isinstance(nx, int) or not isinstance(ny, int)
-                or not isinstance(nz, int)):
+        if not isinstance(nx, int) or not isinstance(ny, int) or \
+                not isinstance(nz, int):
             raise AttributeError(
                 'Invalid mesh shape {}. shape must be integers'.format(
                     str(shape)))
@@ -1279,7 +1280,7 @@ class PrismMesh(object):
         if numpy.ma.isMA(topo):
             topo_mask = topo.mask
         else:
-            topo_mask = [False for i in xrange(len(topo))]
+            topo_mask = [False for i in range(len(topo))]
         c = 0
         for cellz in zc:
             for h, masked in zip(topo, topo_mask):
@@ -1370,7 +1371,7 @@ class PrismMesh(object):
             raise IndexError('Layer index %d is out of range.' % (i))
         start = i * nx * ny
         end = (i + 1) * nx * ny
-        layer = [self.__getitem__(p) for p in xrange(start, end)]
+        layer = [self.__getitem__(p) for p in range(start, end)]
         return layer
 
     def layers(self):
@@ -1394,7 +1395,7 @@ class PrismMesh(object):
 
         """
         nz, ny, nx = self.shape
-        for i in xrange(nz):
+        for i in range(nz):
             yield self.get_layer(i)
 
     def dump(self, meshfile, propfile, prop):
@@ -1749,9 +1750,9 @@ class TriaxialEllipsoid(GeometricElement):
     * x, y, z : float
         The coordinates of the center of the ellipsoid.
     * large_axis, intermediate_axis, small_axis: float
-        Semi-axes forming the ellipsoid.
+        Semi-axes forming the ellipsoid (in m).
     * strike, dip, rake
-        Orientation angles of the ellipsoid.
+        Orientation angles of the ellipsoid (in degrees).
     * props : dict
         Physical properties assigned to the ellipsoid.
         Ex: ``props={'density':10,
[…]

### 2017-03-15 code/mesher/test_ellipsoids.py

@@ -1,5 +1,10 @@
+from __future__ import division, absolute_import
 from ...mesher import TriaxialEllipsoid, ProlateEllipsoid, OblateEllipsoid
+from ...mesher import coord_transf_matrix_triaxial, coord_transf_matrix_oblate
+from ...mesher import auxiliary_angles
 import numpy as np
+from numpy.testing import assert_almost_equal
+from pytest import raises
 
 
 def test_triaxial_ellipsoid_copy():
@@ -29,6 +34,71 @@ def test_triaxial_ellipsoid_copy():
         cp.props['susceptibility tensor']
 
 
+def test_triaxial_ellipsoid_axes():
+    'axes must be given in descending order'
+    raises(AssertionError, TriaxialEllipsoid, x=1, y=2, z=3,
+           large_axis=6, intermediate_axis=5, small_axis=14,
+           strike=10, dip=20, rake=30)
+
+
+def test_triaxial_ellipsoid_susceptibility_tensor_fmt():
+    'susceptibility tensor must be a list containing 6 elements'
+    e = TriaxialEllipsoid(x=1, y=2, z=3, large_axis=6,
+                          intermediate_axis=5, small_axis=4,
+                          strike=10, dip=20, rake=30,
+                          props={'remanent magnetization': [10, 25, 40],
+                                 'susceptibility tensor': [0.562, 0.485,
+                                                           0.25, 90, 0]})
+    with raises(AssertionError):
+        e.susceptibility_tensor()
+
+
+def test_triaxial_ellipsoid_principal_susceptibilities_order():
+    'principal susceptibilities must be given in descending order'
+    e = TriaxialEllipsoid(x=1, y=2, z=3, large_axis=6,
+                          intermediate_axis=5, small_axis=4,
+                          strike=10, dip=20, rake=30,
+                          props={'remanent magnetization': [10, 25, 40],
+                                 'susceptibility tensor': [0.1, 0.485,
+                                                           0.25, 90, 0, 6]})
+    with raises(AssertionError):
+        e.susceptibility_tensor()
+
+
+def test_triaxial_ellipsoid_principal_susceptibilities_signal():
+    'principal susceptibilities must be all positive'
+    e = TriaxialEllipsoid(x=1, y=2, z=3, large_axis=6,
+                          intermediate_axis=5, small_axis=4,
[…]

### 2017-03-15 code/triaxial_ellipsoid.py

@@ -490,127 +490,6 @@ def _bz(xp, yp, zp, ellipsoid, F, inc, dec, dmag=True, pmag=None):
     return res
 
 
-def structural_angles(strike, dip, rake):
-    '''
-    Calculates the orientation angles alpha, gamma
-    and delta (Clark et al., 1986)
-    as functions of the geological angles strike, dip and
-    rake (Clark et al., 1986; Allmendinger et al., 2012).
-    The function implements the formulas presented by
-    Clark et al. (1986).
-
-    Parameters:
-
-    *strike: float
-             strike direction (in degrees).
-    *dip: float
-          true dip (in degrees).
-    *rake: float
-           angle between the strike and the semi-axis a
-           of the body (in degrees).
-
-    Returns:
-
-    *alpha, gamma, delta: float, float, float
-            orientation angles (in radians) defined according
-            to Clark et al. (1986).
-
-    References:
-
-    Clark, D., Saul, S., and Emerson, D.: Magnetic and gravity anomalies
-    of a triaxial ellipsoid, Exploration Geophysics, 17, 189-200, 1986.
-
-    Allmendinger, R., Cardozo, N., and Fisher, D. M.:
-    Structural geology algorithms : vectors and tensors,
-    Cambridge University Press, 2012.
-    '''
-
-    strike_r = np.deg2rad(strike)
-    cos_dip = np.cos(np.deg2rad(dip))
-    sin_dip = np.sin(np.deg2rad(dip))
-    cos_rake = np.cos(np.deg2rad(rake))
-    sin_rake = np.sin(np.deg2rad(rake))
-
-    aux = sin_dip*sin_rake
-    aux1 = cos_rake/np.sqrt(1 - aux*aux)
-    aux2 = sin_dip*cos_rake
-
-    if aux1 > 1.:
-        aux1 = 1.
-    if aux1 < -1.:
-        aux1 = -1.
-
-    alpha = strike_r - np.arccos(aux1)
-    if aux2 != 0:
-        gamma = -np.arctan(cos_dip/aux2)
-    else:
-        if cos_dip >= 0:
-            gamma = np.pi/2
-        if cos_dip <= 0:
-            gamma = -np.pi/2
-    delta = np.arcsin(aux)
-
-    assert delta <= np.pi/2, 'delta must be lower than \
-or equalt to 90 degrees'
-
[…]

### 2017-03-16 code/triaxial_ellipsoid.py
edit gravmag triaxial ellipsoid according to the new mesher code

@@ -18,8 +18,7 @@ due.cite(Doi("XXXXXXXXXXXXXXXXX"),
 
 def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
     r"""
-    The total-field anomaly produced by triaxial ellipsoids
-    (Clark et al., 1986).
+    The total-field anomaly produced by triaxial ellipsoids.
 
     .. math::
 
@@ -37,6 +36,8 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
     where :math:`\mathbf{B}` is the magnetic induction produced by the
     ellipsoid.
 
+    This code follows the approach presented by Clark et al. (1986).
+
     The coordinate system of the input parameters is x -> North, y -> East and
     z -> Down.
 
@@ -45,11 +46,12 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
     Parameters:
 
     * xp, yp, zp : arrays
-        The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidTriaxial`
+        The x, y, and z coordinates where the anomaly will be calculated.
+    * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical property
-        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
-        without ``'k'`` and ``'remanence'`` will be ignored.
+        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
+        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
+        and without ``'remanent magnetization'`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -57,7 +59,7 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
         If True, will include the self-demagnetization.
     * pmag : [mx, my, mz] or None
         A magnetization vector. If not None, will use this value instead
-        of the resultant magnetization of the ellipsoids. Use this, e.g.,
[…]

### 2017-03-16 code/oblate_ellipsoid.py
new gravmag files with tests and commands for running flake8 and pytest

@@ -1,24 +1,17 @@
 r"""
 The potential fields of a homogeneous oblate ellipsoid.
 """
-from __future__ import division
+from __future__ import division, absolute_import
 
 import numpy as np
 
-from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS
-from .. import utils
-from .._our_duecredit import due, Doi
+from fatiando.constants import CM, T2NT
+from fatiando import utils
 
 
-due.cite(Doi("XXXXXXXXXXXXXXXXX"),
-         description='Forward modeling formula for oblate ellipsoids.',
-         path='fatiando.gravmag.oblate_ellipsoid')
-
-
-def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     r"""
-    The total-field anomaly produced by oblate ellipsoids
-    (Emerson et al., 1985).
+    The total-field anomaly produced by oblate ellipsoids.
 
     .. math::
 
@@ -36,6 +29,8 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
     where :math:`\mathbf{B}` is the magnetic induction produced by the
     ellipsoid.
 
+    This code follows the approach presented by Emerson et al. (1985).
+
     The coordinate system of the input parameters is x -> North, y -> East and
     z -> Down.
 
@@ -44,17 +39,20 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
     Parameters:
 
     * xp, yp, zp : arrays
-        The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidOblate`
+        The x, y, and z coordinates where the anomaly will be calculated.
+    * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical property
-        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
-        without ``'k'`` and ``'remanence'`` will be ignored.
+        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
+        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
+        and without ``'remanent magnetization'`` will be ignored.
     * F, inc, dec : floats
[…]

### 2017-03-16 code/prolate_ellipsoid.py

@@ -1,24 +1,17 @@
 r"""
 The potential fields of a homogeneous prolate ellipsoid.
 """
-from __future__ import division
+from __future__ import division, absolute_import
 
 import numpy as np
 
-from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS
-from .. import utils
-from .._our_duecredit import due, Doi
+from fatiando.constants import CM, T2NT
+from fatiando import utils
 
 
-due.cite(Doi("XXXXXXXXXXXXXXXXX"),
-         description='Forward modeling formula for prolate ellipsoids.',
-         path='fatiando.gravmag.prolate_ellipsoid')
-
-
-def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     r"""
-    The total-field anomaly produced by prolate ellipsoids
-    (Emerson et al., 1985).
+    The total-field anomaly produced by prolate ellipsoids.
 
     .. math::
 
@@ -36,6 +29,8 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
     where :math:`\mathbf{B}` is the magnetic induction produced by the
     ellipsoid.
 
+    This code follows the approach presented by Emerson et al. (1985).
+
     The coordinate system of the input parameters is x -> North, y -> East and
     z -> Down.
 
@@ -44,17 +39,20 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, pmag=None):
     Parameters:
 
     * xp, yp, zp : arrays
-        The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.EllipsoidProlate`
+        The x, y, and z coordinates where the anomaly will be calculated.
+    * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical property
-        ``'k'`` and/or ``'remanence'``. Ellipsoids that are ``None`` or
-        without ``'k'`` and ``'remanence'`` will be ignored.
+        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
+        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
+        and without ``'remanent magnetization'`` will be ignored.
     * F, inc, dec : floats
[…]

### 2017-03-16 code/test_oblate_ellipsoid.py

@@ -1,237 +1,287 @@
+from __future__ import division, absolute_import
 import numpy as np
-from numpy.random import rand
+from copy import deepcopy
 
-from ... import utils, gridder
-from ...mesher import OblateEllipsoid
-from .. import oblate_ellipsoid
+from fatiando import utils, gridder
+from fatiando.mesher import OblateEllipsoid
+from fatiando.gravmag import oblate_ellipsoid
+from numpy.testing import assert_almost_equal
+from pytest import raises
 
-F = 20000 + 40000*rand()
-inc = -90 + 180*rand()
-dec = 180*rand()
-sinc = -90 + 180*rand()
-sdec = 180*rand()
+# Local-geomagnetic field
+F = 30000
+inc = 2
+dec = -27
 
-gm = 1e4*rand()  # geometrical factor
+gm = 1000  # geometrical factor
 area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
 x, y, z = gridder.scatter(area, 300, z=0.)
-axis_ref = gm*rand()  # reference semi-axis
+axis_ref = gm  # reference semi-axis
 
-model = [OblateEllipsoid(-3*gm, -3*gm, 3*axis_ref,
-                         0.6*axis_ref, axis_ref,
-                         180*rand(), 90*rand(), 90*rand(),
-                         {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
-         OblateEllipsoid(0, 0, 2*axis_ref,
-                         0.5*axis_ref, axis_ref,
-                         180*rand(), 90*rand(), 90*rand(),
-                         {'remanence': [4., 25., 40.],
-                          'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
-         OblateEllipsoid(3*gm, 3*gm, 3*axis_ref,
-                         0.3*axis_ref, axis_ref,
-                         180*rand(), 90*rand(), 90*rand(),
-                         {'remanence': [8., 25., 40.]})]
+# Prolate ellipsoids used for testing
+model = [OblateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
+                           small_axis=0.6*axis_ref,
+                           large_axis=axis_ref,
+                           strike=78, dip=92, rake=135,
+                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
+                                                            90., 47., 13.]}),
+         OblateEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
+                           small_axis=0.3*axis_ref,
[…]

### 2017-03-16 code/test_prolate_ellipsoid.py

@@ -1,237 +1,287 @@
+from __future__ import division, absolute_import
 import numpy as np
-from numpy.random import rand
+from copy import deepcopy
 
-from ... import utils, gridder
-from ...mesher import ProlateEllipsoid
-from .. import prolate_ellipsoid
+from fatiando import utils, gridder
+from fatiando.mesher import ProlateEllipsoid
+from fatiando.gravmag import prolate_ellipsoid
+from numpy.testing import assert_almost_equal
+from pytest import raises
 
-F = 20000 + 40000*rand()
-inc = -90 + 180*rand()
-dec = 180*rand()
-sinc = -90 + 180*rand()
-sdec = 180*rand()
+# Local-geomagnetic field
+F = 30000
+inc = 2
+dec = -27
 
-gm = 1e4*rand()  # geometrical factor
+gm = 1000  # geometrical factor
 area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
 x, y, z = gridder.scatter(area, 300, z=0.)
-axis_ref = gm*rand()  # reference semi-axis
+axis_ref = gm  # reference semi-axis
 
-model = [ProlateEllipsoid(-3*gm, -3*gm, 3*axis_ref,
-                          axis_ref, 0.8*axis_ref,
-                          180*rand(), 90*rand(), 90*rand(),
-                          {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
-         ProlateEllipsoid(0, 0, 2*axis_ref,
-                          axis_ref, 0.6*axis_ref,
-                          180*rand(), 90*rand(), 90*rand(),
-                          {'remanence': [4., 25., 40.],
-                           'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
-         ProlateEllipsoid(3*gm, 3*gm, 3*axis_ref,
-                          axis_ref, 0.3*axis_ref,
-                          180*rand(), 90*rand(), 90*rand(),
-                          {'remanence': [8., 25., 40.]})]
+# Prolate ellipsoids used for testing
+model = [ProlateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
+                           large_axis=axis_ref,
+                           small_axis=0.6*axis_ref,
+                           strike=78, dip=92, rake=135,
+                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
+                                                            90., 47., 13.]}),
[…]

### 2017-03-16 code/test_triaxial_ellipsoid.py

@@ -1,39 +1,55 @@
+from __future__ import division, absolute_import
 import numpy as np
-from numpy.random import rand
+from copy import deepcopy
 
-from ... import utils, gridder
-from ...mesher import TriaxialEllipsoid
-from .. import triaxial_ellipsoid
+from fatiando import utils, gridder
+from fatiando.mesher import TriaxialEllipsoid
+from fatiando.gravmag import triaxial_ellipsoid
+from numpy.testing import assert_almost_equal
+from pytest import raises
 
-F = 20000 + 40000*rand()
-inc = -90 + 180*rand()
-dec = 180*rand()
-sinc = -90 + 180*rand()
-sdec = 180*rand()
+# Local-geomagnetic field
+F = 30000
+inc = -3
+dec = 57
 
-gm = 1e4*rand()  # geometrical factor
+gm = 1000  # geometrical factor
 area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
 x, y, z = gridder.scatter(area, 300, z=0.)
-axis_ref = gm*rand()  # reference semi-axis
+axis_ref = gm  # reference semi-axis
 
-model = [TriaxialEllipsoid(-3*gm, -3*gm, 3*axis_ref,
-                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
-                           180*rand(), 90*rand(), 90*rand(),
-                           {'k': [0.7, 0.7, 0.7, 90., 47., 13.]}),
-         TriaxialEllipsoid(0, 0, 2*axis_ref,
-                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
-                           180*rand(), 90*rand(), 90*rand(),
-                           {'remanence': [4., 25., 40.],
-                            'k': [0.562, 0.485, 0.25, 90., 0., 0.]}),
-         TriaxialEllipsoid(3*gm, 3*gm, 3*axis_ref,
-                           axis_ref, 0.8*axis_ref, 0.6*axis_ref,
-                           180*rand(), 90*rand(), 90*rand(),
-                           {'remanence': [8., 25., 40.]})]
+# Triaxial ellipsoids used for testing
+model = [TriaxialEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
+                           large_axis=axis_ref,
+                           intermediate_axis=0.8*axis_ref,
+                           small_axis=0.6*axis_ref,
+                           strike=78, dip=92, rake=135,
+                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
[…]

### 2017-03-16 code/triaxial_ellipsoid.py

@@ -1,22 +1,16 @@
 r"""
 The potential fields of a homogeneous triaxial ellipsoid.
 """
-from __future__ import division
+from __future__ import division, absolute_import
 
 import numpy as np
 from scipy.special import ellipeinc, ellipkinc
 
-from ..constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS, PERM_FREE_SPACE
-from .. import utils
-from .._our_duecredit import due, Doi
+from fatiando.constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS, PERM_FREE_SPACE
+from fatiando import utils
 
 
-due.cite(Doi("XXXXXXXXXXXXXXXXX"),
-         description='Forward modeling formula for triaxial ellipsoids.',
-         path='fatiando.gravmag.triaxial_ellipsoid')
-
-
-def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
+def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     r"""
     The total-field anomaly produced by triaxial ellipsoids.
 
@@ -55,7 +49,7 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
-    * dmag : boolean
+    * demag : boolean
         If True, will include the self-demagnetization.
     * pmag : [mx, my, mz] or None
         A magnetization vector. If not None, will use this value instead
@@ -74,14 +68,14 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, dmag=True, pmag=None):
 
     """
     fx, fy, fz = utils.dircos(inc, dec)
-    Bx = bx(xp, yp, zp, ellipsoids, F, inc, dec, dmag, pmag)
-    By = by(xp, yp, zp, ellipsoids, F, inc, dec, dmag, pmag)
-    Bz = bz(xp, yp, zp, ellipsoids, F, inc, dec, dmag, pmag)
+    Bx = bx(xp, yp, zp, ellipsoids, F, inc, dec, demag, pmag)
+    By = by(xp, yp, zp, ellipsoids, F, inc, dec, demag, pmag)
+    Bz = bz(xp, yp, zp, ellipsoids, F, inc, dec, demag, pmag)
 
[…]

### 2017-03-16 code/mesher.py
create a Makefile for checking style and testing

@@ -1,14 +1,9 @@
 """
-Generate and operate on various kinds of meshes and geometric elements
+Generate and operate geometric elements
 """
 from __future__ import division, absolute_import
-from future.builtins import range
 import numpy
-import scipy.special
-import scipy.interpolate
 import copy as cp
-
-from . import gridder
 
 
 class GeometricElement(object):
@@ -43,1684 +38,6 @@ class GeometricElement(object):
     def copy(self):
         """ Return a deep copy of the current instance."""
         return cp.deepcopy(self)
-
-
-class Polygon(GeometricElement):
-
-    """
-    Create a polygon object.
-
-    .. note:: Most applications require the vertices to be **clockwise**!
-
-    Parameters:
-
-    * vertices : list of lists
-        List of [x, y] pairs with the coordinates of the vertices.
-    * props : dict
-        Physical properties assigned to the polygon.
-        Ex: ``props={'density':10, 'susceptibility':10000}``
-
-    Examples::
-
-        >>> poly = Polygon([[0, 0], [1, 4], [2, 5]], {'density': 500})
-        >>> poly.props
-        {'density': 500}
-        >>> poly.nverts
-        3
-        >>> poly.vertices
-        array([[0, 0],
-               [1, 4],
-               [2, 5]])
-        >>> poly.x
-        array([0, 1, 2])
-        >>> poly.y
-        array([0, 4, 5])
-
-    """
-
-    def __init__(self, vertices, props=None):
-        super(Polygon, self).__init__(props)
-        self._vertices = numpy.asarray(vertices)
-
-    @property
-    def vertices(self):
-        return self._vertices
-
-    @property
-    def nverts(self):
-        return len(self.vertices)
-
-    @property
-    def x(self):
-        return self.vertices[:, 0]
-
-    @property
-    def y(self):
-        return self.vertices[:, 1]
-
-
-class Square(Polygon):
-
-    """
-    Create a square object.
-
-    Parameters:
-
-    * bounds : list = [x1, x2, y1, y2]
-        Coordinates of the top right and bottom left corners of the square
-    * props : dict
-        Physical properties assigned to the square.
-        Ex: ``props={'density':10, 'slowness':10000}``
-
-    Example::
-
-        >>> sq = Square([0, 1, 2, 4], {'density': 750})
-        >>> sq.bounds
-        [0, 1, 2, 4]
[…]

### 2017-03-16 code/test_ellipsoids.py

@@ -1,7 +1,10 @@
 from __future__ import division, absolute_import
-from ...mesher import TriaxialEllipsoid, ProlateEllipsoid, OblateEllipsoid
-from ...mesher import coord_transf_matrix_triaxial, coord_transf_matrix_oblate
-from ...mesher import auxiliary_angles
+from mesher import TriaxialEllipsoid
+from mesher import ProlateEllipsoid
+from mesher import OblateEllipsoid
+from mesher import coord_transf_matrix_triaxial
+from mesher import coord_transf_matrix_oblate
+from mesher import auxiliary_angles
 import numpy as np
 from numpy.testing import assert_almost_equal
 from pytest import raises

### 2017-03-16 code/test_oblate_ellipsoid.py

@@ -3,10 +3,9 @@ import numpy as np
 from copy import deepcopy
 
 from fatiando import utils, gridder
-from fatiando.mesher import OblateEllipsoid
-from fatiando.gravmag import oblate_ellipsoid
+from mesher import OblateEllipsoid
+import oblate_ellipsoid
 from numpy.testing import assert_almost_equal
-from pytest import raises
 
 # Local-geomagnetic field
 F = 30000
@@ -20,23 +19,23 @@ axis_ref = gm  # reference semi-axis
 
 # Prolate ellipsoids used for testing
 model = [OblateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
-                           small_axis=0.6*axis_ref,
-                           large_axis=axis_ref,
-                           strike=78, dip=92, rake=135,
-                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
-                                                            90., 47., 13.]}),
+                         small_axis=0.6*axis_ref,
+                         large_axis=axis_ref,
+                         strike=78, dip=92, rake=135,
+                         props={'susceptibility tensor': [0.7, 0.7, 0.7,
+                                                          90., 47., 13.]}),
          OblateEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
-                           small_axis=0.3*axis_ref,
-                           large_axis=1.1*axis_ref,
-                           strike=4, dip=10, rake=5,
-                           props={'susceptibility tensor': [0.2, 0.15, 0.05,
-                                                            180, 19, -8.],
-                                  'remanent magnetization': [3, -6, 35]}),
+                         small_axis=0.3*axis_ref,
+                         large_axis=1.1*axis_ref,
+                         strike=4, dip=10, rake=5,
+                         props={'susceptibility tensor': [0.2, 0.15, 0.05,
+                                                          180, 19, -8.],
+                                'remanent magnetization': [3, -6, 35]}),
          OblateEllipsoid(x=3*gm, y=3*gm, z=4*axis_ref,
-                           small_axis=0.6*axis_ref,
-                           large_axis=1.5*axis_ref,
-                           strike=-58, dip=87, rake=49,
-                           props={'remanent magnetization': [4.7, 39, 0]})]
+                         small_axis=0.6*axis_ref,
+                         large_axis=1.5*axis_ref,
[…]

### 2017-03-16 code/test_prolate_ellipsoid.py

@@ -3,10 +3,9 @@ import numpy as np
 from copy import deepcopy
 
 from fatiando import utils, gridder
-from fatiando.mesher import ProlateEllipsoid
-from fatiando.gravmag import prolate_ellipsoid
+from mesher import ProlateEllipsoid
+import prolate_ellipsoid
 from numpy.testing import assert_almost_equal
-from pytest import raises
 
 # Local-geomagnetic field
 F = 30000
@@ -20,23 +19,23 @@ axis_ref = gm  # reference semi-axis
 
 # Prolate ellipsoids used for testing
 model = [ProlateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
-                           large_axis=axis_ref,
-                           small_axis=0.6*axis_ref,
-                           strike=78, dip=92, rake=135,
-                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
-                                                            90., 47., 13.]}),
+                          large_axis=axis_ref,
+                          small_axis=0.6*axis_ref,
+                          strike=78, dip=92, rake=135,
+                          props={'susceptibility tensor': [0.7, 0.7, 0.7,
+                                                           90., 47., 13.]}),
          ProlateEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
-                           large_axis=1.1*axis_ref,
-                           small_axis=0.3*axis_ref,
-                           strike=4, dip=10, rake=5,
-                           props={'susceptibility tensor': [0.2, 0.15, 0.05,
-                                                            180, 19, -8.],
-                                  'remanent magnetization': [3, -6, 35]}),
+                          large_axis=1.1*axis_ref,
+                          small_axis=0.3*axis_ref,
+                          strike=4, dip=10, rake=5,
+                          props={'susceptibility tensor': [0.2, 0.15, 0.05,
+                                                           180, 19, -8.],
+                                 'remanent magnetization': [3, -6, 35]}),
          ProlateEllipsoid(x=3*gm, y=3*gm, z=4*axis_ref,
-                           large_axis=1.5*axis_ref,
-                           small_axis=0.6*axis_ref,
-                           strike=-58, dip=87, rake=49,
-                           props={'remanent magnetization': [4.7, 39, 0]})]
+                          large_axis=1.5*axis_ref,
+                          small_axis=0.6*axis_ref,
[…]

### 2017-03-16 code/test_triaxial_ellipsoid.py

@@ -3,10 +3,9 @@ import numpy as np
 from copy import deepcopy
 
 from fatiando import utils, gridder
-from fatiando.mesher import TriaxialEllipsoid
-from fatiando.gravmag import triaxial_ellipsoid
+from mesher import TriaxialEllipsoid
+import triaxial_ellipsoid
 from numpy.testing import assert_almost_equal
-from pytest import raises
 
 # Local-geomagnetic field
 F = 30000

### 2017-03-16 code/triaxial_ellipsoid.py

@@ -6,7 +6,7 @@ from __future__ import division, absolute_import
 import numpy as np
 from scipy.special import ellipeinc, ellipkinc
 
-from fatiando.constants import SI2MGAL, G, CM, T2NT, SI2EOTVOS, PERM_FREE_SPACE
+from fatiando.constants import CM, T2NT
 from fatiando import utils
 
 
@@ -490,7 +490,7 @@ def x1x2x3(xp, yp, zp, ellipsoid):
 
 def _lamb(x1, x2, x3, ellipsoid):
     '''
-    Calculates the parameter lambda for a triaxial ellipsoid.
+    Calculates the parameter lambda for a triaxial ellispoid.
 
     The parameter lambda is defined as the largest root of
     the cubic equation defining the surface of the triaxial
@@ -841,6 +841,8 @@ def _gv(ellipsoid, kappa, phi, v='x'):
     Parameters:
 
     * ellipsoid : element of :class:`fatiando.mesher.TriaxialEllipsoid`.
+    * lamb: numpy array 1D
+        Parameter lambda for each point in the ellipsoid system.
     * kappa: numpy array 1D
         Modulus of the elliptic integral.
     * phi: numpy array 1D

### 2017-03-17 code/mesher.py
include changes suggested in the review for fatiando

@@ -1,9 +1,14 @@
 """
-Generate and operate geometric elements
+Generate and operate on various kinds of meshes and geometric elements
 """
 from __future__ import division, absolute_import
+from future.builtins import range, super
 import numpy
+import scipy.special
+import scipy.interpolate
 import copy as cp
+
+from fatiando import gridder
 
 
 class GeometricElement(object):
@@ -40,8 +45,1685 @@ class GeometricElement(object):
         return cp.deepcopy(self)
 
 
-class TriaxialEllipsoid(GeometricElement):
+class Polygon(GeometricElement):
 
+    """
+    Create a polygon object.
+
+    .. note:: Most applications require the vertices to be **clockwise**!
+
+    Parameters:
+
+    * vertices : list of lists
+        List of [x, y] pairs with the coordinates of the vertices.
+    * props : dict
+        Physical properties assigned to the polygon.
+        Ex: ``props={'density':10, 'susceptibility':10000}``
+
+    Examples::
+
+        >>> poly = Polygon([[0, 0], [1, 4], [2, 5]], {'density': 500})
+        >>> poly.props
+        {'density': 500}
+        >>> poly.nverts
+        3
+        >>> poly.vertices
+        array([[0, 0],
+               [1, 4],
+               [2, 5]])
+        >>> poly.x
+        array([0, 1, 2])
+        >>> poly.y
+        array([0, 4, 5])
+
+    """
+
+    def __init__(self, vertices, props=None):
+        super(Polygon, self).__init__(props)
+        self._vertices = numpy.asarray(vertices)
+
+    @property
+    def vertices(self):
+        return self._vertices
+
+    @property
+    def nverts(self):
+        return len(self.vertices)
+
+    @property
+    def x(self):
+        return self.vertices[:, 0]
+
+    @property
+    def y(self):
+        return self.vertices[:, 1]
+
+
+class Square(Polygon):
+
+    """
+    Create a square object.
+
+    Parameters:
+
+    * bounds : list = [x1, x2, y1, y2]
+        Coordinates of the top right and bottom left corners of the square
+    * props : dict
+        Physical properties assigned to the square.
+        Ex: ``props={'density':10, 'slowness':10000}``
+
+    Example::
+
+        >>> sq = Square([0, 1, 2, 4], {'density': 750})
+        >>> sq.bounds
+        [0, 1, 2, 4]
[…]

### 2017-03-17 code/oblate_ellipsoid.py

@@ -41,10 +41,10 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
     * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -92,10 +92,10 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
     * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -123,7 +123,8 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if 'susceptibility tensor' not in ellipsoid.props and \
+        if ('principal susceptibilities' not in ellipsoid.props or \
[…]

### 2017-03-17 code/prolate_ellipsoid.py

@@ -41,10 +41,10 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
     * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -92,10 +92,10 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
     * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -123,7 +123,8 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if 'susceptibility tensor' not in ellipsoid.props and \
+        if ('principal susceptibilities' not in ellipsoid.props or \
[…]

### 2017-03-17 code/test_ellipsoids.py

@@ -2,9 +2,9 @@ from __future__ import division, absolute_import
 from mesher import TriaxialEllipsoid
 from mesher import ProlateEllipsoid
 from mesher import OblateEllipsoid
-from mesher import coord_transf_matrix_triaxial
-from mesher import coord_transf_matrix_oblate
-from mesher import auxiliary_angles
+from mesher import _coord_transf_matrix_triaxial
+from mesher import _coord_transf_matrix_oblate
+from mesher import _auxiliary_angles
 import numpy as np
 from numpy.testing import assert_almost_equal
 from pytest import raises
@@ -14,8 +14,9 @@ def test_triaxial_ellipsoid_copy():
     'Check the elements of a duplicated ellipsoid'
     orig = TriaxialEllipsoid(12, 42, 53, 61, 35, 14, 10, 20, 30, {
                              'remanent magnetization': [10, 25, 40],
-                             'susceptibility tensor': [0.562, 0.485, 0.25,
-                                                       90, 0, 0]})
+                             'principal susceptibilities': [0.562, 0.485,
+                                                            0.25],
+                             'susceptibility angles': [90, 0, 0]})
     cp = orig.copy()
     assert orig is not cp
     assert orig.x == cp.x
@@ -29,12 +30,12 @@ def test_triaxial_ellipsoid_copy():
     cp.x = 4
     cp.y = 6
     cp.z = 7
-    cp.props['susceptibility tensor'] = [0.7, 0.9, 10, 9, 28, -10]
+    cp.props['principal susceptibilities'] = [0.7, 0.9, 1]
     assert orig.x != cp.x
     assert orig.y != cp.y
     assert orig.z != cp.z
-    assert orig.props['susceptibility tensor'] != \
-        cp.props['susceptibility tensor']
+    assert orig.props['principal susceptibilities'] != \
+        cp.props['principal susceptibilities']
 
 
 def test_triaxial_ellipsoid_axes():
@@ -44,16 +45,44 @@ def test_triaxial_ellipsoid_axes():
            strike=10, dip=20, rake=30)
 
 
-def test_triaxial_ellipsoid_susceptibility_tensor_fmt():
-    'susceptibility tensor must be a list containing 6 elements'
+def test_triaxial_ellipsoid_principal_susceptibilities_fmt():
+    'principal susceptibilities must be a list containing 3 elements'
     e = TriaxialEllipsoid(x=1, y=2, z=3, large_axis=6,
                           intermediate_axis=5, small_axis=4,
[…]

### 2017-03-17 code/test_oblate_ellipsoid.py

@@ -22,14 +22,16 @@ model = [OblateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
                          small_axis=0.6*axis_ref,
                          large_axis=axis_ref,
                          strike=78, dip=92, rake=135,
-                         props={'susceptibility tensor': [0.7, 0.7, 0.7,
-                                                          90., 47., 13.]}),
+                         props={'principal susceptibilities': [0.7, 0.7,
+                                                               0.7],
+                                'susceptibility angles': [90., 47., 13.]}),
          OblateEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
                          small_axis=0.3*axis_ref,
                          large_axis=1.1*axis_ref,
                          strike=4, dip=10, rake=5,
-                         props={'susceptibility tensor': [0.2, 0.15, 0.05,
-                                                          180, 19, -8.],
+                         props={'principal susceptibilities': [0.2, 0.15,
+                                                               0.05],
+                                'susceptibility angles': [180, 19, -8.],
                                 'remanent magnetization': [3, -6, 35]}),
          OblateEllipsoid(x=3*gm, y=3*gm, z=4*axis_ref,
                          small_axis=0.6*axis_ref,
@@ -125,7 +127,7 @@ def test_oblate_ellipsoid_ignore_missing_prop():
     model_none = deepcopy(model)
 
     # remove the required properties of an element of the copy
-    del model_none[1].props['susceptibility tensor']
+    del model_none[1].props['principal susceptibilities']
     del model_none[1].props['remanent magnetization']
 
     # magnetic field produced by the original model
@@ -205,7 +207,8 @@ def test_oblate_ellipsoid_neglecting_self_demagnetization():
     "The error in magnetization by negleting self-demagnetization is bounded"
 
     # susceptibility tensor
-    k1, k2, k3, strike, dip, rake = model[0].props['susceptibility tensor']
+    k1, k2, k3 = model[0].props['principal susceptibilities']
+    strike, dip, rake = model[0].props['susceptibility angles']
 
     # demagnetizing factors
     n11, n22 = oblate_ellipsoid.demag_factors(model[0])
@@ -281,6 +284,7 @@ def test_oblate_ellipsoid_depolarization_tensor():
 def test_oblate_ellipsoid_isotropic_susceptibility():
     "Isostropic susceptibility must be proportional to identity"
 
[…]

### 2017-03-17 code/test_prolate_ellipsoid.py

@@ -22,14 +22,16 @@ model = [ProlateEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
                           large_axis=axis_ref,
                           small_axis=0.6*axis_ref,
                           strike=78, dip=92, rake=135,
-                          props={'susceptibility tensor': [0.7, 0.7, 0.7,
-                                                           90., 47., 13.]}),
+                          props={'principal susceptibilities': [0.7, 0.7,
+                                                                0.7],
+                                 'susceptibility angles': [90., 47., 13.]}),
          ProlateEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
                           large_axis=1.1*axis_ref,
                           small_axis=0.3*axis_ref,
                           strike=4, dip=10, rake=5,
-                          props={'susceptibility tensor': [0.2, 0.15, 0.05,
-                                                           180, 19, -8.],
+                          props={'principal susceptibilities': [0.2, 0.15,
+                                                                0.05],
+                                 'susceptibility angles': [180, 19, -8.],
                                  'remanent magnetization': [3, -6, 35]}),
          ProlateEllipsoid(x=3*gm, y=3*gm, z=4*axis_ref,
                           large_axis=1.5*axis_ref,
@@ -125,7 +127,7 @@ def test_prolate_ellipsoid_ignore_missing_prop():
     model_none = deepcopy(model)
 
     # remove the required properties of an element of the copy
-    del model_none[1].props['susceptibility tensor']
+    del model_none[1].props['principal susceptibilities']
     del model_none[1].props['remanent magnetization']
 
     # magnetic field produced by the original model
@@ -205,7 +207,8 @@ def test_prolate_ellipsoid_neglecting_self_demagnetization():
     "The error in magnetization by negleting self-demagnetization is bounded"
 
     # susceptibility tensor
-    k1, k2, k3, strike, dip, rake = model[0].props['susceptibility tensor']
+    k1, k2, k3 = model[0].props['principal susceptibilities']
+    strike, dip, rake = model[0].props['susceptibility angles']
 
     # demagnetizing factors
     n11, n22 = prolate_ellipsoid.demag_factors(model[0])
@@ -281,6 +284,7 @@ def test_prolate_ellipsoid_depolarization_tensor():
 def test_prolate_ellipsoid_isotropic_susceptibility():
     "Isostropic susceptibility must be proportional to identity"
 
[…]

### 2017-03-17 code/test_triaxial_ellipsoid.py

@@ -23,15 +23,17 @@ model = [TriaxialEllipsoid(x=-3*gm, y=-3*gm, z=3*axis_ref,
                            intermediate_axis=0.8*axis_ref,
                            small_axis=0.6*axis_ref,
                            strike=78, dip=92, rake=135,
-                           props={'susceptibility tensor': [0.7, 0.7, 0.7,
-                                                            90., 47., 13.]}),
+                           props={'principal susceptibilities': [0.7, 0.7,
+                                                                 0.7],
+                                  'susceptibility angles': [90., 47., 13.]}),
          TriaxialEllipsoid(x=-gm, y=-gm, z=2.4*axis_ref,
                            large_axis=1.1*axis_ref,
                            intermediate_axis=0.7*axis_ref,
                            small_axis=0.3*axis_ref,
                            strike=4, dip=10, rake=5,
-                           props={'susceptibility tensor': [0.2, 0.15, 0.05,
-                                                            180, 19, -8.],
+                           props={'principal susceptibilities': [0.2, 0.15,
+                                                                 0.05],
+                                  'susceptibility angles': [180, 19, -8.],
                                   'remanent magnetization': [3, -6, 35]}),
          TriaxialEllipsoid(x=3*gm, y=3*gm, z=4*axis_ref,
                            large_axis=1.5*axis_ref,
@@ -128,7 +130,7 @@ def test_triaxial_ellipsoid_ignore_missing_prop():
     model_none = deepcopy(model)
 
     # remove the required properties of an element of the copy
-    del model_none[1].props['susceptibility tensor']
+    del model_none[1].props['principal susceptibilities']
     del model_none[1].props['remanent magnetization']
 
     # magnetic field produced by the original model
@@ -208,7 +210,8 @@ def test_triaxial_ellipsoid_neglecting_self_demagnetization():
     "The error in magnetization by negleting self-demagnetization is bounded"
 
     # susceptibility tensor
-    k1, k2, k3, strike, dip, rake = model[0].props['susceptibility tensor']
+    k1, k2, k3 = model[0].props['principal susceptibilities']
+    strike, dip, rake = model[0].props['susceptibility angles']
 
     # demagnetizing factors
     n11, n22, n33 = triaxial_ellipsoid.demag_factors(model[0])
@@ -286,6 +289,7 @@ def test_triaxial_ellipsoid_depolarization_tensor():
[…]

### 2017-03-17 code/triaxial_ellipsoid.py

@@ -42,10 +42,10 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
     * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -92,10 +92,10 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
     * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
-        The ellipsoids. Ellipsoids must have the physical property
-        ``'susceptibility tensor'`` and/or ``'remanent magnetization'``.
-        Ellipsoids that are ``None`` or without ``'susceptibility tensor'``
-        and without ``'remanent magnetization'`` will be ignored.
+        The ellipsoids. Ellipsoids must have the physical properties
+        ``'principal susceptibilities'`` and ``'susceptibility angles'``
+        and/or ``'remanent magnetization'``. Ellipsoids that do not have
+        these physical properties or are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -122,7 +122,8 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if 'susceptibility tensor' not in ellipsoid.props and \
+        if ('principal susceptibilities' not in ellipsoid.props or \
[…]

### 2017-03-17 code/oblate_ellipsoid.py
problem with missing prop test

@@ -123,10 +123,6 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
-            continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b3 = _bz(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -184,10 +180,6 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     res = 0
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
-            continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
             continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -247,10 +239,6 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
-            continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b3 = _bz(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -308,6 +296,8 @@ def _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
     if pmag is None:
         mx, my, mz = magnetization(ellipsoid, F, inc, dec, demag)
     else:
+        assert demag is not True, 'the use of a forced magnetization \
+impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
[…]

### 2017-03-17 code/test_oblate_ellipsoid.py

@@ -49,13 +49,13 @@ def test_oblate_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property
     bx = oblate_ellipsoid.bx(x, y, z, model,
-                             F, inc, dec, pmag=pmag)
+                             F, inc, dec, demag=False, pmag=pmag)
     by = oblate_ellipsoid.by(x, y, z, model,
-                             F, inc, dec, pmag=pmag)
+                             F, inc, dec, demag=False, pmag=pmag)
     bz = oblate_ellipsoid.bz(x, y, z, model,
-                             F, inc, dec, pmag=pmag)
+                             F, inc, dec, demag=False, pmag=pmag)
     tf = oblate_ellipsoid.tf(x, y, z, model,
-                             F, inc, dec, pmag=pmag)
+                             F, inc, dec, demag=False, pmag=pmag)
 
     # constant factor
     f = 3.71768
@@ -63,13 +63,13 @@ def test_oblate_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property multiplied by the constant factor
     bx2 = oblate_ellipsoid.bx(x, y, z, model,
-                              F, inc, dec, pmag=f*pmag)
+                              F, inc, dec, demag=False, pmag=f*pmag)
     by2 = oblate_ellipsoid.by(x, y, z, model,
-                              F, inc, dec, pmag=f*pmag)
+                              F, inc, dec, demag=False, pmag=f*pmag)
     bz2 = oblate_ellipsoid.bz(x, y, z, model,
-                              F, inc, dec, pmag=f*pmag)
+                              F, inc, dec, demag=False, pmag=f*pmag)
     tf2 = oblate_ellipsoid.tf(x, y, z, model,
-                              F, inc, dec, pmag=f*pmag)
+                              F, inc, dec, demag=False, pmag=f*pmag)
 
     # the fields must be proportional
     assert_almost_equal(bx2, f*bx, decimal=12)
@@ -93,23 +93,23 @@ def test_oblate_ellipsoid_ignore_none():
     # magnetic field produced by the original model
     # without the removed element
     bx = oblate_ellipsoid.bx(x, y, z, [model[0], model[2]],
-                             F, inc, dec, pmag=pmag)
+                             F, inc, dec, demag=False, pmag=pmag)
     by = oblate_ellipsoid.by(x, y, z, [model[0], model[2]],
[…]

### 2017-03-17 code/test_prolate_ellipsoid.py

@@ -49,13 +49,13 @@ def test_prolate_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property
     bx = prolate_ellipsoid.bx(x, y, z, model,
-                              F, inc, dec, pmag=pmag)
+                              F, inc, dec, demag=False, pmag=pmag)
     by = prolate_ellipsoid.by(x, y, z, model,
-                              F, inc, dec, pmag=pmag)
+                              F, inc, dec, demag=False, pmag=pmag)
     bz = prolate_ellipsoid.bz(x, y, z, model,
-                              F, inc, dec, pmag=pmag)
+                              F, inc, dec, demag=False, pmag=pmag)
     tf = prolate_ellipsoid.tf(x, y, z, model,
-                              F, inc, dec, pmag=pmag)
+                              F, inc, dec, demag=False, pmag=pmag)
 
     # constant factor
     f = 3.71768
@@ -63,13 +63,13 @@ def test_prolate_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property multiplied by the constant factor
     bx2 = prolate_ellipsoid.bx(x, y, z, model,
-                               F, inc, dec, pmag=f*pmag)
+                               F, inc, dec, demag=False, pmag=f*pmag)
     by2 = prolate_ellipsoid.by(x, y, z, model,
-                               F, inc, dec, pmag=f*pmag)
+                               F, inc, dec, demag=False, pmag=f*pmag)
     bz2 = prolate_ellipsoid.bz(x, y, z, model,
-                               F, inc, dec, pmag=f*pmag)
+                               F, inc, dec, demag=False, pmag=f*pmag)
     tf2 = prolate_ellipsoid.tf(x, y, z, model,
-                               F, inc, dec, pmag=f*pmag)
+                               F, inc, dec, demag=False, pmag=f*pmag)
 
     # the fields must be proportional
     assert_almost_equal(bx2, f*bx, decimal=12)
@@ -93,23 +93,23 @@ def test_prolate_ellipsoid_ignore_none():
     # magnetic field produced by the original model
     # without the removed element
     bx = prolate_ellipsoid.bx(x, y, z, [model[0], model[2]],
-                              F, inc, dec, pmag=pmag)
+                              F, inc, dec, demag=False, pmag=pmag)
     by = prolate_ellipsoid.by(x, y, z, [model[0], model[2]],
[…]

### 2017-03-17 code/test_triaxial_ellipsoid.py

@@ -52,13 +52,13 @@ def test_triaxial_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property
     bx = triaxial_ellipsoid.bx(x, y, z, model,
-                               F, inc, dec, pmag=pmag)
+                               F, inc, dec, demag=False, pmag=pmag)
     by = triaxial_ellipsoid.by(x, y, z, model,
-                               F, inc, dec, pmag=pmag)
+                               F, inc, dec, demag=False, pmag=pmag)
     bz = triaxial_ellipsoid.bz(x, y, z, model,
-                               F, inc, dec, pmag=pmag)
+                               F, inc, dec, demag=False, pmag=pmag)
     tf = triaxial_ellipsoid.tf(x, y, z, model,
-                               F, inc, dec, pmag=pmag)
+                               F, inc, dec, demag=False, pmag=pmag)
 
     # constant factor
     f = 3.71768
@@ -66,13 +66,13 @@ def test_triaxial_ellipsoid_force_prop():
     # magnetic field produced by the ellipsoids
     # with the forced physical property multiplied by the constant factor
     bx2 = triaxial_ellipsoid.bx(x, y, z, model,
-                                F, inc, dec, pmag=f*pmag)
+                                F, inc, dec, demag=False, pmag=f*pmag)
     by2 = triaxial_ellipsoid.by(x, y, z, model,
-                                F, inc, dec, pmag=f*pmag)
+                                F, inc, dec, demag=False, pmag=f*pmag)
     bz2 = triaxial_ellipsoid.bz(x, y, z, model,
-                                F, inc, dec, pmag=f*pmag)
+                                F, inc, dec, demag=False, pmag=f*pmag)
     tf2 = triaxial_ellipsoid.tf(x, y, z, model,
-                                F, inc, dec, pmag=f*pmag)
+                                F, inc, dec, demag=False, pmag=f*pmag)
 
     # the fields must be proportional
     assert_almost_equal(bx2, f*bx, decimal=12)
@@ -96,23 +96,23 @@ def test_triaxial_ellipsoid_ignore_none():
     # magnetic field produced by the original model
     # without the removed element
     bx = triaxial_ellipsoid.bx(x, y, z, [model[0], model[2]],
-                               F, inc, dec, pmag=pmag)
+                               F, inc, dec, demag=False, pmag=pmag)
[…]

### 2017-03-17 code/triaxial_ellipsoid.py

@@ -122,10 +122,6 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
-            continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b3 = _bz(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -182,10 +178,6 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     res = 0
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
-            continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
             continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -244,10 +236,6 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     for ellipsoid in ellipsoids:
         if ellipsoid is None:
             continue
-        if ('principal susceptibilities' not in ellipsoid.props or \
-                'susceptibility angles' not in ellipsoid.props) and \
-                'remanent magnetization' not in ellipsoid.props:
-            continue
         b1 = _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b2 = _by(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
         b3 = _bz(xp, yp, zp, ellipsoid, F, inc, dec, demag, pmag)
@@ -304,6 +292,8 @@ def _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
     if pmag is None:
         mx, my, mz = magnetization(ellipsoid, F, inc, dec, demag)
     else:
+        assert demag is not True, 'the use of a forced magnetization \
+impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
[…]

### 2017-03-17 code/mesher.py
remove fatiando code

@@ -45,1684 +45,6 @@ class GeometricElement(object):
         return cp.deepcopy(self)
 
 
-class Polygon(GeometricElement):
-
-    """
-    Create a polygon object.
-
-    .. note:: Most applications require the vertices to be **clockwise**!
-
-    Parameters:
-
-    * vertices : list of lists
-        List of [x, y] pairs with the coordinates of the vertices.
-    * props : dict
-        Physical properties assigned to the polygon.
-        Ex: ``props={'density':10, 'susceptibility':10000}``
-
-    Examples::
-
-        >>> poly = Polygon([[0, 0], [1, 4], [2, 5]], {'density': 500})
-        >>> poly.props
-        {'density': 500}
-        >>> poly.nverts
-        3
-        >>> poly.vertices
-        array([[0, 0],
-               [1, 4],
-               [2, 5]])
-        >>> poly.x
-        array([0, 1, 2])
-        >>> poly.y
-        array([0, 4, 5])
-
-    """
-
-    def __init__(self, vertices, props=None):
-        super(Polygon, self).__init__(props)
-        self._vertices = numpy.asarray(vertices)
-
-    @property
-    def vertices(self):
-        return self._vertices
-
-    @property
-    def nverts(self):
-        return len(self.vertices)
-
-    @property
-    def x(self):
-        return self.vertices[:, 0]
-
-    @property
-    def y(self):
-        return self.vertices[:, 1]
-
-
-class Square(Polygon):
-
-    """
-    Create a square object.
-
-    Parameters:
-
-    * bounds : list = [x1, x2, y1, y2]
-        Coordinates of the top right and bottom left corners of the square
-    * props : dict
-        Physical properties assigned to the square.
-        Ex: ``props={'density':10, 'slowness':10000}``
-
-    Example::
-
-        >>> sq = Square([0, 1, 2, 4], {'density': 750})
-        >>> sq.bounds
-        [0, 1, 2, 4]
-        >>> sq.x1
-        0
-        >>> sq.x2
-        1
-        >>> sq.props
-        {'density': 750}
-        >>> sq.addprop('magnetization', 100)
-        >>> sq.props['magnetization']
-        100
-
-    A square can be used as a :class:`~fatiando.mesher.Polygon`::
-
-        >>> sq.vertices
-        array([[0, 2],
-               [1, 2],
-               [1, 4],
-               [0, 4]])
-        >>> sq.x
-        array([0, 1, 1, 0])
[…]

### 2017-03-17 code/oblate_ellipsoid.py

@@ -40,7 +40,7 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
-    * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
+    * ellipsoids : list of :class:`mesher.OblateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -91,7 +91,7 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
+    * ellipsoids : list of :class:`mesher.OblateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -149,7 +149,7 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
+    * ellipsoids : list of :class:`mesher.OblateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -207,7 +207,7 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.OblateEllipsoid`
+    * ellipsoids : list of :class:`mesher.OblateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
[…]

### 2017-03-17 code/prolate_ellipsoid.py

@@ -40,7 +40,7 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
-    * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
+    * ellipsoids : list of :class:`mesher.ProlateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -91,7 +91,7 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
+    * ellipsoids : list of :class:`mesher.ProlateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -149,7 +149,7 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
+    * ellipsoids : list of :class:`mesher.ProlateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -207,7 +207,7 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.ProlateEllipsoid`
+    * ellipsoids : list of :class:`mesher.ProlateEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
[…]

### 2017-03-17 code/triaxial_ellipsoid.py

@@ -41,7 +41,7 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated.
-    * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
+    * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -91,7 +91,7 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
+    * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -148,7 +148,7 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
+    * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
         and/or ``'remanent magnetization'``. Ellipsoids that do not have
@@ -205,7 +205,7 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
 
     * xp, yp, zp : arrays
         The x, y, and z coordinates where the anomaly will be calculated
-    * ellipsoids : list of :class:`fatiando.mesher.TriaxialEllipsoid`
+    * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
[…]

### 2017-03-17 manuscript/manuscript.tex

@@
 
-\title{3D Magnetic modelling of ellipsoidal bodies}
+\title{Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies}
 
@@
 points at a constant vertical coordinate $z = 0$ \unit{m}.
-The total-field anomaly varies from $\approx -295.3$ \unit{nT}
-to $\approx 149.5$ \unit{nT}, resulting in a peak-to-peak amplitude
-of $\approx 444.9$ \unit{nT}, and was calculated by using the 
+The total-field anomaly varies from $\approx -176$ \unit{nT}
+to $\approx 237$ \unit{nT}, resulting in a peak-to-peak amplitude
+of $\approx 413$ \unit{nT}, and was calculated by using the 
 true magnetization $\mathbf{M}$ defined in Eqs. 
@@
 susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
-The peak-to-peak amplitude is $\approx 212.0$ \unit{nT}
-and represents $\approx 48 \%$ of the peak-to-peak amplitude of
+The peak-to-peak amplitude is $\approx 141$ \unit{nT}
+and represents $\approx 34 \%$ of the peak-to-peak amplitude of
 the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
@@
 In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
-$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.2 \%$
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.4 \%$
 (Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
 The peak-to-peak amplitude of the differences in the total-field anomaly
-(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 1.5$ \unit{nT},
-which represents $\approx 4.5 \%$ of the peak-to-peak amplitude of the
+(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 0.8$ \unit{nT},
+which represents $\approx 2.9 \%$ of the peak-to-peak amplitude of the
 total-field anomaly calculates by using the true magnetization $\mathbf{M}$
@@
 In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
-$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.9 \%$
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.8 \%$
 (Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
 The peak-to-peak amplitude of the differences in the total-field anomaly
-(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 2.0$ \unit{nT},
-which represents $\approx 5.1 \%$ of the peak-to-peak amplitude of the
+(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 1.1$ \unit{nT},
+which represents $\approx 3.3 \%$ of the peak-to-peak amplitude of the
 total-field anomaly calculates by using the true magnetization $\mathbf{M}$

### 2017-03-20 code/oblate_ellipsoid.py
edit the repository

@@ -685,9 +685,10 @@ susceptibility tensor'
 
     else:
 
-        assert (suscep is not None) or ('remanent magnetization' \
-            in ellipsoid.props), 'neglecting self-demagnetization requires a \
-susceptibility tensor or a remanent magnetization'
+        assert (suscep is not None) or ('remanent magnetization'
+                                        in ellipsoid.props), 'neglecting \
+            self-demagnetization requires a susceptibility tensor or a rem\
+            anent magnetization'
 
         # resultant magnetization in the main system
         resultant_mag = induced_mag + remanent_mag

### 2017-03-20 code/mesher.py
edit the README files and remove the unused notebooks

@@ -1,5 +1,5 @@
 """
-Generate and operate on various kinds of meshes and geometric elements
+Generate and operate the geometric elements representing ellipsoids
 """
 from __future__ import division, absolute_import
 from future.builtins import super

### 2017-03-20 code/test_triaxial_ellipsoid.py
correct the tests with missing props

@@ -6,6 +6,7 @@ from fatiando import utils, gridder
 from mesher import TriaxialEllipsoid
 import triaxial_ellipsoid
 from numpy.testing import assert_almost_equal
+from pytest import raises
 
 # Local-geomagnetic field
 F = 30000
@@ -80,6 +81,16 @@ def test_triaxial_ellipsoid_force_prop():
     assert_almost_equal(bz2, f*bz, decimal=12)
     assert_almost_equal(tf2, f*tf, decimal=12)
 
+    # pmag not None requires demag not True
+    raises(AssertionError, triaxial_ellipsoid.bx, x, y, z, model,
+           F, inc, dec, demag=True, pmag=pmag)
+    raises(AssertionError, triaxial_ellipsoid.by, x, y, z, model,
+           F, inc, dec, demag=True, pmag=pmag)
+    raises(AssertionError, triaxial_ellipsoid.bz, x, y, z, model,
+           F, inc, dec, demag=True, pmag=pmag)
+    raises(AssertionError, triaxial_ellipsoid.tf, x, y, z, model,
+           F, inc, dec, demag=True, pmag=pmag)
+
 
 def test_triaxial_ellipsoid_ignore_none():
     "Triaxial ellipsoid ignores model elements that are None"
@@ -120,44 +131,27 @@ def test_triaxial_ellipsoid_ignore_none():
     assert_almost_equal(tf2, tf, decimal=15)
 
 
-def test_triaxial_ellipsoid_ignore_missing_prop():
-    "Triaxial ellipsoid ignores model without the needed properties"
+def test_triaxial_ellipsoid_missing_prop():
+    "Self-demagnetization requires specific properties"
 
-    # forced physical property
-    pmag = utils.ang2vec(2, -4, 17)
+    # demag=True requires specific properties
+    raises(AssertionError, triaxial_ellipsoid._bx, x, y, z, model[2],
+           F, inc, dec, demag=True)
+    raises(AssertionError, triaxial_ellipsoid._by, x, y, z, model[2],
+           F, inc, dec, demag=True)
+    raises(AssertionError, triaxial_ellipsoid._bz, x, y, z, model[2],
+           F, inc, dec, demag=True)
 
-    # copy of the original model
-    model_none = deepcopy(model)
 
-    # remove the required properties of an element of the copy
-    del model_none[1].props['principal susceptibilities']
-    del model_none[1].props['remanent magnetization']
[…]

### 2017-03-21 manuscript/manuscript.tex

@@
 
+\usepackage{url}
+
 \begin{document}
@@
 
-The code is implemented in Python language,
+The code is implemented in the Python language,
 by using the NumPy and SciPy libraries \citep{vanderwalt2011},
@@
 test suite formed by a considerable number of
-assertions, unit tests, doc tests and integration tests.
-For readers interested in automated code testing,
-we recommend the freely reusable lessons of the Software Carpentry 
-(\url{https://software-carpentry.org/}) and at the
-description of the doctest module available
-in the documentation for Python 2.X 
-(\url{https://docs.python.org/2/library/doctest.html}).
-
-The numerical simulations presented here was generated with
+assertions, unit tests, doc tests, and integration tests.
+We refer the readers interested in best practices for scientific computing to
+\citet{wilson2014}.
+
+The numerical simulations presented here were generated with
 the Jupyter Notebook
-(\url{http://jupyter-notebook.readthedocs.io/en/latest/notebook.html}),
+(\url{http://jupyter.org}),
 which is a web application that allows creating and sharing
@@
 explanatory text.
-Besides using the Fatiando a Terra \citep{uieda2013},
+Besides using Fatiando a Terra \citep{uieda2013},
 the numerical simulations use the
 NumPy library \citep{vanderwalt2011} to perform numerical
-computations, the Matplotlib library \citep{hunter2007} to plot
+computations and the Matplotlib library \citep{hunter2007} to plot
 the results and generate figures.
-The Jupyter Notebooks used to reproduce all the results presented here
-are available at a repository in the GitHub
+The Jupyter Notebooks used to produce all the results presented here
+are available in a repository on GitHub
 (\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
@@
 
-The current version of our code is freely distributed, under 
-BSD 3-clause licence, in a repository of GitHub
+The current version of our code is freely distributed, under the
+BSD 3-clause licence, in a repository on GitHub
 (\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
+Instructions for running the current version of our code
+are also provided in the repository.
 The code was developed as part of the Fatiando a Terra
-\citep{uieda2013}, which is an open-source Python 
+\citep{uieda2013} open-source Python
 library for modelling and inversion in geophysics.
-Instructions for running the current version of our code
-in the Fatiando a Terra are provided at its repository
-in GitHub.
 Documentation and installation instructions for
-the most current release version of Fatiando a Terra 
-are provided at \url http://www.fatiando.org.
+the 0.5 release version of Fatiando a Terra
+are provided at \url{http://www.fatiando.org/v0.5}.
 

### 2017-03-21 code/plot_functions.py
plot functions

@@ -1,7 +1,8 @@
+from __future__ import division
 import os
-from mpl_toolkits.mplot3d import axes3d
 import matplotlib.pyplot as plt
 import numpy as np
+import mesher
 
 
 def savefig(fname):
@@ -23,307 +24,131 @@ def savefig(fname):
     plt.savefig(fig_file, facecolor='w', bbox_inches='tight')
 
 
-def draw_main_system(ax, length_axes = 1., label_size = 22, elev=200, azim=-20):
+def draw_main_system(ax, length_axes=1, label_size=22, elev=200,
+                     azim=-20):
     '''
     Plot the axes forming the main coordinate system.
 
-    input
-    ax: axes of a matplotlib figure.
-    length_axes: float - length of the axes (in meters).
-        Default is 1.
-    label_size: float - size of the label font. Default is 22.
-    elev and azim: floats - parameters controlling the view
-        of the figure. Default is 200 and -20, respectively.
+    Parameters:
 
-    output
-    matplotlib objects
+    * ax: axes of a matplotlib figure.
+    * length_axes: float
+        Length of the axes (in meters). Default is 1.
+    * label_size: float
+        Size of the label font. Default is 22.
+    * elev and azim: floats
+        Parameters controlling the view of the figure.
+        Default is 200 and -20, respectively.
     '''
 
     # x-axis
-    ax.quiver(length_axes, 0., 0., length_axes, 0., 0.,
-              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+    ax.quiver(length_axes, 0, 0, length_axes, 0, 0,
+              length=length_axes, color='k', linewidth=2, linestyle='-',
               arrow_length_ratio=0.1)
-    ax.text(1.05*length_axes, 0., 0., '$x$', color='k', fontsize=label_size)
+    ax.text(1.05*length_axes, 0, 0, '$x$', color='k', fontsize=label_size)
 
     # y-axis
-    ax.quiver(0., length_axes, 0., 0., length_axes, 0.,
-              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+    ax.quiver(0, length_axes, 0, 0, length_axes, 0,
[…]

### 2017-03-21 code/triaxial_ellipsoid.py

@@ -44,8 +44,8 @@ def tf(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
-        and/or ``'remanent magnetization'``. Ellipsoids that do not have
-        these physical properties or are ``None`` will be ignored.
+        as prerequisite to calculate the self-demagnetization.
+        Ellipsoids that are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -94,8 +94,8 @@ def bx(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
-        and/or ``'remanent magnetization'``. Ellipsoids that do not have
-        these physical properties or are ``None`` will be ignored.
+        as prerequisite to calculate the self-demagnetization.
+        Ellipsoids that are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -151,8 +151,8 @@ def by(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
-        and/or ``'remanent magnetization'``. Ellipsoids that do not have
-        these physical properties or are ``None`` will be ignored.
+        as prerequisite to calculate the self-demagnetization.
+        Ellipsoids that are ``None`` will be ignored.
     * F, inc, dec : floats
        The intensity (in nT), inclination and declination (in degrees) of
        the local-geomagnetic field.
@@ -208,8 +208,8 @@ def bz(xp, yp, zp, ellipsoids, F, inc, dec, demag=True, pmag=None):
     * ellipsoids : list of :class:`mesher.TriaxialEllipsoid`
         The ellipsoids. Ellipsoids must have the physical properties
         ``'principal susceptibilities'`` and ``'susceptibility angles'``
[…]

### 2017-03-22 code/oblate_ellipsoid.py
change the signal of the calculated field in _bx, _by and _bz

@@ -5,7 +5,7 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
-from fatiando.constants import CM, T2NT
+from fatiando.constants import PERM_FREE_SPACE, T2NT
 from fatiando import utils
 
 
@@ -311,7 +311,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 
@@ -377,7 +377,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*my
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 
@@ -443,7 +443,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mz
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 

### 2017-03-22 code/prolate_ellipsoid.py

@@ -5,7 +5,7 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
-from fatiando.constants import CM, T2NT
+from fatiando.constants import PERM_FREE_SPACE, T2NT
 from fatiando import utils
 
 
@@ -311,7 +311,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 
@@ -377,7 +377,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*my
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 
@@ -443,7 +443,7 @@ impedes the computation of self-demagnetization'
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mz
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*b
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
     return res
 
 

### 2017-03-22 code/triaxial_ellipsoid.py

@@ -6,7 +6,7 @@ from __future__ import division, absolute_import
 import numpy as np
 from scipy.special import ellipeinc, ellipkinc
 
-from fatiando.constants import CM, T2NT
+from fatiando.constants import PERM_FREE_SPACE, T2NT
 from fatiando import utils
 
 
@@ -309,7 +309,7 @@ impedes the computation of self-demagnetization'
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*c
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
     return res
 
 
@@ -376,7 +376,7 @@ impedes the computation of self-demagnetization'
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*c
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
     return res
 
 
@@ -443,7 +443,7 @@ impedes the computation of self-demagnetization'
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= -CM*T2NT*2*np.pi*a*b*c
+    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
     return res
 
 

### 2017-03-23 code/oblate_ellipsoid.py
analysis of the external depolarization tensor elements

@@ -5,7 +5,6 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
-from fatiando.constants import PERM_FREE_SPACE, T2NT
 from fatiando import utils
 
 
@@ -308,10 +307,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='x')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -374,10 +377,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='y')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*my
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -440,10 +447,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='z')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mz
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 

### 2017-03-23 code/plot_functions.py

@@ -103,11 +103,11 @@ def draw_ellipsoid(ax, ellipsoid, body_color, body_alpha,
     if ellipsoid.__class__ is mesher.ProlateEllipsoid:
         a = ellipsoid.large_axis
         b = ellipsoid.small_axis
-        c = b
+        c = ellipsoid.small_axis
     if ellipsoid.__class__ is mesher.OblateEllipsoid:
         a = ellipsoid.small_axis
         b = ellipsoid.large_axis
-        c = b
+        c = ellipsoid.large_axis
 
     if plot_axes is True:
 

### 2017-03-23 code/prolate_ellipsoid.py

@@ -5,7 +5,6 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
-from fatiando.constants import PERM_FREE_SPACE, T2NT
 from fatiando import utils
 
 
@@ -308,10 +307,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='x')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -374,10 +377,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='y')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*my
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -440,10 +447,14 @@ impedes the computation of self-demagnetization'
     h2 = _hv(ellipsoid, lamb, v='y')
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='z')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mz
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*b
+    res *= -2*np.pi*a*b*b
+
+    res *= -100 # -PERM_FREE_SPACE*T2NT
+
     return res
 
 

### 2017-03-23 code/triaxial_ellipsoid.py

@@ -305,11 +305,15 @@ impedes the computation of self-demagnetization'
     h3 = _hv(ellipsoid, lamb, v='z')
     kappa, phi = _E_F_field_args(ellipsoid, lamb)
     g = _gv_tejedor(ellipsoid, kappa, phi, lamb, v='x')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
+    res *= -0.5*a*b*c
+
+    res *= -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -372,11 +376,15 @@ impedes the computation of self-demagnetization'
     h3 = _hv(ellipsoid, lamb, v='z')
     kappa, phi = _E_F_field_args(ellipsoid, lamb)
     g = _gv_tejedor(ellipsoid, kappa, phi, lamb, v='y')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*my
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
+    res *= -0.5*a*b*c
+
+    res *= -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -439,11 +447,15 @@ impedes the computation of self-demagnetization'
     h3 = _hv(ellipsoid, lamb, v='z')
     kappa, phi = _E_F_field_args(ellipsoid, lamb)
     g = _gv_tejedor(ellipsoid, kappa, phi, lamb, v='z')
+
     res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mz
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= PERM_FREE_SPACE*T2NT*0.5*a*b*c
+    res *= -0.5*a*b*c
+
+    res *= -PERM_FREE_SPACE*T2NT
+
     return res
 
 
@@ -636,11 +648,13 @@ def _E_F_demag(ellipsoid):
     b = ellipsoid.intermediate_axis
[…]

### 2017-03-24 code/oblate_ellipsoid.py
comparison between a triaxial ellipsoid and a sphere with similar volumes

@@ -5,6 +5,7 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
+from fatiando.constants import CM, T2NT
 from fatiando import utils
 
 
@@ -299,6 +300,12 @@ def _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
+    V = ellipsoid.transf_matrix
+    mx_local = V[0, 0]*mx + V[1, 0]*my + V[2, 0]*mz
+    my_local = V[0, 1]*mx + V[1, 1]*my + V[2, 1]*mz
+    mz_local = V[0, 2]*mx + V[1, 2]*my + V[2, 2]*mz
+
     x1, x2, x3 = x1x2x3(xp, yp, zp, ellipsoid)
     lamb = _lamb(x1, x2, x3, ellipsoid)
     denominator = _dlamb_aux(x1, x2, x3, ellipsoid, lamb)
@@ -308,12 +315,14 @@ impedes the computation of self-demagnetization'
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='x')
 
-    res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
+    res = dlamb*(h1*x1*mx_local + h2*x2*my_local + h3*x3*mz_local)
+    res += g*mx_local
+
     a = ellipsoid.small_axis
     b = ellipsoid.large_axis
-    res *= -2*np.pi*a*b*b
+    volume = 4*np.pi*a*b*b/3
 
-    res *= -100 # -PERM_FREE_SPACE*T2NT
+    res *= -1.5*volume*CM*T2NT
 
     return res
 
@@ -369,6 +378,12 @@ def _by(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
+    V = ellipsoid.transf_matrix
+    mx_local = V[0, 0]*mx + V[1, 0]*my + V[2, 0]*mz
+    my_local = V[0, 1]*mx + V[1, 1]*my + V[2, 1]*mz
[…]

### 2017-03-24 code/prolate_ellipsoid.py

@@ -5,6 +5,7 @@ from __future__ import division, absolute_import
 
 import numpy as np
 
+from fatiando.constants import CM, T2NT
 from fatiando import utils
 
 
@@ -299,6 +300,12 @@ def _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
+    V = ellipsoid.transf_matrix
+    mx_local = V[0, 0]*mx + V[1, 0]*my + V[2, 0]*mz
+    my_local = V[0, 1]*mx + V[1, 1]*my + V[2, 1]*mz
+    mz_local = V[0, 2]*mx + V[1, 2]*my + V[2, 2]*mz
+
     x1, x2, x3 = x1x2x3(xp, yp, zp, ellipsoid)
     lamb = _lamb(x1, x2, x3, ellipsoid)
     denominator = _dlamb_aux(x1, x2, x3, ellipsoid, lamb)
@@ -308,12 +315,14 @@ impedes the computation of self-demagnetization'
     h3 = _hv(ellipsoid, lamb, v='z')
     g = _gv(ellipsoid, lamb, v='x')
 
-    res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
+    res = dlamb*(h1*x1*mx_local + h2*x2*my_local + h3*x3*mz_local)
+    res += g*mx_local
+
     a = ellipsoid.large_axis
     b = ellipsoid.small_axis
-    res *= -2*np.pi*a*b*b
+    volume = 4*np.pi*a*b*b/3
 
-    res *= -100 # -PERM_FREE_SPACE*T2NT
+    res *= -1.5*volume*CM*T2NT
 
     return res
 
@@ -369,6 +378,12 @@ def _by(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
+    V = ellipsoid.transf_matrix
+    mx_local = V[0, 0]*mx + V[1, 0]*my + V[2, 0]*mz
+    my_local = V[0, 1]*mx + V[1, 1]*my + V[2, 1]*mz
[…]

### 2017-03-24 code/triaxial_ellipsoid.py

@@ -6,7 +6,7 @@ from __future__ import division, absolute_import
 import numpy as np
 from scipy.special import ellipeinc, ellipkinc
 
-from fatiando.constants import PERM_FREE_SPACE, T2NT
+from fatiando.constants import CM, T2NT
 from fatiando import utils
 
 
@@ -296,6 +296,12 @@ def _bx(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
+    V = ellipsoid.transf_matrix
+    mx_local = V[0, 0]*mx + V[1, 0]*my + V[2, 0]*mz
+    my_local = V[0, 1]*mx + V[1, 1]*my + V[2, 1]*mz
+    mz_local = V[0, 2]*mx + V[1, 2]*my + V[2, 2]*mz
+
     x1, x2, x3 = x1x2x3(xp, yp, zp, ellipsoid)
     lamb = _lamb(x1, x2, x3, ellipsoid)
     denominator = _dlamb_aux(x1, x2, x3, ellipsoid, lamb)
@@ -306,13 +312,15 @@ impedes the computation of self-demagnetization'
     kappa, phi = _E_F_field_args(ellipsoid, lamb)
     g = _gv_tejedor(ellipsoid, kappa, phi, lamb, v='x')
 
-    res = dlamb*(h1*x1*mx + h2*x2*my + h3*x3*mz) + g*mx
+    res = dlamb*(h1*x1*mx_local + h2*x2*my_local + h3*x3*mz_local)
+    res += g*mx_local
+
     a = ellipsoid.large_axis
     b = ellipsoid.intermediate_axis
     c = ellipsoid.small_axis
-    res *= -0.5*a*b*c
+    volume = 4*np.pi*a*b*c/3
 
-    res *= -PERM_FREE_SPACE*T2NT
+    res *= -1.5*volume*CM*T2NT
 
     return res
 
@@ -367,6 +375,12 @@ def _by(xp, yp, zp, ellipsoid, F, inc, dec, demag=True, pmag=None):
 impedes the computation of self-demagnetization'
         mx, my, mz = pmag
 
+    # Transform the magnetization to the local coordinate system
[…]

### 2017-04-20 code/plot_functions.py
separate the functions draw_ellipsoid and draw_axes

@@ -114,9 +114,7 @@ def get_parameters(ellipsoid):
     return V, a, b, c, xc, yc, zc
 
 
-def draw_ellipsoid(ax, ellipsoid, body_color, body_alpha,
-                   npoints=100, plot_axes=True,
-                   axes_color=(0, 0, 0), label_size=16):
+def draw_ellipsoid(ax, ellipsoid, body_color, body_alpha, npoints=100):
     '''
     Plot the surface of an ellipsoid.
 
@@ -132,18 +130,9 @@ def draw_ellipsoid(ax, ellipsoid, body_color, body_alpha,
     * npoints: int
         Number of points used to interpolate the surface
         of the ellipsoid.
-    * plot_axes: boolean
-        If True, plot the ellipsoid semi-axes.
-    * axes_color: RGB matplotlib tuple
-        Color of the axes. The default is (0,0,0) - black color.
-    * label_size: float
-        Size of the label font. Default is 22.
     '''
 
     V, a, b, c, xc, yc, zc = get_parameters(ellipsoid)
-
-    if plot_axes is True:
-        draw_axes(ax, V, a, b, c, xc, yc, zc, axes_color, label_size)
 
     # Spherical angles (in radians) for plotting the ellipsoidal surface.
     u = np.linspace(0, 2 * np.pi, 2*npoints)
@@ -164,50 +153,52 @@ def draw_ellipsoid(ax, ellipsoid, body_color, body_alpha,
     ax.plot_surface(x, y, z, linewidth=0., color=body_color, alpha=body_alpha)
 
 
-def draw_axes(ax, V, a, b, c, xc, yc, zc,
-              axes_color=(0, 0, 0), label_size=16):
+def draw_axes(ax, ellipsoid, axes_color=(0, 0, 0),
+              label_axes=True, label_size=16):
     '''
     Plot three orthogonal axes.
 
     Parameters:
 
     * ax: axes of a matplotlib figure.
-    * V: numpy array 2D
-        Orthogonal matrix whose columns are unit vectors
-        defining the orthogonal axes.
-    * a, b, c: floats
-        Magnitude of the axes.
-    * xc, yc, zc: floats
-        Origin of the axes.
-    * axes_color: RGB matplotlib tuple
-        Color of the axes. The default is (0,0,0) - black color.
-    * label_size: float
[…]

### 2017-04-20 manuscript/manuscript.tex

@@
 Let us consider an ellipsoidal body with centre at the point
-$(x_{c}, y_{c}, z_{c})$, orientation defined by three angles
-$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a),
-and semi-axes defined by
+$(x_{c}, y_{c}, z_{c})$, orientation defined by the angles
+\textit{strike} $\varepsilon$, \textit{dip} $\zeta$, and \textit{rake} $\eta$
+(Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
 positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
-The angles $\varepsilon$, $\zeta$, and $\eta$ are called \textit{strike},
-\textit{dip}, and \textit{rake}, respectively, and are commonly used to
-define the orientation of lines in structural geology
-\citep{clark1986, allmendinger2012}.
+The orientation angles \textit{strike}, \textit{dip}, and \textit{rake}
+are commonly used to define the orientation of lines in structural geology
+\citep{pollard2005, allmendinger2012}.
 The points $(x, y, z)$ located on the surface of this ellipsoidal body
@@
 (Fig. \ref{fig:orientation-angles}b), respectively.
-These unit vectors are commonly described in terms of auxiliary
-orientation angles $\alpha$, $\gamma$, and $delta$, which are not used
-by the geoscientific community. These angles, however, can be defined from
-$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a)
-as follows \citep{clark1986}:
-\begin{equation}
-\alpha = \varepsilon - \cos^{-1} \left[ \frac{\cos \eta}
-{\left( 1 - \sin^{2} \zeta \, \sin^{2} \eta \right)^{\frac{1}{2}}}\right] \: ,
-\label{eq:alpha}
-\end{equation}
-\begin{equation}
-\gamma = \tan^{-1} \left( \frac{\cos \zeta}{\sin \zeta \, \cos \eta}\right)
-\label{eq:gamma}
+The matrix $\mathbf{V}$ can be defined in terms of three rotation matrices:
+\begin{equation}
+\mathbf{R}_{1}(\theta) = \left[ \begin{array}{ccc}
+1 & 0 & 0 \\
+0 & \cos \theta & \sin \theta \\
+0 & -\sin \theta & \cos \theta
+\end{array} \right] \: ,
+\label{eq:R1}
+\end{equation}
+\begin{equation}
+\mathbf{R}_{2}(\theta) = \left[ \begin{array}{ccc}
+\cos \theta & 0 & -\sin \theta \\
+0 & 1 & 0 \\
+\sin \theta & 0 & \cos \theta
+\end{array} \right]
+\label{eq:R2}
 \end{equation}
@@
 \begin{equation}
-\delta = \sin^{-1} \left( \sin \zeta \, \sin \eta \right) \: ,
-\label{eq:delta}
-\end{equation}
-where $-90^{\circ} \leq \gamma \leq 90^{\circ}$ and
-$0 \leq \delta \leq 90^{\circ}$.
-Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$
-(Fig. \ref{fig:orientation-angles}a), we define the auxiliary angles
-$\alpha$, $\gamma$ and $\delta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
-\ref{eq:delta}) and, finally, the unit vectors
-$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-(Fig. \ref{fig:orientation-angles}b) according to the ellipsoid type.
+\mathbf{R}_{3}(\theta) = \left[ \begin{array}{ccc}
+\cos \theta & \sin \theta & 0 \\
+-\sin \theta & \cos \theta & 0 \\
+0 & 0 & 1
+\end{array} \right] \: .
+\label{eq:R3}
+\end{equation}
 For triaxial ellipsoids (i.e., $a > b > c$) and prolate ellipsoids
-(i.e., $a > b = c$), we opted for defining these unit vectors
-by following \citet{clark1986}:
-\begin{equation}
-\mathbf{v}_{1} = \left[\begin{array}{c}
-                  -\cos\alpha \; \cos\delta \\
-                  -\sin\alpha \; \cos\delta \\
-                  -\sin\delta
-                  \end{array} \right] \: ,
-\label{eq:v1_triaxial_prolate}
-\end{equation}
-\begin{equation}
-\mathbf{v}_{2} = \left[\begin{array}{c}
-                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\
-                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\
-                  -\cos\gamma \; \cos\delta
-                  \end{array} \right] \: ,
-\label{eq:v2_triaxial_prolate}
-\end{equation}
-\begin{equation}
-\mathbf{v}_{3} = \left[\begin{array}{c}
-                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\
-                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
-                  \sin\gamma \; \cos\delta
-                  \end{array} \right] \: .
-\label{eq:v3_triaxial_prolate}
-\end{equation}
-\citet{emerson1985} calculated the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
-and $\mathbf{v}_{3}$ similarly by using Eqs. \ref{eq:v1_triaxial_prolate},
-\ref{eq:v2_triaxial_prolate}, and \ref{eq:v3_triaxial_prolate}, but
-with $\gamma = 0^{\circ}$.
-Finally, we define the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
-and $\mathbf{v}_{3}$ for oblate ellipsoids (i.e., $a < b = c$) as follows:
-\begin{equation}
-\mathbf{v}_{1} = \left[\begin{array}{c}
-                  -\cos\alpha \; \sin\gamma \; \sin\delta + \sin\alpha \; \cos\gamma \\
-                  -\sin\alpha \; \sin\gamma \; \sin\delta - \cos\alpha \; \cos\gamma \\
-                  \sin\gamma \; \cos\delta
-                  \end{array} \right] \: ,
-\label{eq:v1_oblate}
-\end{equation}
-\begin{equation}
-\mathbf{v}_{2} = \left[\begin{array}{c}
-                  -\cos\alpha \; \cos\delta \\
-                  -\sin\alpha \; \cos\delta \\
-                  -\sin\delta
-                  \end{array} \right] \: ,
-\label{eq:v2_oblate}
-\end{equation}
-\begin{equation}
-\mathbf{v}_{3} = \left[\begin{array}{c}
-                  \sin\alpha \; \sin\gamma + \cos\alpha \; \cos\gamma \; \sin\delta \\
-                  -\cos\alpha \; \sin\gamma + \sin\alpha \; \cos\gamma \; \sin\delta \\
-                  -\cos\gamma \; \cos\delta
-                  \end{array} \right] \: .
-\label{eq:v3_oblate}
-\end{equation}
-This approach is very similar to that presented by \citet{emerson1985}.
+(i.e., $a > b = c$), we define the orthogonal matrix $\mathbf{V}$
+as follows:
+\begin{equation}
+\mathbf{V} =
+\mathbf{R}_{1} \left( \frac{\pi}{2} \right) \;
+\mathbf{R}_{2} \left( \varepsilon \right) \;
+\mathbf{R}_{1} \left( \frac{\pi}{2} - \zeta \right) \;
+\mathbf{R}_{3} \left( \eta \right) \: .
+\label{eq:V_triaxial_prolate}
+\end{equation}
+For oblate ellipsoids (i.e., $a < b = c$), we define $\mathbf{V}$ as follows:
+\begin{equation}
+\mathbf{V} =
+\mathbf{R}_{3} \left( -\frac{\pi}{2} \right) \;
+\mathbf{R}_{1} \left( \pi \right) \,
+\mathbf{R}_{3} \left( \varepsilon \right) \,
+\mathbf{R}_{2} \left( \frac{\pi}{2} - \zeta \right) \,
+\mathbf{R}_{1} \left( \eta \right) \: .
+\label{eq:V_oblate}
+\end{equation}
+The orthogonal matrices $\mathbf{V}$ used here for triaxial, prolate and oblate
+ellipsoids (Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}) are
+different from that used by \citet{emerson1985} and \citet{clark1986}.
 
@@
 \textit{principal directions}.
-The unit vectors $\mathbf{u}_{i}$ may be defined
-similarly to $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
-and $\mathbf{v}_{3}$ (Eqs. \ref{eq:v1_triaxial_prolate},
-\ref{eq:v2_triaxial_prolate}, \ref{eq:v3_triaxial_prolate},
-\ref{eq:v1_oblate}, \ref{eq:v2_oblate}, and \ref{eq:v3_oblate}),
-by a given set of orientation angles $\varepsilon$, $\zeta$,
-and $\eta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
-\ref{eq:delta}).
+Similarly to the matrix $\mathbf{V}$ (Eqs. \ref{eq:ellipsoid_surface},
+\ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}), we define
+the matrix $\mathbf{U}$ as a function
+of given orientation angles $\varepsilon$, $\zeta$,
+and $\eta$ depending on the ellipsoid type. For triaxial
+and prolate ellipsoids, we define $\mathbf{U}$ by
+using Eq. \ref{eq:V_triaxial_prolate}, whereas for oblate ellipsoids
+we use Eq. \ref{eq:V_oblate}.
+Notice that the orientation angles $\varepsilon$, $\zeta$,
+and $\eta$ defining the orthogonal matrix $\mathbf{U}$
+may be different from that angles $\varepsilon$, $\zeta$,
+and $\eta$ defining the ellipsoid orientation
+(Fig. \ref{fig:orientation-angles}).
 
@@
 
-%The angular difference $\theta$ between the resultant magnetization
-%and the inducing field is the same, whether the quantities
-%are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
-%or local coordinate system (Fig. \ref{fig:orientation-angles}b).
-%For convenience, we define $\theta$ (in degrees) in the main coordinate system
-%by using the scalar product definition as follows:
-%\begin{equation}
-%\theta = \frac{180}{\pi} \, \cos^{-1} \left(
-%\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
-%{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
-%\label{eq:theta}
-%\end{equation}
-%where $\mathbf{M}$ is obtained by pre-multiplying the
-%magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
-%by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
-%which is defined according to the ellipsoid type, and
-%$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
-%
 For the particular case in which the susceptibility is isotropic,
@@
 \section{Numerical simulations}
+
+All the code developed for generating the results presented in the following
+subsections, as well as the code developed for generating additional numerical simulations,
+can be found at the folder \textit{code} of the repository
+\url{https://github.com/pinga-lab/magnetic-ellipsoid}.
 
@@
 
+The code used for generating the results presented in this section
+can found at \url{https://github.com/pinga-lab/magnetic-ellipsoid/code}
+
 \subsection{Simulation of a geological body}
 
+We simulated an ellipsoidal body similar to the Warrego orebody,
+which was the resource on which the well-known Warrego mine was
+developed in Tennant Creek, Australia. After nearly a decade as
+one of the most important gold and copper mines in Australia, the
+Warrego mine was closed in late 1989.
+According to \citet{wedekind1990}, the Warrego orebody is a combination of
+two major and several small ironstone lodes, which are discrete bodies
+comprised predominantly of magnetite or hematite above the base of
+oxidation.
 \citet{farrar1979} represented the Warrego orebody as a triaxial
@@
 magnetic modelling of this body.
-According to \citet{wedekind1990}, the Warrego orebody is a combination of
-two major and several small ironstone lodes, which are discrete bodies
-comprised predominantly of magnetite or hematite above the base of
-oxidation.
-The Warrego orebody was the resource on which the Warrego mine was
-developed. After nearly a decade as one of the most important
-gold and copper mines in Australia, the Warrego mine was closed
-in late 1989.
 
@@
 points at a constant vertical coordinate $z = 0$ \unit{m}.
-The total-field anomaly varies from $\approx -176$ \unit{nT}
-to $\approx 237$ \unit{nT}, resulting in a peak-to-peak amplitude
-of $\approx 413$ \unit{nT}, and was calculated by using the
+The total-field anomaly varies from $\approx -71$ \unit{nT}
+to $\approx 482$ \unit{nT}, resulting in a peak-to-peak amplitude
+of $\approx 553$ \unit{nT}, and was calculated by using the
 true magnetization $\mathbf{M}$ defined in Eqs.
@@
 susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
-The peak-to-peak amplitude is $\approx 141$ \unit{nT}
-and represents $\approx 34 \%$ of the peak-to-peak amplitude of
+The peak-to-peak amplitude is $\approx 40$ \unit{nT}
+and represents $\approx 8 \%$ of the peak-to-peak amplitude of
 the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
-This result reinforces that the use of the approximated magnetization
-$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
-the magnetic modelling of bodies with high isotropic susceptibility.
+%This result reinforces that the use of the approximated magnetization
+%$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
+%the magnetic modelling of bodies with high isotropic susceptibility.
 
@@
 In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
-$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.4 \%$
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 0.7 \%$
 (Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
 The peak-to-peak amplitude of the differences in the total-field anomaly
-(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 0.8$ \unit{nT},
-which represents $\approx 2.9 \%$ of the peak-to-peak amplitude of the
+(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 0.2$ \unit{nT},
+which represents $\approx 0.6 \%$ of the peak-to-peak amplitude of the
 total-field anomaly calculates by using the true magnetization $\mathbf{M}$
@@
 In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
-$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.8 \%$
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 0.8 \%$
 (Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
 The peak-to-peak amplitude of the differences in the total-field anomaly
-(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 1.1$ \unit{nT},
-which represents $\approx 3.3 \%$ of the peak-to-peak amplitude of the
+(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 0.3$ \unit{nT},
+which represents $\approx 0.7 \%$ of the peak-to-peak amplitude of the
 total-field anomaly calculates by using the true magnetization $\mathbf{M}$
@@
 which contains the $x$ and $y$ axes. The angle $\varepsilon$
-between "minus $x$" and the strike direction is called \textit{strike}.
+between the $x$-axis and the strike direction is called \textit{strike}.
 The angle $\zeta$ between the horizontal plane and the dark gray plane
-is called \textit{dip}. The line containing the unit vector
-$\mathbf{u}$ defines the \textit{plunge direction}.
-The angle $\eta$ between the strike direction and the plunge direction
-is called \textit{rake}. The projection
-of the plunge direction on the horizontal plane is called
-\textit{plunge azimuth direction}. (b) Local coordinate system
+is called \textit{dip}. The angle $\eta$ between the strike direction
+and the line containing the unit vector $\mathbf{u}$
+is called \textit{rake}. The projection of this line on the
+horizontal plane (not shown) is called \textit{dip direction}
+\citep{pollard2005, allmendinger2012}. (b) Local coordinate system
 with origin at the ellipsoid centre $(x_{c}, y_{c}, z_{c})$

### 2017-04-20 manuscript/manuscript.tex

@@
 subsections, as well as the code developed for generating additional numerical simulations,
-can be found at the folder \textit{code} of the repository
+can be found at the folder \textit{code} of the online repository
 \url{https://github.com/pinga-lab/magnetic-ellipsoid}.
@@
 of $m$.
-
-The code used for generating the results presented in this section
-can found at \url{https://github.com/pinga-lab/magnetic-ellipsoid/code}
 

### 2017-05-11 manuscript/manuscript.tex
replace vkj by vjk in equation A1

@@
 In a future work,
-it would be interesting to use a similar approach to
-to bound the maximum relative error in the
+it would be interesting to use a similar approach
+to determine bounds for the maximum relative error in the
 magnetic field calculated by neglecting the self-demagnetization.
 
-This work also provide a set of routines to model the magnetic
+This work also provides a set of routines to model the magnetic
 field produced by ellipsoids.
-The routines are written in Python language as part of
-the Fatiando a Terra \citep{uieda2013}, which is an
+The routines are written in the Python language as part of
+the Fatiando a Terra \citep{uieda2013}
 open-source library for modelling and inversion in geophysics.
 The current version of our code is freely distributed
-in a repository of GitHub. We are working to integrate our
-routines in the following stable release of Fatiando a Terra.
-We hope that these routines be useful to the wide geoscientific
-community either in researching and teaching.
+in a repository hosted on the GitHub website. We are working to integrate our
+routines in the next stable release of Fatiando a Terra.
+We hope that these routines will be useful to the wide geoscientific
+community, either for research or for teaching.
 
@@
 \begin{equation}
-\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
+\tilde{r}_{k} = v_{1k} \, r_{1} + v_{2k} \, r_{2} + v_{3k} \, r_{3} + c_{k} \: ,
 \label{eq:r-tilde-k}
@@
 $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
-$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
+$v_{jk}$, $j = 1, 2, 3$, are the elements of the matrix
 $\mathbf{V}$ (Eq. \ref{eq:A}),

### 2017-05-31 manuscript/manuscript.tex
Correcao das duas primeiras sugestoes do CLark. Inclui finite na linha 5 e inclui informacoes sobre a existencia de softwares fechados que incluem o modelo elipsoidal na linha 27 da segunda página. Tambem corrigi na pagina 7 na secao 2.4.1 do tensor de depolarizacao que representa um ponto calculado dentro e nao fora do elipsoide.

@@
 uniformly magnetized in the presence of a uniform inducing field and
-are the only bodies for which the self-demagnetization can be treated
+are the only finite bodies for which the self-demagnetization can be treated
 analytically. This property makes ellipsoids particularly useful for
@@
 field.
-Besides, the geoscientific community lacks an easy-to-use
+Besides, the geoscientific community lacks an free easy-to-use
 tool to simulate the magnetic field produced by uniformly
-magnetized ellipsoids.
+magnetized ellipsoids. There are some commercial software
+packages that includes the ellipsoid model, but all very
+expensive.
 Such a tool could prove to be useful either for teaching
@@
 $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
-represents a point located outside
+represents a point located inside
 the ellipsoidal body. In this case,

### 2017-06-05 manuscript/manuscript.tex
Correcao ortografica - a free... Exclusao de -there are some commercial... na introducao. Notebook para verificar o ponto 3 do comentario da revisao.

@@
 field.
-Besides, the geoscientific community lacks an free easy-to-use
+Besides, the geoscientific community lacks a free easy-to-use
 tool to simulate the magnetic field produced by uniformly
-magnetized ellipsoids. There are some commercial software
-packages that includes the ellipsoid model, but all very
-expensive.
+magnetized ellipsoids. Software packages that includes the 
+ellipsoid model exist, but all very expensive.
 Such a tool could prove to be useful either for teaching

### 2017-06-08 manuscript/manuscript.tex
include a section about the ambiguity between confocal ellipsoids

@@
-%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
+% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
 %% ---------------------------------
@@
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
+
 Equation \ref{eq:M-tilde} can be easily generalized for the case in
@@
 user-specified relative error $\epsilon$.
+
+\subsubsection{Ambiguity between confocal ellipsoids with the same magnetic moment}
+
+There is a fundamental non-uniqueness of ellipsoidal bodies, analogous to the
+equivalence of concentric spheres with the same magnetic moment.
+To show this ambiguity, let us first
+consider an ellipsoid which is immersed in a uniform inducing
+field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
+and no remanence.
+The magnetization of this ellipsoid, defined in the local coordinate system,
+can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde}, and \ref{eq:M-tilde}
+as follows:
+\begin{equation}
+\tilde{\mathbf{M}} = \chi \left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} 
+\right)^{-1} \tilde{\mathbf{H}}_{0} \: .
+\label{eq:M-tilde-K-isotropic}
+\end{equation}
+In this case, the magnetic moment $\tilde{\mathbf{P}}$, defined in the
+local coordinate system, is given by
+\begin{equation}
+\tilde{\mathbf{P}} = \vartheta \tilde{\mathbf{M}} \: ,
+\label{eq:P-tilde}
+\end{equation}
+where $\vartheta = \frac{4}{3}\pi a b c$ is the ellipsoid volume.
+From Eqs. \ref{eq:M-tilde-K-isotropic} and \ref{eq:P-tilde},
+we can easily show that, if the inducing field $\tilde{\mathbf{H}}_{0}$
+is parallel to a semi-axis $e_{i}$, where $i = 1, 2, 3$, $e_{1} = a$, $e_{2} = b$,
+$e_{3} = c$, only the $i$th component $P_{i}$ of the magnetic moment $\tilde{\mathbf{P}}$
+is non null and given by
+\begin{equation}
+P_{i} = \vartheta \frac{\chi \, H_{0}}{1 + \chi \, \tilde{n}^{\dagger}_{ii}} \: ,
+\label{eq:P-tilde-i}
+\end{equation}
+where $H_{0}$ is the intensity of the inducing field $\tilde{\mathbf{H}}_{0}$
+and the demagnetizing factor $\tilde{n}^{\dagger}_{ii}$ is defined
+by Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
+or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
+
+Now, consider a confocal ellipsoid with semi-axes $a^{\prime} = \sqrt{a^2+u}$,
+$b^{\prime} = \sqrt{b^2+u}$, and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
+positive real number. From Eq. \ref{eq:P-tilde-i}, we can define the
+isotropic susceptibility $\chi^{\prime}$ that is necessary to this confocal
+ellipsoid produce the same magnetic moment $\tilde{\mathbf{P}}$ (Eq. \ref{eq:P-tilde})
+as follows:
+\begin{equation}
+\chi^{\prime} = \frac{P_{i}}{\vartheta^{\prime} \, H_{0} - \tilde{n}^{\dagger}_{ii} \, P_{i}} \: ,
+\label{eq:chi-prime}
+\end{equation}
+where $\vartheta^{\prime} = \frac{4}{3}\pi a^{\prime} b^{\prime} c^{\prime}$ and
+$\tilde{n}^{\dagger}_{ii}$ is the new demagnetizing factor computed for the
+confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
+or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
+It can be shown that this confocal ellipsoid produce the same magnetic field
+as the ellipsoid with semi-axes $a$, $b$, and $c$.
+
+This ambiguity between confocal ellipsoids with the same magnetic moment
+has already been pointed out by Clark (2014) and is verified for the
+particular case in which the uniform inducing field is parallel
+to an ellipsoid axis.
+Otherwise, the magnetic field produced by the confocal ellipsoids
+will be different due to the shape anisotropy.
 

### 2017-06-09 manuscript/manuscript.tex
modify the code readme and include the new test about ambiguity in the manuscript

@@
 remanent magnetization, as well as with isotropic or anisotropic
-susceptibility. We also propose a
+susceptibility. We also discuss the ambiguity between confocal ellipsoids
+with the same magnetic moment and propose a
 way of determining the isotropic susceptibility above which the
@@
 To show this ambiguity, let us first
-consider an ellipsoid which is immersed in a uniform inducing
+consider a reference ellipsoid which is immersed in a uniform inducing
 field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
@@
 It can be shown that this confocal ellipsoid produce the same magnetic field
-as the ellipsoid with semi-axes $a$, $b$, and $c$.
+as the reference ellipsoid.
 
 This ambiguity between confocal ellipsoids with the same magnetic moment
-has already been pointed out by Clark (2014) and is verified for the
+has already been pointed out by Clark (2014). It occurs for the
 particular case in which the uniform inducing field is parallel
-to an ellipsoid axis.
+to an ellipsoid axis and there is no remanence.
 Otherwise, the magnetic field produced by the confocal ellipsoids
@@
 
-We simulate a triaxial ellipsoid with semi-axes
+We simulated a triaxial ellipsoid with semi-axes
 $a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
-Then we use this ellipsoid as a reference to generate
+Then we used this ellipsoid as a reference to generate
 100 different triaxial ellipsoids and calculate
@@
 of $m$.
+
+\subsection{Confocal ellipsoids}
+
+We simulated two confocal ellipsoids by using the parameters
+shown in Tab. \ref{tab:parameters-confocal-ellipsoids}.
+The semi-axes of the Ellipsoid 2 were defined as $\sqrt{a^{2} + u}$,
+$\sqrt{b^{2} + u}$, and $\sqrt{c^{2} + u}$, where $a$, $b$, and $c$
+are the semi-axes of the Ellipsoid 1 and $u = 2 \times 10^{6}$ \unit{m}.
+
+We have computed the total-field anomalies produced by the Ellipsoid 1
+and Ellipsoid 2 at the same regular grid of $200 \times 200$ points
+located on a horizontal plane at $z = 0$ \unit{m} by using two different
+inducing fields $\mathbf{H}_{0}$.
+
+In the first case, we used an uniform inducing field $\mathbf{H}_{0}$ which is
+parallel to the semi-axis $a$ of the confocal ellipsoids and
+has inclination $\approx -4.98^{\circ}$, declination $\approx 15.38^{\circ}$,
+and intensity $H_{0} \approx 18.7$ \unit{A \, m^{-1}}.
+The total-field anomaly produced by the Ellipsoid 1 by using this
+inducing field is shown in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-parallel}.
+In this case, the Ellipsoid 2 produces the same total-field
+anomaly as the Ellipsoid 1.
+The isotropic susceptibility of the Ellipsoid 2 was calculated with
+Eq. \ref{eq:chi-prime} and, consequently, its magnetic moment is equal
+to that of the Ellipsoid 1.
+Notice that the volume of the Ellipsoid 2 is approximately $79$ times greater
+than that of the Ellipsoid 1, whereas the isotropic susceptibility
+of the Ellipsoid 1 is approximately $85$ times greater than that
+of the Ellipsoid 2.
+This result illustrates the ambiguity between the field produced
+by confocal ellipsoids with the same magnetic moment.
+
+The second inducing field $\mathbf{H}_{0}$ used is oblique to
+the semi-axes of the confocal ellipsoids, has the same
+intensity as the other one, but a different direction.
+In this case, the inclination and declination of $\mathbf{H}_{0}$
+are, respectively, $-30^{\circ}$ and $60^{\circ}$.
+Figures \ref{fig:tfa-confocal-ellipsoids-H0-oblique}a and
+\ref{fig:tfa-confocal-ellipsoids-H0-oblique}b show the total-field anomalies
+produced, respectively, by the Ellipsoid 1 and Ellipsoid 2
+by using this new inducing field $\mathbf{H}_{0}$.
+Notice that by using this oblique inducing field, 
+the total-field anomalies produced by the confocal ellipsoids
+are different to each other due to the shape anisotropy.
+The differences are show in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-oblique}c.
+These results confirm numerically what was pointed out by
+\cite{clark2014}: confocal ellipsoids with
+properly scaled isotropic susceptibilities, no remanence and
+the same magnetic moment produce different magnetic fields at the
+same external points, unless the inducing field happens to lie along one
+of their axes.
 
@@
 oblate ellipsoids.
-We also present a theoretical discussion about the
+We also present a numerical simulation confirming the
+ambiguity between confocal ellipsoids with the same magnetic moment
+and present a theoretical discussion about the
 determination of the isotropic susceptibility value above which
@@
 \begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_parallel_field.pdf}
+\caption{Total-field anomaly (in \unit{nT}) produced by the 
+synthetic bodies Ellipsoid 1 and Ellispoid 2, both
+defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
+The synthetic data produced by these confocal ellipsoids
+were calculated on a regular grid of $200 \times 200$ points
+at the constant vertical coordinate $z = 0$ \unit{m}.
+These data were calculated with an uniform inducing field
+parallel to the semi-axis $a$ of the confocal ellipsoids.}
+\label{fig:tfa-confocal-ellipsoids-H0-parallel}
+\end{figure}
+
+%f
+\begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_oblique_field.pdf}
+\caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
+and (b) Ellipsoid 2, both defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
+The synthetic data produced by these confocal ellipsoids
+were calculated on a regular grid of $200 \times 200$ points
+at the constant vertical coordinate $z = 0$ \unit{m}.
+These data were calculated with an uniform inducing field
+which is oblique to the semi-axes of the confocal ellipsoids.
+(c) Difference between the total-field anomalies shown in
+b and a.}
+\label{fig:tfa-confocal-ellipsoids-H0-oblique}
+\end{figure}
+
+%f
+\begin{figure}[t]
 \includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
-\caption{Total-field anomaly produced by the synthetic orebody
+\caption{Total-field anomaly (in \unit{nT}) produced by the synthetic orebody
 defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
@@
 (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
-The total-field anomalies are calculated with Eq. \ref{eq:delta-T-approx},
+The total-field anomalies are in \unit{nT} and were
+calculated with Eq. \ref{eq:delta-T-approx},
 on a regular grid of $100 \times 100$ points,
@@
 \newpage
+
+%t
+\begin{table}[t]
+\caption{Parameters defining two confocal ellipsoids.}
+%\begin{tabular}{column = lcr}
+\begin{tabular}{lccr}
+\tophline
+Parameter & Ellipsoid 1 & Ellipsoid 2 & Unit \\
+\middlehline
+Semi-axis $a$ & $900$ & $\approx 1676.31$ & \unit{m} \\
+Semi-axis $b$ & $500$ & $1500$ & \unit{m} \\
+Semi-axis $c$ & $100$ & $\approx 1417.74$ & \unit{m} \\
+Coordinate of the centre $x_{c}$ & 0 & 0 & \unit{m} \\
+Coordinate of the centre $y_{c}$ & 0 & 0 & \unit{m} \\
+Coordinate of the centre $z_{c}$ & 1500 & 1500 & \unit{m} \\
+Orientation angle $\varepsilon$ $^{\ast}$ & $45$ & $45$ & $^{\circ}$ \\
+Orientation angle $\zeta$ $^{\ast}$ & $10$ & $10$ & $^{\circ}$ \\
+Orientation angle $\eta$ $^{\ast}$ & $-30$ & $-30$ & $^{\circ}$ \\
+Isotropic susceptibility $\chi$ & $1.2$ & $\approx 0.014$ & \unit{SI} \\
+\bottomhline
+\end{tabular}
+\belowtable{$^{\ast}$ Defined in Fig. \ref{fig:orientation-angles}a} % Table Footnotes
+\label{tab:parameters-confocal-ellipsoids}
+\end{table}
 

### 2017-06-12 code/mesher.py
timing the routines for computing tf and try to optimize small pieces of code

@@ -204,7 +204,7 @@ susceptibilities must be all positive'
         Calculate the ellipsoid volume.
         '''
 
-        cte = 4*numpy.pi/3 # constant
+        cte = 4*numpy.pi/3  # constant
         volume = cte*self.large_axis*self.intermediate_axis*self.small_axis
         return volume
 
@@ -363,14 +363,13 @@ susceptibilities must be all positive'
         else:
             return None
 
-
     @property
     def volume(self):
         '''
         Calculate the ellipsoid volume.
         '''
 
-        cte = 4*numpy.pi/3 # constant
+        cte = 4*numpy.pi/3  # constant
         volume = cte*self.large_axis*self.small_axis*self.small_axis
         return volume
 
@@ -530,14 +529,13 @@ susceptibilities must be all positive'
         else:
             return None
 
-
     @property
     def volume(self):
         '''
         Calculate the ellipsoid volume.
         '''
 
-        cte = 4*numpy.pi/3 # constant
+        cte = 4*numpy.pi/3  # constant
         volume = cte*self.large_axis*self.large_axis*self.small_axis
         return volume
 

### 2017-06-12 code/prolate_ellipsoid.py

@@ -505,15 +505,19 @@ def x1x2x3(xp, yp, zp, ellipsoid):
     assert xp.size == yp.size == zp.size, \
         'xp, yp and zp must have the same size'
 
-    x1 = ellipsoid.transf_matrix[0, 0]*(xp - ellipsoid.x) + \
-        ellipsoid.transf_matrix[1, 0]*(yp - ellipsoid.y) + \
-        ellipsoid.transf_matrix[2, 0]*(zp - ellipsoid.z)
-    x2 = ellipsoid.transf_matrix[0, 1]*(xp - ellipsoid.x) + \
-        ellipsoid.transf_matrix[1, 1]*(yp - ellipsoid.y) + \
-        ellipsoid.transf_matrix[2, 1]*(zp - ellipsoid.z)
-    x3 = ellipsoid.transf_matrix[0, 2]*(xp - ellipsoid.x) + \
-        ellipsoid.transf_matrix[1, 2]*(yp - ellipsoid.y) + \
-        ellipsoid.transf_matrix[2, 2]*(zp - ellipsoid.z)
+    dx = xp - ellipsoid.x
+    dy = yp - ellipsoid.y
+    dz = zp - ellipsoid.z
+
+    x1 = ellipsoid.transf_matrix[0, 0]*dx + \
+        ellipsoid.transf_matrix[1, 0]*dy + \
+        ellipsoid.transf_matrix[2, 0]*dz
+    x2 = ellipsoid.transf_matrix[0, 1]*dx + \
+        ellipsoid.transf_matrix[1, 1]*dy + \
+        ellipsoid.transf_matrix[2, 1]*dz
+    x3 = ellipsoid.transf_matrix[0, 2]*dx + \
+        ellipsoid.transf_matrix[1, 2]*dy + \
+        ellipsoid.transf_matrix[2, 2]*dz
 
     return x1, x2, x3
 

### 2017-07-10 code/test_prolate_ellipsoid.py
include three tests verifying the field produced by confocal ellipsoids

@@ -282,3 +282,58 @@ def test_prolate_ellipsoid_isotropic_susceptibility():
     strike, dip, rake = model[0].props['susceptibility angles']
     suscep = model[0].susceptibility_tensor
     assert np.allclose(suscep, k1*np.identity(3))
+
+
+def test_confocal_prolate_ellipsoids():
+    "Confocal bodies with properly scaled suscep produce the same field"
+    # Reference ellipsoid
+    a, b, = 1000., 400.  # semi-axes
+    chi = 1.2  # reference susceptibility
+    ellipsoid = ProlateEllipsoid(0., 0., 1500., a, b, 45., 10., -30.,
+                                 {'principal susceptibilities': [chi,
+                                                                 chi,
+                                                                 chi],
+                                  'susceptibility angles': [0., 0., 0.]})
+    # Intensity of the local-geomagnetic field (in nT)
+    B0 = 23500.
+    # Direction parallel to the semi-axis a
+    _, inc, dec = utils.vec2ang(ellipsoid.transf_matrix.T[0])
+    # Magnetic moment of the reference ellipsoid
+    volume = ellipsoid.volume
+    mag = prolate_ellipsoid.magnetization(ellipsoid, B0,
+                                          inc, dec, demag=True)
+    moment = volume*mag
+    # Confocal ellipsoid
+    u = 2.0e6
+    a_confocal = np.sqrt(a*a + u)
+    b_confocal = np.sqrt(b*b + u)
+    xc = ellipsoid.x
+    yc = ellipsoid.y
+    zc = ellipsoid.z
+    strike = ellipsoid.strike
+    dip = ellipsoid.dip
+    rake = ellipsoid.rake
+    confocal_ellipsoid = ProlateEllipsoid(xc, yc, zc,
+                                          a_confocal, b_confocal,
+                                          strike, dip, rake,
+                                          {'susceptibility angles':
+                                           [0., 0., 0.]})
+    n11, n22 = prolate_ellipsoid.demag_factors(confocal_ellipsoid)
+    H0 = B0/(4*np.pi*100)
+    volume_confocal = confocal_ellipsoid.volume
+    # Equivalent susceptibility
+    moment_norm = np.sqrt(np.sum(moment*moment))
+    chi_confocal = moment_norm/(volume_confocal*H0 - n11*moment_norm)
+    confocal_ellipsoid.addprop('principal susceptibilities',
[…]

### 2017-07-10 code/test_triaxial_ellipsoid.py

@@ -15,7 +15,7 @@ dec = 57
 
 gm = 1000  # geometrical factor
 area = [-5.*gm, 5.*gm, -5.*gm, 5.*gm]
-x, y, z = gridder.scatter(area, 300, z=0.)
+x, y, z = gridder.scatter(area, n=300, z=0.)
 axis_ref = gm  # reference semi-axis
 
 # Triaxial ellipsoids used for testing
@@ -286,4 +286,60 @@ def test_triaxial_ellipsoid_isotropic_susceptibility():
     k1, k2, k3 = model[0].props['principal susceptibilities']
     strike, dip, rake = model[0].props['susceptibility angles']
     suscep = model[0].susceptibility_tensor
-    assert np.allclose(suscep, k1*np.identity(3))
+    assert_almost_equal(suscep, k1*np.identity(3), decimal=15)
+
+
+def test_confocal_triaxial_ellipsoids():
+    "Confocal bodies with properly scaled suscep produce the same field"
+    # Reference ellipsoid
+    a, b, c = 900., 500., 100.  # semi-axes
+    chi = 1.2  # reference susceptibility
+    ellipsoid = TriaxialEllipsoid(0., 0., 1500., a, b, c, 45., 10., -30.,
+                                  {'principal susceptibilities': [chi,
+                                                                  chi,
+                                                                  chi],
+                                   'susceptibility angles': [0., 0., 0.]})
+    # Intensity of the local-geomagnetic field (in nT)
+    B0 = 23500.
+    # Direction parallel to the semi-axis a
+    _, inc, dec = utils.vec2ang(ellipsoid.transf_matrix.T[0])
+    # Magnetic moment of the reference ellipsoid
+    volume = ellipsoid.volume
+    mag = triaxial_ellipsoid.magnetization(ellipsoid, B0,
+                                           inc, dec, demag=True)
+    moment = volume*mag
+    # Confocal ellipsoid
+    u = 2.0e6
+    a_confocal = np.sqrt(a*a + u)
+    b_confocal = np.sqrt(b*b + u)
+    c_confocal = np.sqrt(c*c + u)
+    xc = ellipsoid.x
+    yc = ellipsoid.y
+    zc = ellipsoid.z
+    strike = ellipsoid.strike
+    dip = ellipsoid.dip
+    rake = ellipsoid.rake
+    confocal_ellipsoid = TriaxialEllipsoid(xc, yc, zc,
+                                           a_confocal, b_confocal, c_confocal,
[…]

### 2017-07-10 manuscript/manuscript.tex
include the reference soliverez2016

@@
 tool to simulate the magnetic field produced by uniformly
-magnetized ellipsoids. Software packages that includes the 
-ellipsoid model exist, but all very expensive.
+magnetized ellipsoids.
 Such a tool could prove to be useful either for teaching
@@
 The matrix $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform})
-is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008}.
+is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008, soliverez2016}.
 
@@
 $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
-supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
+supported \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
 postulate about uniformly magnetized ellipsoids.

### 2017-07-10 manuscript/manuscript.tex
include a link to zenodo

@@
 
-The current version of our code is freely distributed, under the
-BSD 3-clause licence, in a repository on GitHub
-(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
+The current version of our code is freely distributed under the
+BSD 3-clause licence and it is available for at 
+Zenodo (\url{http://doi.org/10.5281/zenodo.825261}). The latest
+development version of our code can be freely downloaded from
+a repository on GitHub (\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
 Instructions for running the current version of our code
-are also provided in the repository.
+are also provided on the repository.
+The code is still being improved and we encourage the user to 
+work with the latest development version.
 The code was developed as part of the Fatiando a Terra

### 2017-07-24 manuscript/manuscript.tex
small change in the code availability section

@@
 The current version of our code is freely distributed under the
-BSD 3-clause licence and it is available for at 
+BSD 3-clause licence and it is available for download at 
 Zenodo (\url{http://doi.org/10.5281/zenodo.825261}). The latest

### 2017-08-10 manuscript/manuscript.tex
cite our code at Zenodo

--- 2017-07-10 manuscript/manuscript.tex
@@
 These formulas can be obtained by properly manipulating those
-presented by \citep{emerson1985}.
+presented by \citet{emerson1985}.
 
@@
 these formulas can be obtained by properly manipulating those
-presented by \citep{emerson1985}.
+presented by \citet{emerson1985}.
 
@@
 The current version of our code is freely distributed under the
-BSD 3-clause licence and it is available for at 
-Zenodo (\url{http://doi.org/10.5281/zenodo.825261}). The latest
+BSD 3-clause licence and it is available for download at 
+Zenodo:  \url{http://doi.org/10.5281/zenodo.825261} \citep{tomazella2017}. The latest
 development version of our code can be freely downloaded from

### 2017-08-22 manuscript/manuscript.tex
change figure names for uploading the final files

@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/structural_orientation_angles.png}
+\includegraphics[width=8.3cm]{figures/f01.png}
 \caption{Schematic representation of the coordinate systems used to
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
+\includegraphics[width=8.3cm]{figures/f02.pdf}
 \caption{(a) Comparison between the demagnetizing factors
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_parallel_field.pdf}
+\includegraphics[width=8.3cm]{figures/f03.pdf}
 \caption{Total-field anomaly (in \unit{nT}) produced by the 
-synthetic bodies Ellipsoid 1 and Ellispoid 2, both
+synthetic bodies Ellipsoid 1 and Ellipsoid 2, both
 defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_oblique_field.pdf}
+\includegraphics[width=8.3cm]{figures/f04.pdf}
 \caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
+\includegraphics[width=8.3cm]{figures/f05.pdf}
 \caption{Total-field anomaly (in \unit{nT}) produced by the synthetic orebody
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/field_differences.pdf}
+\includegraphics[width=8.3cm]{figures/f06.pdf}
 \caption{Difference between the total-field

### 2017-09-25 manuscript/manuscript.tex
final proofreading version

@@
 
-\title{Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies}
+\title{Ellipsoids (v1.0): 3D magnetic modelling of ellipsoidal bodies}
 
@@
 
-\Author[1]{Diego}{Takahashi Tomazella}
+\Author[1]{Diego}{Takahashi}
 \Author[1]{Vanderlei}{C. Oliveira Jr.}
@@
 
-\runningauthor{Tomazella and Oliveira Jr.}
+\runningauthor{D. Takahashi and V. C. Oliveira Jr.}
 
@@
 empirically and there has been no discussion about how this value was
-determined. Besides, the geoscientific community lacks an easy-to-use
+determined. In addition, the geoscientific community lacks an easy-to-use
 tool to simulate the magnetic field produced by uniformly magnetized
@@
 defined as limiting cases of an ellipsoid
-(e.g., spheres, elliptic cylinders), however all the
+(e.g. spheres, elliptic cylinders). However all the
 remaining non-ellipsoidal bodies cannot be
@@
 the only bodies which enable an analytical computation
-of its self-demagnetization.
-The self-demagnetization contributes to decrease the
+of their self-demagnetization.
+The self-demagnetization contributes to a decrease in the
 magnitude of the magnetization along the shortest
 axes of a body.
-It is a function of the body shape and gives rise
+This a function of the body shape and gives rise
 to shape anisotropy \citep{uyeda1963, thompson1986,
 dunlop1997, clark1999, tauxe2003}.
-It is well-established in the literature that
+It is well established in the literature that
 the self-demagnetization can be neglected if the
@@
 Australia.
-Posteriorly, \citet{hoschke1991} also showed how the
+Later, \citet{hoschke1991} also showed how the
 ellipsoidal model proved to be highly successful in
@@
 According to \citet{clark2000}, neglecting the effects
-of self-demagnetisation led errors of $\approx 55^{\circ}$
+of self-demagnetisation led to errors of $\approx 55^{\circ}$
 in the interpreted dip.
@@
 field.
-Besides, the geoscientific community lacks a free easy-to-use
+Furthermore, the geoscientific community lacks a free easy-to-use
 tool to simulate the magnetic field produced by uniformly
 magnetized ellipsoids.
-Such a tool could prove to be useful either for teaching
+Such a tool could prove useful both for teaching
 and researching geophysics.
@@
 We attempt to use the best practices of continuous
-integration, documentation, unit-testing, and version-control
+integration, documentation, unit-testing and version-control
 for the purpose of providing a reliable and easy-to-use
@@
 Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
-$x$, $y$ and $z$ pointing to, respectively, North, East and down.
-For convenience, we denominate this coordinate system as
+$x$, $y$ and $z$ pointing to, respectively, north, east and down.
+For convenience, we denominate this coordinate system as the
 \textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
@@
 $(x_{c}, y_{c}, z_{c})$, orientation defined by the angles
-\textit{strike} $\varepsilon$, \textit{dip} $\zeta$, and \textit{rake} $\eta$
+\textit{strike} $\varepsilon$, \textit{dip} $\zeta$ and \textit{rake} $\eta$
 (Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
 positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
-The orientation angles \textit{strike}, \textit{dip}, and \textit{rake}
+The orientation angles \textit{strike}, \textit{dip} and \textit{rake}
 are commonly used to define the orientation of lines in structural geology
@@
 and $\mathbf{V}$ is an orthogonal matrix whose first, second and third columns
-are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$
 (Fig. \ref{fig:orientation-angles}b), respectively.
@@
 \end{equation}
-For triaxial ellipsoids (i.e., $a > b > c$) and prolate ellipsoids
-(i.e., $a > b = c$), we define the orthogonal matrix $\mathbf{V}$
+For triaxial ellipsoids (i.e. $a > b > c$) and prolate ellipsoids
+(i.e. $a > b = c$), we define the orthogonal matrix $\mathbf{V}$
 as follows:
@@
 \end{equation}
-For oblate ellipsoids (i.e., $a < b = c$), we define $\mathbf{V}$ as follows:
+For oblate ellipsoids (i.e. $a < b = c$), we define $\mathbf{V}$ as follows:
 \begin{equation}
@@
 ellipsoids (Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}) are
-different from that used by \citet{emerson1985} and \citet{clark1986}.
+different from those used by \citet{emerson1985} and \citet{clark1986}.
 
@@
 For convenience, we denominate this particular coordinate
-system as \textit{local coordinate system}.
+system as the \textit{local coordinate system}.
 The relationship between the Cartesian coordinates
@@
 coordinates $(x, y, z)$ of the same point in the main
-system is given by:
+system is given by
 \begin{equation}
@@
 (Eq. \ref{eq:A}) is defined according to the ellipsoid type.
-Subsequently, quantities referred to the local coordinate system
-(Fig. \ref{fig:orientation-angles}b) are represented with
-the simbol "$\sim$".
+In what follows, quantities referred to the local coordinate system
+(Fig. \ref{fig:orientation-angles}b) are indicated with
+the symbol "$\sim$".
 
@@
 where $\| \cdot \|$ denotes the Euclidean norm (or 2-norm) and
-$D$ and $I$ are respectively, the declination and inclination of the
-local-geomagnetic field in the main coordinate system
+$D$ and $I$ are respectively the declination and inclination of the
+local geomagnetic field in the main coordinate system
 (Fig. \ref{fig:orientation-angles}a).
@@
 where the second term is the negative gradient of
-the magnetic scalar potential $V(\mathbf{r})$ given by:
+the magnetic scalar potential $V(\mathbf{r})$ given by
 \begin{equation}
@@
 at any point within the body and $\mathbf{K}$ is a
-constant and symmetrical 2nd-order tensor representing the
+constant and symmetrical second-order tensor representing the
 magnetic susceptibility of the body.
@@
 the matrix $\mathbf{U}$ as a function
-of given orientation angles $\varepsilon$, $\zeta$,
+of given orientation angles $\varepsilon$, $\zeta$
 and $\eta$ depending on the ellipsoid type. For triaxial
@@
 and $\eta$ defining the orthogonal matrix $\mathbf{U}$
-may be different from that angles $\varepsilon$, $\zeta$,
+may be different from the angles $\varepsilon$, $\zeta$
 and $\eta$ defining the ellipsoid orientation
@@
 anisotropy of magnetic susceptibility (AMS).
-The AMS is generally associated to the preferred orientation
+The AMS is generally associated with the preferred orientation
 of the grains of magnetic minerals forming the rock
@@
 \end{equation}
-$r_{1} = x$, $r_{2} = y$, $r_{3} = z$ are the elements of
+where $r_{1} = x$, $r_{2} = y$, $r_{3} = z$ are the elements of
 the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
@@
 The matrix $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform})
-is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008, soliverez2016}.
+is called the \textit{depolarization tensor} \citep{soliverez1981, soliverez2008, soliverez2016}.
 
@@
 produced by homogeneous ellipsoids.
-Posteriorly, several authors also deduced and used this function
+Later, several authors also deduced and used this function
 for describing the magnetic and gravitational fields produced
@@
 is a quadratic function of the spatial coordinates
-$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
+$\tilde{x}$, $\tilde{y}$ and $\tilde{z}$, which
 supported \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
@@
 ellipsoid type as a function of the spatial coordinates
- $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ (see Appendix B).
+ $\tilde{x}$, $\tilde{y}$ and $\tilde{z}$ (see Appendix B).
 For readers interested in additional information about the
@@
 \end{equation}
-where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$,
+where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$
 and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
@@
 vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}).
-Besides, the off-diagonal elements are zero and
+Also, the off-diagonal elements are zero and
 the diagonal elements are given by \citep{stoner1945}:
@@
 Here, we calculate the demagnetizing factors in the \unit{SI}
-system. Consequently, they satisfies the condition
+system. Consequently, they satisfy the condition
 $\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} +
@@
 
-Notice that, according to Eqs. \ref{eq:H-tilde}
+Note that, according to Eqs. \ref{eq:H-tilde}
 and \ref{eq:N-tilde-VT-N-V},
@@
 
-For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
+For triaxial ellipsoids (i.g. $a > b > c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
-are given by:
+are given by
 \begin{equation}
@@
 \frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
-d\psi \: ,
+d\psi
 \label{eq:F-kappa-phi}
@@
 called Legendre's normal elliptic integrals of the first and
-second kind, respectivelly. \citet{stoner1945} presented a
+second kind, respectively. \citet{stoner1945} presented a
 detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
@@
 
-For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
+For prolate ellipsoids (i.e. $a > b = c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
-are given by:
+are given by
 \begin{equation}
@@
 can be found, for example, in \citet{stoner1945}.
-These formulas were posteriorly presented by \citet{emerson1985}.
+These formulas were later presented by \citet{emerson1985}.
 It can be shown that these demagnetizing factors
@@
 
-For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
+For oblate ellipsoids (i.e. $a < b = c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
-are given by:
+are given by
 \begin{equation}
@@
 \end{equation}
-$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and
+where $e_{1} = a$, $e_{2} = b$, $e_{3} = c$ and
 $\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
@@
 
-For triaxial ellipsoids (e.g., $a > b > c$), the functions
+For triaxial ellipsoids (i.e. $a > b > c$), the functions
 $g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
@@
 
-For prolate (e.g., $a > b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by:
+For prolate (i.e. $a > b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by
 \begin{equation}
@@
 
-For oblate (e.g., $a < b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by:
+For oblate (i.e. $a < b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by
 \begin{equation}
@@
 By considering $\tilde{\mathbf{r}}$ as a point within the
-volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate
+volume $\vartheta$ of the ellipsoid and using the Maxwell postulate
 about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$
@@
 where $\mathbf{I}$ is the identity matrix and
-$\tilde{\mathbf{N}}^{\dagger}$ is defined in the
+$\tilde{\mathbf{N}}^{\dagger}$ is as defined in the
 previous section.
@@
 \end{equation}
-Despite of the coordinate system transformation represented by the
+Despite the coordinate system transformation represented by the
 matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
@@
 the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
-In this case, the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
+In this case the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
 referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
@@
 many authors
-\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
+\citep{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
 the induced magnetization opposes the inducing field
@@
 $\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
-can be approximated by:
+can be approximated by
 \begin{equation}
@@
 where $\tilde{n}^{\dagger}_{max}$ is the demagnetization
-factor associated to the shortest ellipsoid semi-axis.
+factor associated with the shortest ellipsoid semi-axis.
 For a triaxial ellipsoid,
@@
 which represents the maximum isotropic susceptibility
-that the ellipsoidal body can assume in order o guarantee
+that the ellipsoidal body can assume in order to guarantee
 a relative error lower than or equal to $\epsilon$.
@@
 consider a reference ellipsoid which is immersed in a uniform inducing
-field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
+field and has semi-axes $a$, $b$ and $c$, isotropic susceptibility $\chi$
 and no remanence.
 The magnetization of this ellipsoid, defined in the local coordinate system,
-can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde}, and \ref{eq:M-tilde}
+can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde} and \ref{eq:M-tilde}
 as follows:
@@
 $e_{3} = c$, only the $i$th component $P_{i}$ of the magnetic moment $\tilde{\mathbf{P}}$
-is non null and given by
+is non-null, and given by
 \begin{equation}
@@
 Now, consider a confocal ellipsoid with semi-axes $a^{\prime} = \sqrt{a^2+u}$,
-$b^{\prime} = \sqrt{b^2+u}$, and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
+$b^{\prime} = \sqrt{b^2+u}$ and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
 positive real number. From Eq. \ref{eq:P-tilde-i}, we can define the
@@
 $\tilde{n}^{\dagger}_{ii}$ is the new demagnetizing factor computed for the
-confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
+confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate}
 or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
-It can be shown that this confocal ellipsoid produce the same magnetic field
+It can be shown that this confocal ellipsoid produces the same magnetic field
 as the reference ellipsoid.
@@
 by using the NumPy and SciPy libraries \citep{vanderwalt2011},
-as part of the open-source source library
+as part of the open-source library
 Fatiando a Terra \citep{uieda2013}.
@@
 (\url{http://jupyter.org}),
-which is a web application that allows creating and sharing
+which is a web application that allows the creation and sharing of
 documents that contain live code, equations, visualizations and
@@
 All the code developed for generating the results presented in the following
-subsections, as well as the code developed for generating additional numerical simulations,
+sections, as well as the code developed for generating additional numerical simulations,
 can be found at the folder \textit{code} of the online repository
@@
 We simulated a triaxial ellipsoid with semi-axes
-$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
+$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m} and $c_{0} = 200$ \unit{m}.
 Then we used this ellipsoid as a reference to generate
@@
 their demagnetizing factors $\tilde{n}^{\dagger}_{11}$,
-$\tilde{n}^{\dagger}_{22}$, and $\tilde{n}^{\dagger}_{33}$
+$\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$
 by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
-\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
+\ref{eq:n-tilde-dagger-22-triaxial} and \ref{eq:n-tilde-dagger-33-triaxial}.
 The semi-axes of these 100 ellipsoids are given by
-$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
+$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$ and
 $c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$.
-Notice that, for $u = 0$, the resulting semi-axes are equal those
+Notice that, for $u = 0$, the resulting semi-axes are equal to those
 of the reference ellipsoid.
 The larger the variable $u$, the larger the resulting semi-axes
-$a$, $b$, and $c$, but the smaller the relative difference between
+$a$, $b$ and $c$, but the smaller the relative difference between
 them.
@@
 (Eq. \ref{eq:n-tilde-dagger-11-triaxial}),
-$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial}),
+$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial})
 and
 $\tilde{n}^{\dagger}_{33}$ (Eq. \ref{eq:n-tilde-dagger-33-triaxial})
-tend to $1/3$ \citep[e.g.,][]{stoner1945}.
+tend to $1/3$ \citep[e.g.][]{stoner1945}.
 
@@
 demagnetizing factors $\tilde{n}^{\dagger}_{11}$ (in red),
-$\tilde{n}^{\dagger}_{22}$ (in green), and
+$\tilde{n}^{\dagger}_{22}$ (in green) and
 $\tilde{n}^{\dagger}_{33}$ (in blue) for the
@@
 to what we know from theory.
-Besides, Fig. \ref{fig:demag-factors}a confirms that the demagnetizing
+Also, Fig. \ref{fig:demag-factors}a confirms that the demagnetizing
 factors satisfy the condition
@@
 calculated for the prolate ellipsoids are close to $1/3$ for $m$ close to $1$.
-Besides, these demagnetizing factors satisfy the condition
+Also, these demagnetizing factors satisfy the condition
 $\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$ for all values
@@
 shown in Tab. \ref{tab:parameters-confocal-ellipsoids}.
-The semi-axes of the Ellipsoid 2 were defined as $\sqrt{a^{2} + u}$,
-$\sqrt{b^{2} + u}$, and $\sqrt{c^{2} + u}$, where $a$, $b$, and $c$
-are the semi-axes of the Ellipsoid 1 and $u = 2 \times 10^{6}$ \unit{m}.
-
-We have computed the total-field anomalies produced by the Ellipsoid 1
+The semi-axes of Ellipsoid 2 were defined as $\sqrt{a^{2} + u}$,
+$\sqrt{b^{2} + u}$ and $\sqrt{c^{2} + u}$, where $a$, $b$, and $c$
+are the semi-axes of Ellipsoid 1 and $u = 2 \times 10^{6}$ \unit{m}.
+
+We have computed the total-field anomalies produced by Ellipsoid 1
 and Ellipsoid 2 at the same regular grid of $200 \times 200$ points
@@
 
-In the first case, we used an uniform inducing field $\mathbf{H}_{0}$ which is
+In the first case, we used a uniform inducing field $\mathbf{H}_{0}$ which is
 parallel to the semi-axis $a$ of the confocal ellipsoids and
-has inclination $\approx -4.98^{\circ}$, declination $\approx 15.38^{\circ}$,
+has inclination $\approx -4.98^{\circ}$, declination $\approx 15.38^{\circ}$
 and intensity $H_{0} \approx 18.7$ \unit{A \, m^{-1}}.
@@
 inducing field is shown in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-parallel}.
-In this case, the Ellipsoid 2 produces the same total-field
-anomaly as the Ellipsoid 1.
+In this case, Ellipsoid 2 produces the same total-field
+anomaly as Ellipsoid 1.
 The isotropic susceptibility of the Ellipsoid 2 was calculated with
-Eq. \ref{eq:chi-prime} and, consequently, its magnetic moment is equal
-to that of the Ellipsoid 1.
-Notice that the volume of the Ellipsoid 2 is approximately $79$ times greater
-than that of the Ellipsoid 1, whereas the isotropic susceptibility
-of the Ellipsoid 1 is approximately $85$ times greater than that
-of the Ellipsoid 2.
+Eq. \ref{eq:chi-prime} and consequently its magnetic moment is equal
+to that of Ellipsoid 1.
+Notice that the volume of Ellipsoid 2 is approximately $79$ times greater
+than that of Ellipsoid 1, whereas the isotropic susceptibility
+of Ellipsoid 1 is approximately $85$ times greater than that
+of Ellipsoid 2.
 This result illustrates the ambiguity between the field produced
@@
 \ref{fig:tfa-confocal-ellipsoids-H0-oblique}b show the total-field anomalies
-produced, respectively, by the Ellipsoid 1 and Ellipsoid 2
+produced, respectively, by Ellipsoid 1 and Ellipsoid 2
 by using this new inducing field $\mathbf{H}_{0}$.
@@
 the total-field anomalies produced by the confocal ellipsoids
-are different to each other due to the shape anisotropy.
-The differences are show in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-oblique}c.
+are different from each other due to the shape anisotropy.
+The differences are shown in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-oblique}c.
 These results confirm numerically what was pointed out by
@@
 We simulated an ellipsoidal body similar to the Warrego orebody,
-which was the resource on which the well-known Warrego mine was
+which was the resource on which the well-known Warrego mine 
 developed in Tennant Creek, Australia. After nearly a decade as
@@
 the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
-%This result reinforces that the use of the approximated magnetization
-%$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
-%the magnetic modelling of bodies with high isotropic susceptibility.
 
@@
 which represents $\approx 0.6 \%$ of the peak-to-peak amplitude of the
-total-field anomaly calculates by using the true magnetization $\mathbf{M}$
+total-field anomaly calculated by using the true magnetization $\mathbf{M}$
 (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
@@
 which represents $\approx 0.7 \%$ of the peak-to-peak amplitude of the
-total-field anomaly calculates by using the true magnetization $\mathbf{M}$
+total-field anomaly calculated by using the true magnetization $\mathbf{M}$
 (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
-In this case, the use an isotropic susceptibility greater than the usual
+In this case, the use of an isotropic susceptibility greater than the usual
 limit $0.1$ \unit{SI} does not mislead the magnetic modelling
@@
 BSD 3-clause licence and it is available for download at 
-Zenodo:  \url{http://doi.org/10.5281/zenodo.825261} \citep{tomazella2017}. The latest
+Zenodo:  \url{http://doi.org/10.5281/zenodo.825261} \citep{takahashi2017}. The latest
 development version of our code can be freely downloaded from
@@
 $v_{jk}$, $j = 1, 2, 3$, are the elements of the matrix
-$\mathbf{V}$ (Eq. \ref{eq:A}),
+$\mathbf{V}$ (Eq. \ref{eq:A})
 and $c_{k}$ is a constant defined by the coordinates
@@
 evaluated at the same point, but on different coordinate
-systems, we have:
+systems, we have
 \begin{equation*}
@@
 $r_{i}$ of the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
-we obtain:
+we obtain
 \begin{equation}
@@
 where $\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ is a $3 \times 3$
-matrix whose $ij$-th element is
+matrix whose $ij$th element is
 $\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
@@
 where $\mathbf{F}(\mathbf{r})$ is a $3 \times 3$
-matrix whose $ij$-th element is
+matrix whose $ij$th element is
 $\frac{\partial^{2} f(\mathbf{r})}
@@
 $\mathbf{V}$ (Eq. \ref{eq:A}) is defined according
-to the ellipsoid type. As one may noticed,
+to the ellipsoid type. Notice that
 the matrices $\mathbf{F}(\mathbf{r})$ and
@@
 and $\tilde{f}(\tilde{\mathbf{r}})$, respectively.
-Besides, the depolarization tensor $\mathbf{N}(\mathbf{r})$
+Also, the depolarization tensor $\mathbf{N}(\mathbf{r})$
 (Eq. \ref{eq:H-M-uniform}) can be
 rewritten by using the matrix $\mathbf{F}(\mathbf{r})$
-as follows
+as follows:
 \begin{equation}
@@
 Let us consider an ellipsoid with semi-axes $a$, $b$, $c$ oriented along
-the $\tilde{x}$-, $\tilde{y}$-, and $\tilde{z}$-axis, respectively,
+the $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ axis, respectively,
 of its local coordinate system (Fig. \ref{fig:orientation-angles}b), where $a > b > c > 0$.
@@
 \end{equation}
-A quadric surface (e.g., ellipsoid, hyperboloid of one sheet or
+A quadric surface (e.g. ellipsoid, hyperboloid of one sheet or
 hyperboloid of two sheets) which is confocal with the ellipsoid
@@
 Now, consider the problem of determining the ellipsoid which is confocal
-with that one defined in \ref{eq:reference-triaxial-ell} and pass through
+with that defined in \ref{eq:reference-triaxial-ell} and pass through
 a particular point $(\tilde{x}, \tilde{y}, \tilde{z})$.
 This problem consists in determining the real number $u$ that,
-given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$,
+given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$ and $\tilde{z}$,
 satisfies Eq. \ref{eq:quadric-confocal-triaxial-ell} and
@@
 \end{equation}
-This cubic equation shows that:
+This cubic equation shows that
 \begin{equation}
@@
 Let us now consider a prolate ellipsoid with semi-axes $a$, $b$,
-$c$ oriented along the $\tilde{x}$-, $\tilde{y}$-, and
-$\tilde{z}$-axis, respectively, of its local coordinate system
+$c$ oriented along the $\tilde{x}$, $\tilde{y}$, and
+$\tilde{z}$ axis, respectively, of its local coordinate system
 (Fig. \ref{fig:orientation-angles}b), where $a > b = c > 0$.
-In this case, the Eq. defining the surface of the ellipsoid
+In this case, the equation defining the surface of the ellipsoid
 is obtained by substituting $c = b$ in Eq. \ref{eq:reference-triaxial-ell}.
@@
 and the new condition that must be fulfilled by the variable
-$u$ so that Eq. \ref{eq:quadric-confocal-prolate-ell}
-represent an ellipsoid is
+$u$ for Eq. \ref{eq:quadric-confocal-prolate-ell}
+to represent an ellipsoid is
 \begin{equation}
@@
 Similarly to the case of a triaxial ellipsoid presented
-in the previous subsection, we are interested in
+in the previous section, we are interested in
 determining the real number $u$ that,
-given $a$, $b$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$,
+given $a$, $b$, $\tilde{x}$, $\tilde{y}$ and $\tilde{z}$,
 satisfies Eq. \ref{eq:quadric-confocal-prolate-ell} and
@@
 requires not only the parameter lambda defined by Eqs.
-\ref{eq:lambda-triaxial-ell} and \ref{eq:lambda-prolate-ell},
+\ref{eq:lambda-triaxial-ell} and \ref{eq:lambda-prolate-ell}
 but also its derivatives with respect to the spatial coordinates
-$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$.
+$\tilde{x}$, $\tilde{y}$ and $\tilde{z}$.
 Fortunately, the spatial derivatives of the parameter $\lambda$
@@
 $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, $\tilde{r}_{3} = \tilde{z}$,
-$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$.
+$e_{1} = a$, $e_{2} = b$ and $e_{3} = c$.
 This equation can be determined directly from equation
@@
 
-D. T. Tomazella thanks the brazilian research founding agency
+D. Takahashi thanks the brazilian research founding agency
 Conselho Nacional de
@@
 (a) Main coordinate system with axes $x$, $y$, and $z$ pointing to
-North, East, ans down, respectively.
-The dark gray plane contains the centre $(x_{c}, y_{c}, z_{c})$
+north, east, ans down, respectively.
+The dark grey plane contains the centre $(x_{c}, y_{c}, z_{c})$
 (white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
@@
 The strike direction is defined by the intersection of the
-dark gray plane and the horizontal plane (represented in light gray),
-which contains the $x$ and $y$ axes. The angle $\varepsilon$
-between the $x$-axis and the strike direction is called \textit{strike}.
-The angle $\zeta$ between the horizontal plane and the dark gray plane
+dark grey plane and the horizontal plane (represented in light grey),
+which contains the $x$ axis and $y$ axis. The angle $\varepsilon$
+between the $x$ axis and the strike direction is called \textit{strike}.
+The angle $\zeta$ between the horizontal plane and the dark grey plane
 is called \textit{dip}. The angle $\eta$ between the strike direction
@@
 (black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
-$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
-define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
+$\mathbf{v}_{2}$ and $\mathbf{v}_{3}$. These unit vectors
+define the semi-axes $a$, $b$ and $c$ of triaxial, prolate
 and oblate ellipsoids in the same way.
@@
 produced by 100 triaxial ellipsoids with semi-axes
-$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
+$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$ and
 $c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$ and
@@
 \ref{eq:n-tilde-dagger-22-oblate}.
-The horizontal black line represent the value $1/3$.}
+The horizontal black line represents the value $1/3$.}
 \label{fig:demag-factors}
@@
 at the constant vertical coordinate $z = 0$ \unit{m}.
-These data were calculated with an uniform inducing field
+These data were calculated with a uniform inducing field
 parallel to the semi-axis $a$ of the confocal ellipsoids.}
@@
 \includegraphics[width=8.3cm]{figures/f04.pdf}
-\caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
+\caption{Total-field anomalies (in \unit{nT}) produced by (a) Ellipsoid 1
 and (b) Ellipsoid 2, both defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
@@
 at the constant vertical coordinate $z = 0$ \unit{m}.
-These data were calculated with an uniform inducing field
+These data were calculated with a uniform inducing field
 which is oblique to the semi-axes of the confocal ellipsoids.
 (c) Difference between the total-field anomalies shown in
-b and a.}
+(b) and (a).}
 \label{fig:tfa-confocal-ellipsoids-H0-oblique}
@@
 \caption{Parameters defining a synthetic orebody. This model is
-based on the that presented by \citet{farrar1979} to simulate
+based on that presented by \citet{farrar1979} to simulate
 the Warrego orebody, Tennant Creek field, Australia.}
@@
 Isotropic susceptibility $\chi$ & $1.69$ & \unit{SI} \\
-$x$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 32610 & \unit{nT} \\
-$y$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 0 & \unit{nT} \\
-$z$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 39450 & \unit{nT} \\
+$x$ component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 32610 & \unit{nT} \\
+$y$ component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 0 & \unit{nT} \\
+$z$ component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 39450 & \unit{nT} \\
 \bottomhline
